### 2016-10-21 Paper/paper.tex
add paper materials

\documentclass[reprint,aps,prd,superscriptaddress,showkeys,showpacs]{revtex4-1}
\usepackage{epsfig,amsmath,natbib}

\usepackage{aas_macros}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage{hyperref}
\usepackage{color}
\usepackage{pbox}
\usepackage{booktabs}
\usepackage[dvipsnames]{xcolor}

\hypersetup{
	colorlinks=false,
	citecolor=green
}

%%%%%%%%%%%%%%%%%
%Custom commands%
%%%%%%%%%%%%%%%%%

\newcommand{\bb}[1]{\mathbf{#1}}
\newcommand{\bbh}[1]{\mathbf{\hat{#1}}}
\newcommand{\h}[1]{\hat{#1}}

\newcommand{\ttt}[1]{\texttt{#1}}

\newcommand\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
        \raise1pt\hbox{$<$}}}
\newcommand\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
        \raise1pt\hbox{$>$}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{On the validity of the Born approximation for Weak Lensing convergence moments}

\author{Andrea Petri}
\email{apetri@phys.columbia.edu}
\affiliation{Department of Physics, Columbia University, New York, NY 10027, USA}
\affiliation{Physics Department, Brookhaven National Laboratory, Upton, NY 11973, USA}

\author{Zolt\'an Haiman}
\affiliation{Department of Astronomy, Columbia University, New York, NY 10027, USA}

\author{Morgan May}
\affiliation{Physics Department, Brookhaven National Laboratory, Upton, NY 11973, USA}

\date{\today}

\label{firstpage}

\begin{abstract}

\end{abstract}

\keywords{Weak gravitational lensing --- Simulations --- Methods: numerical, analytical, statistical}
\pacs{98.80.-k, 95.36.+x, 95.30.Sf, 98.62.Sb}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%% INTRO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
%

%%%%%%%%%%%%%%%%%%%%%%%%%% SIMULATIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Simulations}
%

\subsection{Ray tracing}

\subsection{Born approximation}

\subsection{Post Born corrections}

%%%%%%%%%%%%%%%%%%%%%%%%%% PARAMETERS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Parameter inference}
%

%%%%%%%%%%%%%%%%%%%%%%%%%% DISCUSSION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion}
% 
%%%%%%%%%%%%%%%%%%%%%%%%%% CONCLUSIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusions}
%

%%%%%%%%%%%%%%%%%%%%%%%%%% ACKNOWLEDGMENTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Acknowledgments}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{ref}

\label{lastpage}
\end{document}

### 2016-10-24 Paper/paper.tex
wrote raytracing section

@@
 
-\title{On the validity of the Born approximation for Weak Lensing convergence moments}
+\title{On the validity of the Born approximation for Weak Lensing observables}
 
@@
 \begin{abstract}
-
+Accurate forward modeling of Weak Lensing (WL) observables from cosmological parameters is a necessary tool for upcoming galaxy surveys.
+Because WL probes structures in the non--linear regime, analytical forward modeling is very challenging, if not impossible.
+Numerical simulations of WL features rely on ray--tracing through the outputs of $N$--body simulations, which requires knowledge of the gravitational potential and accurate solvers for light ray trajectories.
+A cheaper but less accurate procedure based on the Born approximation, on the other hand, requires knowledge of the density only and can be implemented more efficiently and at lower computational cost.
+In this work we show that geodesic perturbations are the dominant cause of inaccuracy in the Born approximation, lens-lens couplings being negligible.
+We also show that, although the Born approximation does not accurately predict WL convergence moments in the noiseless case, once galaxy shape noise is added the loss of accuracy is negligible even for a LSST--like survey.
 \end{abstract}
@@
 %
+Weak Gravitational Lensing is a promising observational technique to probe the standard $w$CDM model of the universe, and can help in constraining the Dark Energy equation of state parameters \citep{wlreview}.
+Accurate forward modeling of WL observables is crucial for parameter estimation purposes.
+This however is a challenging problem due to the non--linear nature of WL image fields.
+Numerical efforts for feature forward modeling are based on ray--tracing simulations that make use of the multi--lens--plane algorithm \citep{RayTracingJain,RayTracingHartlap} to predict cosmic shear from outputs of $N$--body simulations.
+Approximate techniques based on the Born approximation allow for a computationally cheaper, but potentially inaccurate, forward modeling \citep{RayTracingHartlap} which requires only knowledge of the matter density contrast integrated along the observer unperturbed line of sight.
+A variety of groups have studied the validity of the Born approximation for forward modeling of convergence power spectra and bi--spectra \citep{WLBispectrumDodelson}, spectra of WL cosmic flexions \citep{BornFlexion} and, in more recent work, CMB lensing bi--spectra \citep{CMBPrattenLewis}.
+In this work we focus on a numerical study of the Born approximation validity for forward modeling of a subset convergence real space low order moments.
+The paper is organized as follows: we give a brief review of the ray--tracing formalism, along with the Born approximation and its lowest order corrections.
+We then outline how cosmological parameter constraints can be derived from WL features.
+Finally, we summarize our main findings and discuss possible future developments of this study.
 
@@
 % 
+In this section we give an overview of the formalism behind WL simulations.
+WL observables are related to the matter density contrast $\delta$.
+Light rays crossing density inhomogeneities experience deflections, which cause observed galaxy shapes to be distorted.
+Modeling of image distortions can be done by computing light ray geodesics in the density field $\delta$.
+To simulate the matter density field we make use of the public code \ttt{Gadget2} \citep{Gadget2} and we run $N$--body simulations with a box size of $L_b=260\,{\rm Mpc}/h$ and $N_p=512^3$ particles, which corresponds to a mass resolution of $M_p\approx 10^{10}M_\odot$ per particle.
+We then perform a grid--based density estimation based on the position of the particles at different times.
+From the three dimensional density contrast $\delta$, the two dimensional lensing potential $\Phi$ can be inferred by solving the Poisson equation
+
+\begin{equation}
+\label{sim:poisson}
+\nabla_\perp^2\Phi(\bb{x}_\perp,\chi) = \frac{3H_0^2\Omega_m}{2c^2a(\chi)} \delta(\bb{x}_\perp,\chi)
+\end{equation} 
+%
+Where we indicated the transverse comoving coordinates as $\bb{x}_\perp$, the longitudinal comoving distance as $\chi$, the universe scale factor as $a$ and as $H_0$,$\Omega_m$ the Hubble parameter and the matter density parameter respectively.
+The time dependence of $\Phi,\delta$ has been absorbed in $\chi$ with the use of the distance--redshift relation.
+Under the flat sky approximation, the transverse coordinates $\bb{x}_\perp$ can be related as the angles as seen from an Earth based observer $\pmb{\beta}=\bb{x}_\perp/\chi$.
+In the following paragraph we give a summary of the ray--tracing basics.
 
 \subsection{Ray tracing}
+Light ray trajectories correspond to null geodesics in the space--time metric induced by the density fluctuations $\delta(\bb{x}_\perp,\chi)$.
+It can be shown that with the spacetime parametrization adopted in this section, the geodesic equation takes the form (see \citep{BornFlexion} for a possible reference)
+
+\begin{equation}
+\label{sim:geodiff}
+\frac{d^2 \bb{x}_\perp(\chi)}{d\chi^2} = -2\nabla_\perp \Phi(\bb{x}_\perp,\chi)
+\end{equation}
+%
+Equation (\ref{sim:geodiff}) can be directly integrated to express its solution $\bb{x}_\perp(\chi)$ in explicit form (see \citep{DodelsonWL})
+
+\begin{equation}
+\label{sim:geosol}
+\bb{x}_\perp(\chi_s) = \bb{x}_\perp(0) -2\int_0^{\chi_s} d\chi (\chi_s-\chi) \nabla_\perp \Phi(\bb{x}_\perp(\chi),\chi)
+\end{equation}
+%
+Where $\chi_s$ is the source galaxy comoving distance.
+WL observables are related to the differential deflection that nearby light rays experience when traveling from the observer to the source.
+Indicating with $\pmb{\theta}$ the starting angular position of a light ray at $\chi=0$ and with $\pmb{\beta}_s$ the angular position of the light ray at $\chi=\chi_s$, we are interested in the Jacobian matrix $\bb{A}_s(\pmb{\theta})=\partial\pmb{\beta}_s(\pmb{\theta})/\partial \pmb{\theta}$, which is usually parametrized as
+
+\begin{equation}
+\bb{A}_s(\pmb{\theta}) = 
+\begin{pmatrix}
+1-\kappa(\pmb{\theta})-\gamma^1(\pmb{\theta}) & -\gamma^2(\pmb{\theta}) + \omega(\pmb{\theta}) \\
+-\gamma^2(\pmb{\theta}) - \omega(\pmb{\theta}) & 1-\kappa(\pmb{\theta})+\gamma^1(\pmb{\theta})
+\end{pmatrix}
+\end{equation}
+%
+Where $\kappa,\pmb{\gamma},\omega$ refer respectively to the WL cosmic convergence, shear and rotation angle.
+The implicit solution (\ref{sim:geosol}) to the geodesic equation (\ref{sim:geodiff}) can be translated in an integral equation for the lensing Jacobian
+
+\begin{widetext}
+\begin{equation}
+\label{sim:jacsol}
+A_{ij}(\pmb{\theta},\chi_s) = \delta^K_{ij}-2\int_0^{\chi_s} d\chi\chi W(\chi,\chi_s)\Phi_{ik}(\bb{x}_\perp(\chi,\pmb{\theta}),\chi)A_{kj}(\pmb{\theta},\chi)
+\end{equation} 
+\end{widetext}
+%
+We indicated the partial derivatives of the lensing potential $\Phi$ with respect to the transverse coordinates $x,y$ as subscripts.
+We also defined the single redshift source lensing kernel $W(\chi,\chi_s)=1-\chi/\chi_s$ and indicated the Kronecker delta symbol as $\delta^K$.
+The WL convergence $\kappa(\pmb{\theta},\chi_s)$ can be calculated from the trace of the Jacobian
+\begin{equation}
+\kappa(\pmb{\theta},\chi_s) = 1-\frac{1}{2}{\rm tr}\left[\bb{A}(\pmb{\theta},\chi_s)\right]
+\end{equation}
+%
+The implicit form of equation (\ref{sim:jacsol}) suggests a straightforward way to solve the geodesic equation numerically because $A(\pmb{\theta},\chi_s)$ can be expressed once one knows $A(\pmb{\theta},\chi)$ for $\chi<\chi_s$.
+The multi--lens--plane algorithm \citep{RayTracingJain,RayTracingHartlap} is a popular method to compute the integral in (\ref{sim:jacsol}) in discrete steps (lenses) by keeping track of the intermediate values $A(\pmb{\theta},\chi)$ using dynamic programming.
+To carry out the geodesic calculations we make use of the \ttt{LensTools} software package \citep{LensTools-paper}, which provides a {\sc python} implementation of the multi--lens--plane algorithm.
+The exact solution of (\ref{sim:geodiff}) based on (\ref{sim:jacsol}) is computationally expensive because it requires knowledge of the lensing potential $\Phi$.
+In the next paragraph we review the details of a computationally cheaper but approximate approach based on the Born approximation.
 
 \subsection{Born approximation}
+The integral in (\ref{sim:jacsol}) can be approximated using a series expansion in powers of $\Phi$, which can yield acceptable results in the limit in which $\Phi$ is small.
+To compute the lowest order approximation to (\ref{sim:jacsol}) one notes that the lensing potential appears on the right hand side and hence we can replace the Jacobian on the right hand side with its zeroth order expression, i.e.
+the identity matrix.
+We can also replace the real ray trajectory $\bb{x}_\perp(\chi,\pmb{\theta})$ with the unperturbed one, i.e.
+$\chi\pmb{\theta}$.
+This yields an expression for $\kappa$ at first order in $\Phi$
+
+\begin{equation}
+\label{sim:born}
+\kappa^{\rm born}(\pmb{\theta},\chi_s) = \frac{3H_0^2\Omega_m}{2c^2}\int_0^{\chi_s} d\chi\frac{\chi}{a(\chi)} W(\chi,\chi_s)\delta(\chi\pmb{\theta},\chi)
+\end{equation}
+%
+The Born approximated convergence in equation (\ref{sim:born}) has a simple interpretation: at lowest order in the lensing potential, $\kappa$ is the integrated matter density on the unperturbed line of sight, weighted by the lensing kernel $W$.
+Contrary to the exact ray--tracing approach, the Born approximation does not required knowledge of the solution to the Poisson equation (\ref{sim:poisson}) and is hence computationally cheaper.
+In the next paragraph we examine the corrections to the Born approximation that come at second order in the potential $\Phi$.
 
 \subsection{Post Born corrections}
+Equation (\ref{sim:jacsol}) allows to express the convergence $\kappa$ at arbitrary high orders in $\Phi$ powers.
+The linear order expression corresponds to the Born approximation in equation (\ref{sim:born}).
+At second order in $\Phi$ we can write, following \citep{WLBispectrumDodelson}
+
+\begin{equation}
+\kappa = \kappa^{\rm born} + \kappa^{\rm lens-lens} + \kappa^{\rm geodesic} + O(\Phi^3)
+\end{equation}
+%
+The second order corrections can be expressed as double integrals along the unperturbed line of sight
+
+\begin{widetext}
+
+\begin{equation}
+\label{sim:ll}
+\kappa^{\rm lens-lens}(\pmb{\theta},\chi_s) = \int_0^{\chi_s}d\chi\int_0^\chi d\chi' \chi\chi' W(\chi,\chi_s)W(\chi',\chi_s)\Phi_{ij}(\chi\pmb{\theta},\chi)\Phi_{ij}(\chi'\pmb{\theta},\chi')
+\end{equation}
+
+\begin{equation}
+\label{sim:gp}
+\kappa^{\rm geodesic}(\pmb{\theta},\chi_s) = \frac{3H_0^2\Omega_m}{2c^2}\int_0^{\chi_s}d\chi\int_0^\chi d\chi' \frac{\chi\chi'}{a(\chi')} W(\chi,\chi_s)W(\chi',\chi_s)\nabla_\perp\Phi(\chi\pmb{\theta},\chi)\cdot\nabla_\perp\delta(\chi'\pmb{\theta},\chi')
+\end{equation}
+
+\end{widetext}
+%
+These second order expression have a simple physical interpretation.
+Equation (\ref{sim:ll}) encodes the post--Born correction to the convergence due to non local quadratic lens--lens couplings, which add to the density line of sight integration in (\ref{sim:born}).
+Equation (\ref{sim:gp}), on the other hand, encodes the integral of the density contrast on the real light ray trajectory, at lowest order in the geodesic deflections.
+We computed the line of sight integrals (\ref{sim:born}), (\ref{sim:ll}) and (\ref{sim:gp}) using the functionality of the \ttt{LensTools} suite \citep{LensTools-paper}.
+A sample of the simulation outputs is shown in Figure \ref{fig:csample}.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.4]{Figures/csample.eps}
+\end{center}
+\caption{Sample convergence outputs for one realization of a $(3.5\,{\rm deg})^2$ field of view.
+The figure shows the convergence profile (top left), along with the Born approximation residuals (top right), the lens-lens post--Born contribution (bottom left) and the geodesic contribution (bottom right).
+The images have been smoothed with a Gaussian kernel of size $\theta_G=0.5^\prime$.}
+\label{fig:csample}
+\end{figure*}
 
@@
 % 
+The parameter estimator (\ref{par:fisherest})
+\begin{equation}
+\label{par:fisherest}
+\bbh{p} = \bb{p}_0 + (\bb{M\Psi M}^T)^{-1} \bb{M\Psi} (\bbh{d}-\bb{d}_0)
+\end{equation}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%% DISCUSSION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%% RESULTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Discussion}
+\section{Results}
 % 

### 2016-10-24 Paper/Figures/generate.py

@@ -9,9 +9,11 @@ import itertools
 import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
+import astropy.units as u
 
 from lenstools.pipeline.simulation import SimulationBatch
 
+from lenstools.image.convergence import ConvergenceMap
 from lenstools.statistics.ensemble import Ensemble
 from lenstools.statistics.constraints import FisherAnalysis
 
@@ -36,6 +38,40 @@ variations = (
 )
 
 plab = { "Om":r"$\Omega_m$", "w0":r"$w_0$", "wa":r"$w_a$", "si8":r"$\sigma_8$" }
+
+###################################################################################################
+###################################################################################################
+
+def convergenceVisualize(cmd_args,smooth=0.5*u.arcmin,fontsize=22):
+
+	#Initialize plot
+	fig,ax = plt.subplots(2,2,figsize=(16,16))
+
+	#Load data
+	cborn = ConvergenceMap.load(os.path.join(fiducial["c0"].getMapSet("kappaBorn").home,"born_z2.00_0001r.fits"))
+	cray = ConvergenceMap.load(os.path.join(fiducial["c0"].getMapSet("kappa").home,"WLconv_z2.00_0001r.fits"))
+	cll = ConvergenceMap.load(os.path.join(fiducial["c0"].getMapSet("kappaGP").home,"postBorn2-ll_z2.00_0001r.fits"))
+	cgp = ConvergenceMap.load(os.path.join(fiducial["c0"].getMapSet("kappaGP").home,"postBorn2-gp_z2.00_0001r.fits"))
+
+	#Smooth
+	for c in (cborn,cray,cll,cgp):
+		c.smooth(smooth,kind="gaussianFFT",inplace=True)
+
+	#Plot
+	cray.visualize(colorbar=True,fig=fig,ax=ax[0,0])
+	(cray+cborn*-1).visualize(colorbar=True,fig=fig,ax=ax[0,1])
+	cll.visualize(colorbar=True,fig=fig,ax=ax[1,0])
+	cgp.visualize(colorbar=True,fig=fig,ax=ax[1,1])
+
+	#Titles
+	ax[0,0].set_title(r"$\kappa$",fontsize=fontsize)
+	ax[0,1].set_title(r"$\kappa-\kappa^{\rm born}$",fontsize=fontsize)
[…]

### 2016-10-24 batchcode/scripts/measure_from_maps.py
add method to measure cross power

@@ -42,6 +42,34 @@ def convergence_power(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,
 	except IOError:
 		return None
 
+##########################################################################################
+##############Measure the cross power#####################################################
+##########################################################################################
+
+def cross_power(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=15,smoothing_scale=0.0*u.arcmin,cross="kappaGP"):
+
+	try:
+		conv = ConvergenceMap.load(map_set.path(fname))
+		conv2 = ConvergenceMap.load(map_set.path(fname).replace(map_set.name,cross))
+
+		if "0001r" in fname:
+			np.save(os.path.join(map_set.home_subdir,"num_ell_nb{0}.npy".format(len(l_edges)-1)),conv.countModes(l_edges))
+	
+		if smoothing_scale>0:
+			conv = conv.smooth(smoothing_scale,kind="gaussianFFT")
+			conv2 = conv2.smooth(smoothing_scale,kind="gaussianFFT")
+
+		if add_shape_noise:
+			gen = GaussianNoiseGenerator.forMap(conv)
+			conv = conv + gen.getShapeNoise(z=z,ngal=ngal*(u.arcmin**-2),seed=hash(os.path.basename(fname))%4294967295)
+			conv2 = conv2 + gen.getShapeNoise(z=z,ngal=ngal*(u.arcmin**-2),seed=hash(os.path.basename(fname))%4294967295)
+
+		l,Pl = conv.cross(conv2,l_edges=l_edges)
+		return Pl
+
+	except IOError:
+		return None
+
 ##############################################################################
 ##############Peak counts#####################################################
 ##############################################################################

### 2016-10-25 Paper/paper.tex
wrote parameters section

@@
         \raise1pt\hbox{$>$}}}
+
+\newcommand\pt{\pmb{\theta}}
 
@@
 WL observables are related to the differential deflection that nearby light rays experience when traveling from the observer to the source.
-Indicating with $\pmb{\theta}$ the starting angular position of a light ray at $\chi=0$ and with $\pmb{\beta}_s$ the angular position of the light ray at $\chi=\chi_s$, we are interested in the Jacobian matrix $\bb{A}_s(\pmb{\theta})=\partial\pmb{\beta}_s(\pmb{\theta})/\partial \pmb{\theta}$, which is usually parametrized as
+Indicating with $\pt$ the starting angular position of a light ray at $\chi=0$ and with $\pmb{\beta}_s$ the angular position of the light ray at $\chi=\chi_s$, we are interested in the Jacobian matrix $\bb{A}_s(\pt)=\partial\pmb{\beta}_s(\pt)/\partial \pt$, which is usually parametrized as
 
 \begin{equation}
-\bb{A}_s(\pmb{\theta}) = 
+\bb{A}_s(\pt) = 
 \begin{pmatrix}
-1-\kappa(\pmb{\theta})-\gamma^1(\pmb{\theta}) & -\gamma^2(\pmb{\theta}) + \omega(\pmb{\theta}) \\
--\gamma^2(\pmb{\theta}) - \omega(\pmb{\theta}) & 1-\kappa(\pmb{\theta})+\gamma^1(\pmb{\theta})
+1-\kappa(\pt)-\gamma^1(\pt) & -\gamma^2(\pt) + \omega(\pt) \\
+-\gamma^2(\pt) - \omega(\pt) & 1-\kappa(\pt)+\gamma^1(\pt)
 \end{pmatrix}
@@
 \label{sim:jacsol}
-A_{ij}(\pmb{\theta},\chi_s) = \delta^K_{ij}-2\int_0^{\chi_s} d\chi\chi W(\chi,\chi_s)\Phi_{ik}(\bb{x}_\perp(\chi,\pmb{\theta}),\chi)A_{kj}(\pmb{\theta},\chi)
+A_{ij}(\pt,\chi_s) = \delta^K_{ij}-2\int_0^{\chi_s} d\chi\chi W(\chi,\chi_s)\Phi_{ik}(\bb{x}_\perp(\chi,\pt),\chi)A_{kj}(\pt,\chi)
 \end{equation} 
@@
 We also defined the single redshift source lensing kernel $W(\chi,\chi_s)=1-\chi/\chi_s$ and indicated the Kronecker delta symbol as $\delta^K$.
-The WL convergence $\kappa(\pmb{\theta},\chi_s)$ can be calculated from the trace of the Jacobian
+The WL convergence $\kappa(\pt,\chi_s)$ can be calculated from the trace of the Jacobian
 \begin{equation}
-\kappa(\pmb{\theta},\chi_s) = 1-\frac{1}{2}{\rm tr}\left[\bb{A}(\pmb{\theta},\chi_s)\right]
+\label{sim:trkappa}
+\kappa(\pt,\chi_s) = 1-\frac{1}{2}{\rm tr}\left[\bb{A}(\pt,\chi_s)\right]
 \end{equation}
 %
-The implicit form of equation (\ref{sim:jacsol}) suggests a straightforward way to solve the geodesic equation numerically because $A(\pmb{\theta},\chi_s)$ can be expressed once one knows $A(\pmb{\theta},\chi)$ for $\chi<\chi_s$.
-The multi--lens--plane algorithm \citep{RayTracingJain,RayTracingHartlap} is a popular method to compute the integral in (\ref{sim:jacsol}) in discrete steps (lenses) by keeping track of the intermediate values $A(\pmb{\theta},\chi)$ using dynamic programming.
+The implicit form of equation (\ref{sim:jacsol}) suggests a straightforward way to solve the geodesic equation numerically because $A(\pt,\chi_s)$ can be expressed once one knows $A(\pt,\chi)$ for $\chi<\chi_s$.
+The multi--lens--plane algorithm \citep{RayTracingJain,RayTracingHartlap} is a popular method to compute the integral in (\ref{sim:jacsol}) in discrete steps (lenses) by keeping track of the intermediate values $A(\pt,\chi)$ using dynamic programming.
 To carry out the geodesic calculations we make use of the \ttt{LensTools} software package \citep{LensTools-paper}, which provides a {\sc python} implementation of the multi--lens--plane algorithm.
@@
 the identity matrix.
-We can also replace the real ray trajectory $\bb{x}_\perp(\chi,\pmb{\theta})$ with the unperturbed one, i.e.
-$\chi\pmb{\theta}$.
+We can also replace the real ray trajectory $\bb{x}_\perp(\chi,\pt)$ with the unperturbed one, i.e.
+$\chi\pt$.
 This yields an expression for $\kappa$ at first order in $\Phi$
@@
 \label{sim:born}
-\kappa^{\rm born}(\pmb{\theta},\chi_s) = \frac{3H_0^2\Omega_m}{2c^2}\int_0^{\chi_s} d\chi\frac{\chi}{a(\chi)} W(\chi,\chi_s)\delta(\chi\pmb{\theta},\chi)
+\kappa^{\rm born}(\pt,\chi_s) = \frac{3H_0^2\Omega_m}{2c^2}\int_0^{\chi_s} d\chi\frac{\chi}{a(\chi)} W(\chi,\chi_s)\delta(\chi\pt,\chi)
 \end{equation}
@@
 \label{sim:ll}
-\kappa^{\rm lens-lens}(\pmb{\theta},\chi_s) = \int_0^{\chi_s}d\chi\int_0^\chi d\chi' \chi\chi' W(\chi,\chi_s)W(\chi',\chi_s)\Phi_{ij}(\chi\pmb{\theta},\chi)\Phi_{ij}(\chi'\pmb{\theta},\chi')
+\kappa^{\rm lens-lens}(\pt,\chi_s) = \int_0^{\chi_s}d\chi\int_0^\chi d\chi' \chi\chi' W(\chi,\chi_s)W(\chi',\chi_s)\Phi_{ij}(\chi\pt,\chi)\Phi_{ij}(\chi'\pt,\chi')
 \end{equation}
@@
 \label{sim:gp}
-\kappa^{\rm geodesic}(\pmb{\theta},\chi_s) = \frac{3H_0^2\Omega_m}{2c^2}\int_0^{\chi_s}d\chi\int_0^\chi d\chi' \frac{\chi\chi'}{a(\chi')} W(\chi,\chi_s)W(\chi',\chi_s)\nabla_\perp\Phi(\chi\pmb{\theta},\chi)\cdot\nabla_\perp\delta(\chi'\pmb{\theta},\chi')
+\kappa^{\rm geodesic}(\pt,\chi_s) = \frac{3H_0^2\Omega_m}{2c^2}\int_0^{\chi_s}d\chi\int_0^\chi d\chi' \frac{\chi\chi'}{a(\chi')} W(\chi,\chi_s)W(\chi',\chi_s)\nabla_\perp\Phi(\chi\pt,\chi)\cdot\nabla_\perp\delta(\chi'\pt,\chi')
 \end{equation}
@@
 Equation (\ref{sim:gp}), on the other hand, encodes the integral of the density contrast on the real light ray trajectory, at lowest order in the geodesic deflections.
-We computed the line of sight integrals (\ref{sim:born}), (\ref{sim:ll}) and (\ref{sim:gp}) using the functionality of the \ttt{LensTools} suite \citep{LensTools-paper}.
+The line of sight integrals (\ref{sim:born}), (\ref{sim:ll}) and (\ref{sim:gp}) can be computed efficiently with runtime that scales linearly with the number of lenses using the functionality of the \ttt{LensTools} suite \citep{LensTools-paper}.
 A sample of the simulation outputs is shown in Figure \ref{fig:csample}.
+In the next section we show how to infer cosmological parameters from WL features forward models applied to observations.
 
@@
 The figure shows the convergence profile (top left), along with the Born approximation residuals (top right), the lens-lens post--Born contribution (bottom left) and the geodesic contribution (bottom right).
-The images have been smoothed with a Gaussian kernel of size $\theta_G=0.5^\prime$.}
+The images have been smoothed with a Gaussian kernel of size $\theta_G=0.5\,{\rm arcmin}$.}
 \label{fig:csample}
@@
 % 
-The parameter estimator (\ref{par:fisherest})
+Parameter estimation from WL observations involves measurement of an image feature $\bbh{d}_{\rm obs}$ from a reconstructed convergence field $\h{\kappa}(\pt)$.
+The measured image feature is matched against a forward model $\bb{d}(\bb{p})$ to get an estimate of the cosmological parameters $\bbh{p}$.
+In the limit in which the feature likelihood is a multivariate Gaussian with $\bb{p}$--independent covariance $\bb{C}^{\bb{d}\bb{d}}$ and the forward model is linear in the parameters
+
+\begin{equation}
+\label{par:linapprox}
+\bb{d}(\bb{p}) = \bb{d}_0 + \bb{M}(\bb{p}-\bb{p}_0)
+\end{equation}
+%
+the maximum likelihood parameter estimator (\ref{par:fisherest}) is given by (see \citep{DodelsonSchneider13,PetriVariance} for example)
 \begin{equation}
 \label{par:fisherest}
-\bbh{p} = \bb{p}_0 + (\bb{M\Psi M}^T)^{-1} \bb{M\Psi} (\bbh{d}-\bb{d}_0)
+\bbh{p} = \bb{p}_0 + (\bb{M}^T\bb{\Psi M})^{-1} \bb{M}^T\bb{\Psi} (\bbh{d}_{\rm obs}-\bb{d}_0)
 \end{equation}
+%
+where $\bb{\Psi}=(\bb{C}^{\bb{d}\bb{d}})^{-1}$.
+The linearity assumption (\ref{par:linapprox}) is justified when the scatter of the measure feature $\bbh{d}_{\rm obs}$ around the expansion point $\bb{d}_0$ is expected to be small.
+This is true for upcoming large area surveys such as LSST \citep{LSST}, WFIRST \citep{WFIRST} and Euclid \citep{Euclid}.
+In this work we use $N$--body simulations coupled with the \ttt{LensTools} routines to simulate multiple realizations of a convergence field $\h{\kappa}(\pt)$ for different combinations of the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$.
+We choose the values $\bbh{p}_0=(0.26,-1,0.8)$ as our fiducial cosmological parameters and vary one parameter at a time as in Table \ref{tab:cosmopar} to measure the feature derivatives $\bb{M}$.
+
+To study the effect of the Born approximation on parameter constraints, we measure the fiducial features $\bb{d}_0$, the derivatives $\bb{M}$ and the feature covariance $\bb{C}^{\bb{d}\bb{d}}$ from $\kappa$ mocks constructed with the Born approximation (\ref{sim:born}).
+We then evaluate the induced parameter bias by applying the parameter estimator (\ref{par:fisherest}) to a mock observation constructed with full ray--tracing as in equations (\ref{sim:jacsol}), (\ref{sim:trkappa}).
+We perform the ray--tracing and the line of sight integrals for fixed redshift sources at $z_s=2$ uniformly distributed in a $(3.5\,{\rm deg})^2$ field of view, with a resolution of $2048^2$ pixels.
+To mimic an LSST--like mock observation, we use the 8192 realizations in our fiducial $\kappa$ ensemble to bootstrap the mean of 1000 fiducial feature measurements, which is equivalent approximately to a $10000\,{\rm deg}^2$ sky coverage.
+We use this bootstrapped mean as $\bbh{d}_{\rm obs}$.
+
+\begin{table}
+\begin{center}
+
+\begin{tabular}{c|c|c|c}
+$\Omega_m$ & $w$ & $\sigma_8$ & $\kappa$ realizations \\ \hline \hline
+\multicolumn{4}{c}{\textbf{Fiducial}} \\ \hline
+0.26 & -1 & 0.8 & 8192 \\ \hline
+
+\multicolumn{4}{c}{\textbf{Variation 1}} \\ \hline
+0.29 & -1 & 0.8 & 1024 \\
+0.26 & -0.8 & 0.8 & 1024 \\
+0.26 & -1 & 0.9 & 1024 \\ \hline
+
+\multicolumn{4}{c}{\textbf{Variation 2}} \\ \hline
+0.23 & -1 & 0.8 & 1024 \\
+0.26 & -1.2 & 0.8 & 1024 \\
+0.26 & -1 & 0.7 & 1024 \\ \hline
+
+\end{tabular}
+
+\end{center}
+
+\caption{Cosmological parameters used in our simulation suite}
+\label{tab:cosmopar}
+
+\end{table}
+
+We can add galaxy shape noise to our $\kappa$ mocks in the form of a pixel uncorrelated white Gaussian noise \citep{SongKnox} with rms
+\begin{equation}
+\label{par:shaperms}
+\sigma_{\rm shape} = \frac{0.15+0.035z_s}{\sqrt{N_g}}
+\end{equation}
+%
+where the number of galaxies per pixel $N_g$ is based on a galaxy angular density of $15\,{\rm arcmin}^{-2}$.
+
+Our image feature choice includes the $\kappa$ power spectrum $P^{\kappa\kappa}(\ell)$ defined as 
+\begin{equation}
+\label{par:powerdef}
+\langle\tilde{\kappa}(\pmb{\ell})\tilde{\kappa}^*(\pmb{\ell}')\rangle = (2\pi)^2\delta^D(\pmb{\ell}+\pmb{\ell}')P^{\kappa\kappa}(\ell) 
+\end{equation}
+%
+Where the expectation value is taken over $\pmb{\ell}$ modes with the same magnitude $\ell=\vert\pmb{\ell}\vert$ and $\delta^D$ is the Dirac delta function.
+Because the $\kappa$ field is non--Gaussian, higher order statistics such as higher real space $\kappa$ moments have been shown to contain complementary information in addition to the one already supplied by the power spectrum \citep{MinkPetri,CFHTMink,NG-Jain1,NG-Jain2}.
+We consider the following set of $\kappa$ moments $\pmb{\mu}$
+
+\begin{equation}
+\label{par:moments}
+\begin{matrix}
+\pmb{\mu} = (\pmb{\mu}_2,\pmb{\mu}_3,\pmb{\mu}_4) \\ \\
+\pmb{\mu}_2 = \left(\langle\kappa^2\rangle,\langle\vert\nabla\kappa\vert^2\rangle\right) \\ \\
+\pmb{\mu}_3 = \left(\langle\kappa^3\rangle,\langle\kappa^2\nabla^2\kappa\rangle,\langle\kappa\vert\nabla\kappa\vert^2\rangle\right) \\ \\
+\pmb{\mu}_4 = \left(\langle\kappa^4\rangle_c,\langle\kappa^3\nabla^2\kappa\rangle_c,\langle\kappa^2\vert\nabla\kappa\vert^2\rangle_c,\langle\vert\nabla\kappa\vert^4\rangle_c\right) \\
+\end{matrix}
+\end{equation} 
+%
+Where the expectation values are taken with respect to pixels and the subscript $c$ indicated that we are considering the connected components of the quartic moments $\pmb{\mu}_4$.
+In the next section we outline our main results.
 
@@
 %
+
+\subsection{Forward model accuracy}
+
+\subsection{Parameter bias}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%% DISCUSSION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Discussion}
+%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%% CONCLUSIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-10-25 Paper/Figures/generate.py
use seaborn for plotting

@@ -9,7 +9,10 @@ import itertools
 import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
+import seaborn as sns
 import astropy.units as u
+
+sns.set(font_scale=2)
 
 from lenstools.pipeline.simulation import SimulationBatch
 
@@ -68,6 +71,11 @@ def convergenceVisualize(cmd_args,smooth=0.5*u.arcmin,fontsize=22):
 	ax[0,1].set_title(r"$\kappa-\kappa^{\rm born}$",fontsize=fontsize)
 	ax[1,0].set_title(r"$\kappa^{\rm lens-lens}$",fontsize=fontsize)
 	ax[1,1].set_title(r"$\kappa^{\rm geodesic}$",fontsize=fontsize)
+
+	#Switch off grids
+	for i in (0,1):
+		for j in (0,1):
+			ax[i,j].grid(b=False) 
 
 	#Save
 	fig.tight_layout()
@@ -209,7 +217,14 @@ def pdfPlot(cmd_args,features,figname,fontsize=22):
 def pdfMoments(cmd_args,kappa_models=("kappa","kappaBorn","kappaBornRT"),figname="pdfMoments",fontsize=22):
 
 	#Moment labels
-	moment_labels = (r"$\sigma_0^2$",r"$\sigma_1^2$",r"$S_0$",r"$S_1$",r"$S_2$",r"$K_0$",r"$K_1$",r"$K_2$",r"$K_3$")
+	moment_labels = (
+		r"$\langle\kappa^2\rangle$",r"$\langle\vert\nabla\kappa\vert^2\rangle$",
+		r"$\langle\kappa^3\rangle$",r"$\langle\kappa^2\nabla^2\kappa\rangle$",r"$\langle\vert\nabla\kappa\vert^2\nabla^2\kappa\rangle$",
+		r"$\langle\kappa^4\rangle_c$",r"$\langle\kappa^3\nabla^2\kappa\rangle_c$",r"$\langle\kappa\vert\nabla\kappa\vert^2\nabla^2\kappa\rangle_c$",r"$\langle\vert\nabla\kappa\vert^4\rangle_c$"
+		)
+	
+	#Model labels
+	model_labels = {"kappa":"full","kappaBorn":"born","kappaBornRT":"hybrid"}
 
 	#Set up plot
 	fig,axes = plt.subplots(3,3,figsize=(24,)*2)
[…]

### 2016-10-25 batchcode/scripts/measure_from_maps.py
insert smoothing in feature ensemble filename

@@ -21,7 +21,7 @@ from emcee.utils import MPIPool
 ##############Measure the power spectrum#####################################################
 #############################################################################################
 
-def convergence_power(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=15,smoothing_scale=0.0*u.arcmin):
+def convergence_power(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=15,smoothing=0.0):
 	
 	try:
 		conv = ConvergenceMap.load(map_set.path(fname))
@@ -29,8 +29,8 @@ def convergence_power(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,
 		if "0001r" in fname:
 			np.save(os.path.join(map_set.home_subdir,"num_ell_nb{0}.npy".format(len(l_edges)-1)),conv.countModes(l_edges))
 	
-		if smoothing_scale>0:
-			conv = conv.smooth(smoothing_scale,kind="gaussianFFT")
+		if smoothing>0.:
+			conv = conv.smooth(smoothing*u.arcmin,kind="gaussianFFT")
 
 		if add_shape_noise:
 			gen = GaussianNoiseGenerator.forMap(conv)
@@ -46,7 +46,7 @@ def convergence_power(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,
 ##############Measure the cross power#####################################################
 ##########################################################################################
 
-def cross_power(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=15,smoothing_scale=0.0*u.arcmin,cross="kappaGP"):
+def cross_power(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=15,smoothing=0.0,cross="kappaGP"):
 
 	try:
 		conv = ConvergenceMap.load(map_set.path(fname))
@@ -55,9 +55,9 @@ def cross_power(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=1
 		if "0001r" in fname:
 			np.save(os.path.join(map_set.home_subdir,"num_ell_nb{0}.npy".format(len(l_edges)-1)),conv.countModes(l_edges))
 	
-		if smoothing_scale>0:
-			conv = conv.smooth(smoothing_scale,kind="gaussianFFT")
[…]

### 2016-10-25 batchcode/scripts/measure_from_maps.py
fix typo

@@ -82,7 +82,7 @@ def convergence_peaks(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,
 		if "0001r" in fname:
 			np.save(os.path.join(map_set.home_subdir,"th_peaks_nb{0}.npy".format(len(kappa_edges)-1)),0.5*(kappa_edges[1:]+kappa_edges[:-1]))
 	
-		if smoothing_scale>0:
+		if smoothing>0.:
 			conv = conv.smooth(smoothing*u.arcmin,kind="gaussianFFT")
 
 		if add_shape_noise:
@@ -105,7 +105,7 @@ def convergence_moments(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=Fals
 	try:
 		conv = ConvergenceMap.load(map_set.path(fname))
 	
-		if smoothing_scale>0:
+		if smoothing>0.:
 			conv = conv.smooth(smoothing*u.arcmin,kind="gaussianFFT")
 
 		if add_shape_noise:

### 2016-10-26 batchcode/scripts/measure_from_maps.py
fix paths in measure_cross_power

@@ -46,11 +46,11 @@ def convergence_power(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,
 ##############Measure the cross power#####################################################
 ##########################################################################################
 
-def cross_power(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=15,smoothing=0.0,cross="kappaGP"):
+def cross_powerGP(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=15,smoothing=0.0,cross="kappaGP",fnrep=("born_z","postBorn2-gp_z")):
 
 	try:
 		conv = ConvergenceMap.load(map_set.path(fname))
-		conv2 = ConvergenceMap.load(map_set.path(fname).replace(map_set.name,cross))
+		conv2 = ConvergenceMap.load(map_set.path(fname).replace(map_set.name,cross).replace(*fnrep))
 
 		if "0001r" in fname:
 			np.save(os.path.join(map_set.home_subdir,"num_ell_nb{0}.npy".format(len(l_edges)-1)),conv.countModes(l_edges))
@@ -69,6 +69,9 @@ def cross_power(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=1
 
 	except IOError:
 		return None
+
+def cross_powerLL(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=15,smoothing=0.0,cross="kappaLL",fnrep=("born_z","postBorn2-ll_z")):
+	return cross_powerGP(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=add_shape_noise,ngal=ngal,smoothing=smoothing,cross=cross,fnrep=fnrep)
 
 ##############################################################################
 ##############Peak counts#####################################################

### 2016-10-26 Paper/paper.tex
use seaborn for plotting
first results

@@
 \begin{equation}
-\kappa = \kappa^{\rm born} + \kappa^{\rm lens-lens} + \kappa^{\rm geodesic} + O(\Phi^3)
+\label{sim:pb2}
+\kappa = \kappa^{\rm born} + \kappa^{\rm ll} + \kappa^{\rm geo} + O(\Phi^3)
 \end{equation}
@@
 \label{sim:ll}
-\kappa^{\rm lens-lens}(\pt,\chi_s) = \int_0^{\chi_s}d\chi\int_0^\chi d\chi' \chi\chi' W(\chi,\chi_s)W(\chi',\chi_s)\Phi_{ij}(\chi\pt,\chi)\Phi_{ij}(\chi'\pt,\chi')
+\kappa^{\rm ll}(\pt,\chi_s) = \int_0^{\chi_s}d\chi\int_0^\chi d\chi' \chi\chi' W(\chi,\chi_s)W(\chi',\chi_s)\Phi_{ij}(\chi\pt,\chi)\Phi_{ij}(\chi'\pt,\chi')
 \end{equation}
@@
 \label{sim:gp}
-\kappa^{\rm geodesic}(\pt,\chi_s) = \frac{3H_0^2\Omega_m}{2c^2}\int_0^{\chi_s}d\chi\int_0^\chi d\chi' \frac{\chi\chi'}{a(\chi')} W(\chi,\chi_s)W(\chi',\chi_s)\nabla_\perp\Phi(\chi\pt,\chi)\cdot\nabla_\perp\delta(\chi'\pt,\chi')
+\kappa^{\rm geo}(\pt,\chi_s) = \frac{3H_0^2\Omega_m}{2c^2}\int_0^{\chi_s}d\chi\int_0^\chi d\chi' \frac{\chi\chi'}{a(\chi')} W(\chi,\chi_s)W(\chi',\chi_s)\nabla_\perp\Phi(\chi\pt,\chi)\cdot\nabla_\perp\delta(\chi'\pt,\chi')
 \end{equation}
@@
 This is true for upcoming large area surveys such as LSST \citep{LSST}, WFIRST \citep{WFIRST} and Euclid \citep{Euclid}.
-In this work we use $N$--body simulations coupled with the \ttt{LensTools} routines to simulate multiple realizations of a convergence field $\h{\kappa}(\pt)$ for different combinations of the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$.
+In this work we use $N$--body simulations coupled with the \ttt{LensTools} routines to simulate multiple realizations of a convergence field $\h{\kappa}(\pt)$ for different combinations of the cosmological parameter triplet $(\Omega_m,w_0,\sigma_8)$.
 We choose the values $\bbh{p}_0=(0.26,-1,0.8)$ as our fiducial cosmological parameters and vary one parameter at a time as in Table \ref{tab:cosmopar} to measure the feature derivatives $\bb{M}$.
@@
 \begin{tabular}{c|c|c|c}
-$\Omega_m$ & $w$ & $\sigma_8$ & $\kappa$ realizations \\ \hline \hline
+
+$\Omega_m$ & $w_0$ & $\sigma_8$ & $\kappa$ realizations \\ \hline \hline
 \multicolumn{4}{c}{\textbf{Fiducial}} \\ \hline
@@
 
-\multicolumn{4}{c}{\textbf{Variation 1}} \\ \hline
+\multicolumn{4}{c}{\textbf{Variations}} \\ \hline
 0.29 & -1 & 0.8 & 1024 \\
@@
 0.26 & -1 & 0.9 & 1024 \\ \hline
-
-\multicolumn{4}{c}{\textbf{Variation 2}} \\ \hline
-0.23 & -1 & 0.8 & 1024 \\
-0.26 & -1.2 & 0.8 & 1024 \\
-0.26 & -1 & 0.7 & 1024 \\ \hline
 
@@
 \pmb{\mu}_2 = \left(\langle\kappa^2\rangle,\langle\vert\nabla\kappa\vert^2\rangle\right) \\ \\
-\pmb{\mu}_3 = \left(\langle\kappa^3\rangle,\langle\kappa^2\nabla^2\kappa\rangle,\langle\kappa\vert\nabla\kappa\vert^2\rangle\right) \\ \\
-\pmb{\mu}_4 = \left(\langle\kappa^4\rangle_c,\langle\kappa^3\nabla^2\kappa\rangle_c,\langle\kappa^2\vert\nabla\kappa\vert^2\rangle_c,\langle\vert\nabla\kappa\vert^4\rangle_c\right) \\
+\pmb{\mu}_3 = \left(\langle\kappa^3\rangle,\langle\kappa^2\nabla^2\kappa\rangle,\langle\vert\nabla\kappa\vert^2\nabla^2\kappa\rangle\right) \\ \\
+\pmb{\mu}_4 = \left(\langle\kappa^4\rangle_c,\langle\kappa^3\nabla^2\kappa\rangle_c,\langle\kappa\vert\nabla\kappa\vert^2\nabla^2\kappa\rangle_c,\langle\vert\nabla\kappa\vert^4\rangle_c\right) \\
 \end{matrix}
@@
 % 
+In this section we presents the results of this work, regarding the WL feature forward model accuracy and the cosmological parameter bias induced by the Born approximation.
 
@@
 
+In this paragraph we compare the accuracy of the Born approximation in predicting WL image features, in particular we focus on the $\kappa$ power spectrum and the 9 moments described in equation (\ref{par:moments}).
+Figure \ref{fig:psResiduals} shows the auto power spectra of $\kappa^{\rm born},\kappa^{\rm lens-lens},\kappa^{\rm geodesic}$ as defined in equation (\ref{sim:pb2}).
+At lowest order the lensing potential contributes to the $\kappa$ power spectrum quadratically.
+The first post--Born correction to $P^{\kappa\kappa}$ comes to $O(\Phi^3)$ and is given by
+\begin{equation}
+\label{res:powercorr}
+P^{\kappa\kappa} = P^{\kappa\kappa}_{\rm born,born} + 2P^{\kappa\kappa}_{\rm born,ll} + 2P^{\kappa\kappa}_{\rm born,geo} + O(\Phi^4)
+\end{equation}
+%
+Where we defined the $\kappa$ cross spectra as
+\begin{equation}
+\label{res:powercross}
+\langle\tilde{\kappa}^{a}(\pmb{\ell})\tilde{\kappa}^{b,*}(\pmb{\ell}')\rangle = (2\pi)^2\delta^D(\pmb{\ell}+\pmb{\ell}')P_{a,b}^{\kappa\kappa}(\ell)
+\end{equation} 
+%
+Figure \ref{fig:psResiduals} shows the magnitudes of the $O(\Phi^3)$ post--Born corrections to the convergence power spectrum.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.3]{Figures/powerResiduals.eps}
+\end{center}
+\caption{Power spectrum residuals}
+\label{fig:psResiduals}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.25]{Figures/pdfMoments.eps}
+\end{center}
+\caption{PDF of $\kappa$ moments}
+\label{fig:pdfMoments}
+\end{figure*}
+
 \subsection{Parameter bias}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.25]{Figures/bias_convergence_power_s0_nb100.eps}
+\includegraphics[scale=0.25]{Figures/bias_convergence_moments_s0_nb9.eps}
+\includegraphics[scale=0.25]{Figures/bias_convergence_momentsSN_s0_nb9.eps}
+\end{center}
+\caption{Parameter bias}
+\label{fig:parbias}
+\end{figure*}
 

### 2016-10-26 Paper/Figures/generate.py

@@ -69,8 +69,8 @@ def convergenceVisualize(cmd_args,smooth=0.5*u.arcmin,fontsize=22):
 	#Titles
 	ax[0,0].set_title(r"$\kappa$",fontsize=fontsize)
 	ax[0,1].set_title(r"$\kappa-\kappa^{\rm born}$",fontsize=fontsize)
-	ax[1,0].set_title(r"$\kappa^{\rm lens-lens}$",fontsize=fontsize)
-	ax[1,1].set_title(r"$\kappa^{\rm geodesic}$",fontsize=fontsize)
+	ax[1,0].set_title(r"$\kappa^{\rm ll}$",fontsize=fontsize)
+	ax[1,1].set_title(r"$\kappa^{\rm geo}$",fontsize=fontsize)
 
 	#Switch off grids
 	for i in (0,1):
@@ -84,7 +84,48 @@ def convergenceVisualize(cmd_args,smooth=0.5*u.arcmin,fontsize=22):
 ###################################################################################################
 ###################################################################################################
 
-def pbBias(cmd_args,feature_name="convergence_power_s0_nb100",kappa_models=("Born",),callback=None,variation_idx=(0,1),bootstrap_size=100,resample=1000,fontsize=22):
+def powerResiduals(cmd_args,fontsize=22):
+
+	#Initialize plot
+	fig,ax = plt.subplots(1,2,figsize=(16,8))
+
+	#Load data
+	ell = np.load(os.path.join(batch.home,"ell_nb100.npy"))
+	pFull = np.load(os.path.join(fiducial["c0"].getMapSet("kappa").home,"convergence_power_s0_nb100.npy"))
+	pBorn = np.load(os.path.join(fiducial["c0"].getMapSet("kappaBorn").home,"convergence_power_s0_nb100.npy"))
+	pLL = np.load(os.path.join(fiducial["c0"].getMapSet("kappaLL").home,"convergence_power_s0_nb100.npy"))
+	pLL_cross = np.load(os.path.join(fiducial["c0"].getMapSet("kappaBorn").home,"cross_powerLL_s0_nb100.npy"))
+	pGP = np.load(os.path.join(fiducial["c0"].getMapSet("kappaGP").home,"convergence_power_s0_nb100.npy"))
[…]

### 2016-10-27 Paper/Figures/generate.py
finished first draft

@@ -102,9 +102,9 @@ def powerResiduals(cmd_args,fontsize=22):
 	ax[0].plot(ell,ell*(ell+1)*pBorn.mean(0)/(2.*np.pi),label="born")
 	ax[0].plot(ell,ell*(ell+1)*pGP.mean(0)/(2.*np.pi),label="geodesic")
 	ax[0].plot(ell,ell*(ell+1)*pLL.mean(0)/(2.*np.pi),label="lens-lens")
-	ax[1].plot(ell,(np.abs(pFull.mean(0)-pBorn.mean(0))),label=r"${\rm ray-born}$")
-	ax[1].plot(ell,2*np.abs(pGP_cross.mean(0)),label=r"$2{\rm born}\times{\rm geo}$")
-	ax[1].plot(ell,2*np.abs(pLL_cross.mean(0)),label=r"$2{\rm born}\times{\rm ll}$")
+	ax[1].plot(ell,ell*(ell+1)*(np.abs(pFull.mean(0)-pBorn.mean(0)))/(2.0*np.pi),label=r"${\rm ray-born}$")
+	ax[1].plot(ell,ell*(ell+1)*np.abs(pGP_cross.mean(0))/np.pi,label=r"$2{\rm born}\times{\rm geo}$")
+	ax[1].plot(ell,ell*(ell+1)*np.abs(pLL_cross.mean(0))/np.pi,label=r"$2{\rm born}\times{\rm ll}$")
 
 	#Labels
 	for n in (0,1):
@@ -116,7 +116,7 @@ def powerResiduals(cmd_args,fontsize=22):
 		ax[n].set_xlabel(r"$\ell$",fontsize=fontsize)
 	
 	ax[0].set_ylabel(r"$\ell(\ell+1)P^{\kappa\kappa}(\ell)/2\pi$",fontsize=fontsize)
-	ax[1].set_ylabel(r"${\rm abs(residuals)}$")
+	ax[1].set_ylabel(r"$\ell(\ell+1){\rm abs(residuals)/2\pi}$")
 
 	#Save
 	fig.tight_layout()
@@ -125,7 +125,7 @@ def powerResiduals(cmd_args,fontsize=22):
 ###################################################################################################
 ###################################################################################################
 
-def pbBias(cmd_args,feature_name="convergence_power_s0_nb100",kappa_models=("Born",),callback=None,variation_idx=(0,),bootstrap_size=100,resample=1000,fontsize=22):
[…]

### 2016-10-28 Paper/paper.tex

@@
 A cheaper but less accurate procedure based on the Born approximation, on the other hand, requires knowledge of the density only and can be implemented more efficiently and at lower computational cost.
-In this work we show that geodesic perturbations are the dominant cause of inaccuracy in the Born approximation, lens-lens couplings being negligible.
-We also show that, although the Born approximation does not accurately predict WL convergence moments in the noiseless case, once galaxy shape noise is added the loss of accuracy is negligible even for a LSST--like survey.
+In this work we show that geodesic perturbations are the dominant correction to the Born approximation, lens-lens couplings being negligible.
+We also show that, although the Born approximation does not accurately predict WL convergence moments in the noiseless case, once galaxy shape noise is added the loss of accuracy is negligible even for a LSST--like survey, due to the increased statistical errors.
 \end{abstract}
@@
 % 
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.3]{Figures/powerResiduals.eps}
+\end{center}
+\caption{Contributions of different $\Phi$ orders to the $\kappa$ power spectrum: the left panel shows the auto power spectra $P_{\rm born,born}$ ($O(\Phi^2)$) and $P_{\rm ll},P_{\rm geo}$ ($O(\Phi^4)$).
+The right panel shows the residuals between the power spectrum of the full ray--traced $\kappa$ field and the one obtained with the Born approximation.
+The residuals are compared to the two $O(\Phi^3)$ terms $2P_{\rm born,ll},2P_{\rm born,geo}$.
+The quantities shown are the averages over 1024 realizations of $\kappa$ in the fiducial cosmology $\bb{p}_0$.}
+\label{fig:psResiduals}
+\end{figure*}
+%
+We also studied the accuracy of the Born approximation in predicting the 9 higher order convergence moments defined in (\ref{par:moments}). The results are shown in Figure \ref{fig:pdfMoments}.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.25]{Figures/pdfMoments.eps}
+\end{center}
+\caption{Probability distribution function (PDF) of the 9 $\kappa$ moments defined in (\ref{par:moments}), over 8192 realizations of the fiducial cosmological model $\bb{p}_0$.
+We show both the PDFs obtained with full ray--tracing (blue) and the Born approximation (green).
+No shape noise has been added.
+The $\kappa$ maps were smoothed with a Gaussian kernel of size $\theta_G=0.5\,{\rm arcmin}$ before measuring the moments.}
+\label{fig:pdfMoments}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.25]{Figures/bias_convergence_power_s0_nb100.eps}
+\includegraphics[scale=0.25]{Figures/bias_convergence_moments_s0_nb9.eps}
+\includegraphics[scale=0.25]{Figures/bias_convergence_momentsSN_s0_nb9.eps}
+\end{center}
+\caption{Distribution of the parameter estimator (\ref{par:fisherest}) over 1000 realizations of an LSST--like survey.
+We show parameter estimates obtained using the noiseless $\kappa$ power spectrum (top panel), the noiseless $\kappa$ moments defined in (\ref{par:moments}) (middle panel) and the noisy $\kappa$ moments, based on a galaxy density of $15\,{\rm arcmin}^{-2}$ (bottom panel).
+We show both a control case, in which the observation has been constructed with the Born approximation (blue), and the real case, in which the observation has been constructed with full ray--tracing (green).}
+\label{fig:parbias}
+\end{figure*}
+
+\subsection{Parameter bias}
+When using forward models based on the Born approximation to fit observations, parameter biases may occur if the forward model is not accurate enough.
+We studied if this is the case by simulating 1000 LSST--like observations in which the convergence field $\kappa(\pt)$ is constructed using the full ray--tracing procedure.
+We used the Born approximation to fit these mock observations using the Fisher parameter estimator in (\ref{par:fisherest}).
+The results are shown in Figure \ref{fig:parbias}.
+
 In this section we presents the results of this work, regarding the WL feature forward model accuracy and the cosmological parameter bias induced by the Born approximation.
@@
 In this paragraph we compare the accuracy of the Born approximation in predicting WL image features, in particular we focus on the $\kappa$ power spectrum and the 9 moments described in equation (\ref{par:moments}).
-Figure \ref{fig:psResiduals} shows the auto power spectra of $\kappa^{\rm born},\kappa^{\rm lens-lens},\kappa^{\rm geodesic}$ as defined in equation (\ref{sim:pb2}).
+Figure \ref{fig:psResiduals} shows the auto power spectra of $\kappa^{\rm born},\kappa^{\rm ll},\kappa^{\rm geo}$ as defined in equation (\ref{sim:pb2}).
 At lowest order the lensing potential contributes to the $\kappa$ power spectrum quadratically.
@@
 
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=0.3]{Figures/powerResiduals.eps}
-\end{center}
-\caption{Power spectrum residuals}
-\label{fig:psResiduals}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=0.25]{Figures/pdfMoments.eps}
-\end{center}
-\caption{PDF of $\kappa$ moments}
-\label{fig:pdfMoments}
-\end{figure*}
-
-\subsection{Parameter bias}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=0.25]{Figures/bias_convergence_power_s0_nb100.eps}
-\includegraphics[scale=0.25]{Figures/bias_convergence_moments_s0_nb9.eps}
-\includegraphics[scale=0.25]{Figures/bias_convergence_momentsSN_s0_nb9.eps}
-\end{center}
-\caption{Parameter bias}
-\label{fig:parbias}
-\end{figure*}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%% DISCUSSION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % 
+In this section we discuss our main findings.
+Figure \ref{fig:csample} shows that the dominant post--Born correction to the $\kappa$ reconstruction comes from the geodesic term (\ref{sim:gp}).
+This can be shown both looking at the lens-lens term, which is one order of magnitude smaller than the geodesic term, and looking at the $\kappa-\kappa^{\rm born}$ residuals, which show similar structure to the ones found in the $\kappa^{\rm geo}$ map.
+
+Figure \ref{fig:psResiduals} shows a comparison between the Born approximated $\kappa$ power spectra and the ones obtained with full ray--tracing, separating different orders in $\Phi$.
+We can conclude that the dominant contributions to the residuals come from the Born--geodesic cross power, which dominates the Born--lens--lens cross power by two orders of magnitude on small scales.
+Figure \ref{fig:psResiduals} also gives indications that the perturbation series in powers of $\Phi$ becomes asymptotic on small angular scales as the higher orders $O(\Phi^4)$ tend to dominate the leading orders.
+This is likely due to the non--linearity of the density contrast on small scales.
+
+Figure \ref{fig:pdfMoments} shows the PDF of the 9 $\kappa$ moments defined in (\ref{par:moments}) over 1000 realizations of an LSST--like survey.
+The plot clearly shows that, while the Born approximation is a good predictor of the quadratic moments $\pmb{\mu}_2$ within one standard deviation, the higher moments $\pmb{\mu}_3,\pmb{\mu}_4$ show $2\div 3\sigma$ deviations from their Born approximated counterparts.
+This can lead to parameter biases when fitting observations.
+Figure \ref{fig:parbias} studies this possibility and shows that, while the Born approximation is sufficient to fit cosmology with the power spectrum of an LSST--like survey, even in the noiseless case, the same is not true for the higher $\kappa$ moments.
+The middle panel of Figure \ref{fig:parbias} show that high significance biases are observed when fitting a real observation with Born approximated $\kappa$ moments.
+The bias however disappears when introducing galaxy shape noise, due to the resulting increased statistical error.
 
@@
 \section{Conclusions}
+In this work we studied the effectiveness of the Born approximation in predicting Weak Lensing observables, and studied the approximation effects on parameter constraints.
+Our main findings can be summarized in the following points:
+
+\begin{itemize}
+\item The main corrections to the Born approximations come from the perturbations in the light ray geodesic, with lens--lens coupling being at least one order of magnitude sub leading
+\item The $\kappa$ power spectrum leads to negligible parameter bias for an LSST--like survey, even in the noiseless case
+\item Fitting an observation with Born approximated higher $\kappa$ moments leads to high significance bias in the $(\Omega_m,w_0,\sigma_8)$ in the noiseless case.
+The bias significance becomes negligible when galaxy shape noise is added due to an increased scatter in parameter estimates.
+\end{itemize}
 %
+Future prospects involve study the Born approximation validity for CMB lensing observations.
 
@@
 \section*{Acknowledgments}
+We thank Uros Seljak for useful discussions.
+The $N$--body simulations in this work were performed at National Energy Research Scientific Computing Center (NERSC).
+We thank the LSST Dark Energy Science Collaboration (DESC) for the allocation of time.
+The ray--tracing simulations and parameter estimation calculations were performed at the NSF XSEDE facility, supported by grant number
+ACI-1053575, and at the New York Center for Computational Sciences, a
+cooperative effort between Brookhaven National Laboratory and Stony
+Brook University, supported in part by the State of New York. This
+work was supported in part by the U.S. Department of Energy under
+Contract No. DE-SC00112704, and by the NSF Grant
+No. AST-1210877 (to Z.H.) and by the Research Opportunities and
+Approaches to Data Science (ROADS) program at the Institute for Data
+Sciences and Engineering at Columbia University (to Z.H.).
 

### 2016-10-28 Paper/Figures/generate.py
switch order of smoothing and shape noise

@@ -108,7 +108,7 @@ def powerResiduals(cmd_args,fontsize=22):
 
 	#Labels
 	for n in (0,1):
-		ax[n].legend(loc="upper left",prop={"size":13})
+		ax[n].legend(loc="upper left",prop={"size":15})
 
 	for n in (0,1):
 		ax[n].set_xscale("log")
@@ -239,6 +239,10 @@ def pbBiasKurtSN(cmd_args,feature_name="convergence_kurtSN_s0_nb9"):
 	callback = lambda f:np.load(f.replace("kurt","moments"))[:,5:]
 	pbBias(cmd_args,feature_name=feature_name,callback=callback)
 
+def pbBiasPeaks(cmd_args,feature_name="convergence_peaks_s50_nb100"):
+	callback = None
+	pbBias(cmd_args,feature_name=feature_name,callback=callback)
+
 ####################################################################################################################
 ####################################################################################################################
 
@@ -331,6 +335,7 @@ method["3"] = pdfMoments
 method["4"] = pbBiasPower
 method["4b"] = pbBiasMoments
 method["4c"] = pbBiasMomentsSN
+method["5"] = pbBiasPeaks
 
 #Main
 def main():

### 2016-10-28 batchcode/scripts/measure_from_maps.py

@@ -29,12 +29,12 @@ def convergence_power(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,
 		if "0001r" in fname:
 			np.save(os.path.join(map_set.home_subdir,"num_ell_nb{0}.npy".format(len(l_edges)-1)),conv.countModes(l_edges))
 	
-		if smoothing>0.:
-			conv = conv.smooth(smoothing*u.arcmin,kind="gaussianFFT")
-
 		if add_shape_noise:
 			gen = GaussianNoiseGenerator.forMap(conv)
 			conv = conv + gen.getShapeNoise(z=z,ngal=ngal*(u.arcmin**-2),seed=hash(os.path.basename(fname))%4294967295)
+
+		if smoothing>0.:
+			conv = conv.smooth(smoothing*u.arcmin,kind="gaussianFFT")
 
 		l,Pl = conv.powerSpectrum(l_edges)
 		return Pl
@@ -55,14 +55,14 @@ def cross_powerGP(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal
 		if "0001r" in fname:
 			np.save(os.path.join(map_set.home_subdir,"num_ell_nb{0}.npy".format(len(l_edges)-1)),conv.countModes(l_edges))
 	
-		if smoothing>0.:
-			conv = conv.smooth(smoothing*u.arcmin,kind="gaussianFFT")
-			conv2 = conv2.smooth(smoothing*u.arcmin,kind="gaussianFFT")
-
 		if add_shape_noise:
 			gen = GaussianNoiseGenerator.forMap(conv)
 			conv = conv + gen.getShapeNoise(z=z,ngal=ngal*(u.arcmin**-2),seed=hash(os.path.basename(fname))%4294967295)
 			conv2 = conv2 + gen.getShapeNoise(z=z,ngal=ngal*(u.arcmin**-2),seed=hash(os.path.basename(fname))%4294967295)
+
+		if smoothing>0.:
+			conv = conv.smooth(smoothing*u.arcmin,kind="gaussianFFT")
+			conv2 = conv2.smooth(smoothing*u.arcmin,kind="gaussianFFT")
 
 		l,Pl = conv.cross(conv2,l_edges=l_edges)
 		return Pl
@@ -85,12 +85,12 @@ def convergence_peaks(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,
 		if "0001r" in fname:
[…]

### 2016-10-31 Paper/Figures/generate.py
routine for plotting skew(thetaG)

@@ -322,6 +322,38 @@ def pdfMoments(cmd_args,kappa_models=("kappa","kappaBorn"),figname="pdfMoments",
 
 ####################################################################################################################
 
+def plotSmooth(cmd_args,reference="kappaBorn",variations=("kappa","kappaB+GP","kappaB+LL"),moment_index=2,smooth=(0.5,1.0,2.0),fontsize=22):
+
+	#Model labels
+	labels = {"kappaBorn":"born","kappa":"full","kappaB+GP":"geodesic","kappaB+LL":"lens-lens"}
+
+	#Set up plot
+	fig,ax = plt.subplots()
+
+	#Load data
+	moments = dict()
+	for l in (reference,)+variations:
+		moments[l] = list()
+
+	for s in smooth:
+		for l in (reference,)+variations:
+			samples = np.load(os.path.join(fiducial["c0"].getMapSet(l).home,"convergence_moments_s{0}_nb9.npy".format(int(smooth*100))))
+			moments[l].append(samples[:,moment_index].mean(0))
+
+	#Plot
+	for v in variations:
+		ax.plot(smooth,moments[v]/moments[reference]-1.0,label=labels[v])
+
+	#Labels
+	ax.set_xlabel(r"$\theta_G({\rm} arcmin)$",fontsize=fontsize)
+	ax.set_ylabel(r"$\langle\delta\kappa^3\rangle/\langle\kappa^3\rangle$",fontsize=fontsize)
+	ax.legend()
+
+	#Save
+	fig.savefig("delta_moment{0}.{1}".format(moment_index,cmd_args.type))
+
+####################################################################################################################
+
 ###################################################################################################
 ###################################################################################################
 ###################################################################################################

### 2016-11-01 batchcode/scripts/measure_from_maps.py
command line option parsing

@@ -4,6 +4,7 @@ from __future__ import division
 import sys,os,glob
 import logging
 import json
+import argparse
 
 from lenstools.image.convergence import ConvergenceMap
 from lenstools.image.noise import GaussianNoiseGenerator
@@ -129,12 +130,23 @@ def convergence_moments(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=Fals
 
 if __name__=="__main__":
 
+	#Command line argiments
+	parser = argparse.ArgumentParser()
+	parser.add_argument("-c","--config",dest="config",action="store",default=None,help="config file")
+	parser.add_argument("-s","--smooth",dest="smooth",action="store",type=float,default=None,help="smoothing scale in arcmin")
+	cmd_args = parser.parse_args()
+
+	#Make sure config is provided
+	if cmd_args.config is None:
+		parser.print_help()
+		sys.exit(1)
+
 	#Globals
 	logging.basicConfig(level=logging.INFO)
 	measurers = globals()
 
 	#Read options from json config file
-	with open(sys.argv[1],"r") as fp:
+	with open(cmd_args.config,"r") as fp:
 		options = json.load(fp)
 
 	#Initialize MPIPool
@@ -157,6 +169,8 @@ if __name__=="__main__":
 
 	#Smoothing
 	smoothing = options["smoothing"]
+	if cmd_args.smooth is not None:
+		smoothing = cmd_args.smooth
 
 	#Savename
 	savename = options["method"]
@@ -191,10 +205,10 @@ if __name__=="__main__":
 	
 	#####################################################################################################################
 
-	for model in batch.models:
+	for model in [ batch.getModel("Om0.260_Ode0.740_w-1.000_wa0.000_si0.800") ]:
 
 		#Perform the measurements for all the map sets
-		for map_set in model["c0"].mapsets:
+		for map_set in [ model["c0"].getMapSet("kappa"),model["c0"].getMapSet("kappaBorn"),model["c0"].getMapSet("kappaB+LL"),model["c0"].getMapSet("kappaB+GP") ]:
 
 			#Log to user
 			logging.info("Processing model {0}, map set {1}".format(map_set.cosmo_id,map_set.settings.directory_name))

### 2016-11-01 batchcode/scripts/measure_from_maps.py
specify mapsets to process in a config file

@@ -134,10 +134,11 @@ if __name__=="__main__":
 	parser = argparse.ArgumentParser()
 	parser.add_argument("-c","--config",dest="config",action="store",default=None,help="config file")
 	parser.add_argument("-s","--smooth",dest="smooth",action="store",type=float,default=None,help="smoothing scale in arcmin")
+	parser.add_argument("-m","--maps",dest="maps",action="store",default=None,help="map sets file")
 	cmd_args = parser.parse_args()
 
 	#Make sure config is provided
-	if cmd_args.config is None:
+	if (cmd_args.config is None) or (cmd_args.maps is None):
 		parser.print_help()
 		sys.exit(1)
 
@@ -148,6 +149,10 @@ if __name__=="__main__":
 	#Read options from json config file
 	with open(cmd_args.config,"r") as fp:
 		options = json.load(fp)
+
+	#Read the json map sets file
+	with open(cmd_args.maps,"r") as fp:
+		maps = json.load(fp)
 
 	#Initialize MPIPool
 	try:
@@ -205,10 +210,14 @@ if __name__=="__main__":
 	
 	#####################################################################################################################
 
-	for model in [ batch.getModel("Om0.260_Ode0.740_w-1.000_wa0.000_si0.800") ]:
+	for cosmo_id in maps:
+
+		model = batch.getModel(cosmo_id)
 
 		#Perform the measurements for all the map sets
-		for map_set in [ model["c0"].getMapSet("kappa"),model["c0"].getMapSet("kappaBorn"),model["c0"].getMapSet("kappaB+LL"),model["c0"].getMapSet("kappaB+GP") ]:
+		for ms in maps[cosmo_id]:
+
+			map_set = model["c0"].getMapSet(ms)
 
 			#Log to user
 			logging.info("Processing model {0}, map set {1}".format(map_set.cosmo_id,map_set.settings.directory_name))

### 2016-11-01 batchcode/scripts/measure_from_maps.py
measure cross skewness

@@ -124,6 +124,37 @@ def convergence_moments(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=Fals
 	except IOError:
 		return None
 
+def skew_crossGP(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=15,smoothing=0.0,cross="kappaGP",fnrep=("born_z","postBorn2-gp_z")):
+
+	try:
+		conv = ConvergenceMap.load(map_set.path(fname))
+		conv2 = ConvergenceMap.load(map_set.path(fname).replace(map_set.name,cross).replace(*fnrep))
+
+		if "0001r" in fname:
+			np.save(os.path.join(map_set.home_subdir,"num_ell_nb{0}.npy".format(len(l_edges)-1)),conv.countModes(l_edges))
+	
+		if add_shape_noise:
+			gen = GaussianNoiseGenerator.forMap(conv)
+			conv = conv + gen.getShapeNoise(z=z,ngal=ngal*(u.arcmin**-2),seed=hash(os.path.basename(fname))%4294967295)
+			conv2 = conv2 + gen.getShapeNoise(z=z,ngal=ngal*(u.arcmin**-2),seed=hash(os.path.basename(fname))%4294967295)
+
+		if smoothing>0.:
+			conv = conv.smooth(smoothing*u.arcmin,kind="gaussianFFT")
+			conv2 = conv2.smooth(smoothing*u.arcmin,kind="gaussianFFT")
+
+		#Subtract mean
+		conv.data -= conv.data.mean()
+		conv2.data -= conv2.data.mean()
+
+		#Measure cross skewness
+		return np.array([(3*(conv.data**2)*(conv2.data)).mean()])
+
+	except IOError:
+		return None
+
+def skew_crossLL(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=15,smoothing=0.0,cross="kappaLL",fnrep=("born_z","postBorn2-ll_z")):
+	return skew_crossGP(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=add_shape_noise,ngal=ngal,smoothing=smoothing,cross=cross,fnrep=fnrep)
+
 #################################################################################
 ##############Main execution#####################################################
 #################################################################################

### 2016-11-01 batchcode/scripts/measure_from_maps.py
rename

@@ -124,7 +124,7 @@ def convergence_moments(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=Fals
 	except IOError:
 		return None
 
-def skew_crossGP(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=15,smoothing=0.0,cross="kappaGP",fnrep=("born_z","postBorn2-gp_z")):
+def cross_skewGP(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=15,smoothing=0.0,cross="kappaGP",fnrep=("born_z","postBorn2-gp_z")):
 
 	try:
 		conv = ConvergenceMap.load(map_set.path(fname))
@@ -152,8 +152,8 @@ def skew_crossGP(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=
 	except IOError:
 		return None
 
-def skew_crossLL(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=15,smoothing=0.0,cross="kappaLL",fnrep=("born_z","postBorn2-ll_z")):
-	return skew_crossGP(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=add_shape_noise,ngal=ngal,smoothing=smoothing,cross=cross,fnrep=fnrep)
+def cross_skewLL(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=15,smoothing=0.0,cross="kappaLL",fnrep=("born_z","postBorn2-ll_z")):
+	return cross_skewGP(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=add_shape_noise,ngal=ngal,smoothing=smoothing,cross=cross,fnrep=fnrep)
 
 #################################################################################
 ##############Main execution#####################################################

### 2016-11-02 batchcode/scripts/measure_from_maps.py
measre cross kurtosis

@@ -129,9 +129,6 @@ def cross_skewGP(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=
 	try:
 		conv = ConvergenceMap.load(map_set.path(fname))
 		conv2 = ConvergenceMap.load(map_set.path(fname).replace(map_set.name,cross).replace(*fnrep))
-
-		if "0001r" in fname:
-			np.save(os.path.join(map_set.home_subdir,"num_ell_nb{0}.npy".format(len(l_edges)-1)),conv.countModes(l_edges))
 	
 		if add_shape_noise:
 			gen = GaussianNoiseGenerator.forMap(conv)
@@ -154,6 +151,35 @@ def cross_skewGP(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=
 
 def cross_skewLL(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=15,smoothing=0.0,cross="kappaLL",fnrep=("born_z","postBorn2-ll_z")):
 	return cross_skewGP(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=add_shape_noise,ngal=ngal,smoothing=smoothing,cross=cross,fnrep=fnrep)
+
+def cross_kurtGP(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=15,smoothing=0.0,cross="kappaGP",fnrep=("born_z","postBorn2-gp_z")):
+
+	try:
+		conv = ConvergenceMap.load(map_set.path(fname))
+		conv2 = ConvergenceMap.load(map_set.path(fname).replace(map_set.name,cross).replace(*fnrep))
+	
+		if add_shape_noise:
+			gen = GaussianNoiseGenerator.forMap(conv)
+			conv = conv + gen.getShapeNoise(z=z,ngal=ngal*(u.arcmin**-2),seed=hash(os.path.basename(fname))%4294967295)
+			conv2 = conv2 + gen.getShapeNoise(z=z,ngal=ngal*(u.arcmin**-2),seed=hash(os.path.basename(fname))%4294967295)
+
+		if smoothing>0.:
+			conv = conv.smooth(smoothing*u.arcmin,kind="gaussianFFT")
+			conv2 = conv2.smooth(smoothing*u.arcmin,kind="gaussianFFT")
+
+		#Subtract mean
+		conv.data -= conv.data.mean()
+		conv2.data -= conv2.data.mean()
+
+		#Measure connected cross kurtosis
[…]

### 2016-11-02 batchcode/scripts/measure_from_maps.py
fix typo

@@ -173,7 +173,7 @@ def cross_kurtGP(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=
 
 		#Measure connected cross kurtosis
 		kurt = 4*((conv.data**3)*conv2.data).mean() - 12*((conv.data**2).mean())*(conv.data*conv2.data).mean()
-		return np.array([(3*(conv.data**2)*(conv2.data)).mean()])
+		return np.array([kurt])
 
 	except IOError:
 		return None

### 2016-11-02 Paper/paper.tex
switch order of smoothing and shape noise
routine for plotting skew(thetaG)
finished second version of the draft

@@
 A cheaper but less accurate procedure based on the Born approximation, on the other hand, requires knowledge of the density only and can be implemented more efficiently and at lower computational cost.
-In this work we show that geodesic perturbations are the dominant correction to the Born approximation, lens-lens couplings being negligible.
-We also show that, although the Born approximation does not accurately predict WL convergence moments in the noiseless case, once galaxy shape noise is added the loss of accuracy is negligible even for a LSST--like survey, due to the increased statistical errors.
+In this work we show that the deviations of the Born--approximated convergence power spectrum, skewness and kurtosis from the ray--traced ones are consistent with the smallest non trivial post--Born corrections.
+We also show that perturbative approaches to the post--Born corrections break down at higher orders, making full ray--tracing more reliable.
+Because we find that cosmological parameter biases induced by the Born approximation are negligible even for an LSST--like survey once galaxy shape noise is considered, we argue that the Born approximation is preferred for future analysis.
+Using the \ttt{LensTools} software suite, we show that the Born approximation saves a factor of 4 in computing time with respect to the full ray--tracing in reconstructing the convergence.
 \end{abstract}
@@
 %
-The implicit form of equation (\ref{sim:jacsol}) suggests a straightforward way to solve the geodesic equation numerically because $A(\pt,\chi_s)$ can be expressed once one knows $A(\pt,\chi)$ for $\chi<\chi_s$.
+The implicit form of equation (\ref{sim:jacsol}) suggests a straightforward way to solve the geodesic equation numerically because $A(\pt,\chi_s)$ can be calculated once $A(\pt,\chi)$ for $\chi<\chi_s$ is known.
 The multi--lens--plane algorithm \citep{RayTracingJain,RayTracingHartlap} is a popular method to compute the integral in (\ref{sim:jacsol}) in discrete steps (lenses) by keeping track of the intermediate values $A(\pt,\chi)$ using dynamic programming.
@@
 \label{sim:born}
-\kappa^{\rm born}(\pt,\chi_s) = \frac{3H_0^2\Omega_m}{2c^2}\int_0^{\chi_s} d\chi\frac{\chi}{a(\chi)} W(\chi,\chi_s)\delta(\chi\pt,\chi)
+\kappa_{\rm born}(\pt,\chi_s) = \frac{3H_0^2\Omega_m}{2c^2}\int_0^{\chi_s} d\chi\frac{\chi}{a(\chi)} W(\chi,\chi_s)\delta(\chi\pt,\chi)
 \end{equation}
@@
 \label{sim:pb2}
-\kappa = \kappa^{\rm born} + \kappa^{\rm ll} + \kappa^{\rm geo} + O(\Phi^3)
+\kappa = \kappa_{\rm born} + \kappa_{\rm ll} + \kappa_{\rm geo} + O(\Phi^3)
 \end{equation}
@@
 \label{sim:ll}
-\kappa^{\rm ll}(\pt,\chi_s) = \int_0^{\chi_s}d\chi\int_0^\chi d\chi' \chi\chi' W(\chi,\chi_s)W(\chi',\chi_s)\Phi_{ij}(\chi\pt,\chi)\Phi_{ij}(\chi'\pt,\chi')
+\kappa_{\rm ll}(\pt,\chi_s) = \int_0^{\chi_s}d\chi\int_0^\chi d\chi' \chi\chi' W(\chi,\chi_s)W(\chi',\chi)\Phi_{ij}(\chi\pt,\chi)\Phi_{ij}(\chi'\pt,\chi')
 \end{equation}
@@
 \label{sim:gp}
-\kappa^{\rm geo}(\pt,\chi_s) = \frac{3H_0^2\Omega_m}{2c^2}\int_0^{\chi_s}d\chi\int_0^\chi d\chi' \frac{\chi\chi'}{a(\chi')} W(\chi,\chi_s)W(\chi',\chi_s)\nabla_\perp\Phi(\chi\pt,\chi)\cdot\nabla_\perp\delta(\chi'\pt,\chi')
+\kappa_{\rm geo}(\pt,\chi_s) = \frac{3H_0^2\Omega_m}{2c^2}\int_0^{\chi_s}d\chi\int_0^\chi d\chi' \frac{\chi\chi'}{a(\chi')} W(\chi,\chi_s)W(\chi',\chi)\nabla_\perp\Phi(\chi\pt,\chi)\cdot\nabla_\perp\delta(\chi'\pt,\chi')
 \end{equation}
@@
 A sample of the simulation outputs is shown in Figure \ref{fig:csample}.
+Benchmarks for the runtime of the ray--tracing and line--of--sight integrals operations, performed with \ttt{LensTools}, are provided in Table \ref{tab:benchmarks}.
 In the next section we show how to infer cosmological parameters from WL features forward models applied to observations.
+
+\begin{table*}
+\begin{center}
+
+\begin{tabular}{c|c|c|c}
+
+\textbf{Integration type} & \textbf{Runtime (One field of view)} & \textbf{Memory usage} & \textbf{CPU time (1000 fields of view)} \\ \hline \hline
+Born & 36.0\,s & 0.86\,GB & 10\,hours  \\
+Full ray--tracing & 124.8\,s & 1.65\,GB & 35\,hours  \\
+Born + $O(\Phi^2)$ & 156.7\,s & 1.52\,GB & 44\,hours \\ \hline
+
+\end{tabular}
+
+\end{center}
+
+\caption{Time and memory usage benchmarks for the convergence reconstruction operations.
+The test case we considered consists in a discretization with 42 uniformly spaced lenses between the observer and the sources at $z_s=2$, each with a resolution of $4096^2$ pixels.
+The $\kappa$ field is resolved with $2048^2$ light rays.
+We show both the runtime for producing a single field of view and the CPU hours needed to perform the reconstruction 1000 times, to mock an LSST--like galaxy survey.}
+\label{tab:benchmarks}
+
+\end{table*}
 
@@
 % 
+In this section we presents the results of this work, regarding the WL feature forward model accuracy and the cosmological parameter bias induced by the Born approximation.
+
 \begin{figure*}
@@
 The residuals are compared to the two $O(\Phi^3)$ terms $2P_{\rm born,ll},2P_{\rm born,geo}$.
-The quantities shown are the averages over 1024 realizations of $\kappa$ in the fiducial cosmology $\bb{p}_0$.}
+The quantities shown are the ensemble averages over 8192 realizations of $\kappa$ in the fiducial cosmology $\bb{p}_0$.}
 \label{fig:psResiduals}
 \end{figure*}
-%
-We also studied the accuracy of the Born approximation in predicting the 9 higher order convergence moments defined in (\ref{par:moments}). The results are shown in Figure \ref{fig:pdfMoments}.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.4]{Figures/delta_m2.eps}
+\includegraphics[scale=0.4]{Figures/delta_m5.eps}
+\end{center}
+\caption{Dominant post--Born corrections to the $\kappa$ skewness and kurtosis due to lens--lens coupling and geodesic perturbation, as a function of the scale $\theta_G$ of the Gaussian smoothing window.
+We show the contributions of the lens--lens couplings (red) and the geodesic perturbation (green).
+We show both the cases in which the residuals $\delta\kappa^3,\delta\kappa^4$ are computed adding equations (\ref{sim:ll},\ref{sim:gp}) to the Born field (solid lines) and in which the residuals are computed from the dominant $\Phi$ orders only as in equations (\ref{res:skewcross},\ref{res:kurtcross}) (dashed lines).
+The quantities shown are the ensemble averages over 8192 realizations of $\kappa$ in the fiducial cosmology $\bb{p}_0$.}
+\label{fig:skResiduals}
+\end{figure*}
 
@@
 
-\subsection{Parameter bias}
-When using forward models based on the Born approximation to fit observations, parameter biases may occur if the forward model is not accurate enough.
-We studied if this is the case by simulating 1000 LSST--like observations in which the convergence field $\kappa(\pt)$ is constructed using the full ray--tracing procedure.
-We used the Born approximation to fit these mock observations using the Fisher parameter estimator in (\ref{par:fisherest}).
-The results are shown in Figure \ref{fig:parbias}.
-
-In this section we presents the results of this work, regarding the WL feature forward model accuracy and the cosmological parameter bias induced by the Born approximation.
-
 \subsection{Forward model accuracy}
@@
 In this paragraph we compare the accuracy of the Born approximation in predicting WL image features, in particular we focus on the $\kappa$ power spectrum and the 9 moments described in equation (\ref{par:moments}).
-Figure \ref{fig:psResiduals} shows the auto power spectra of $\kappa^{\rm born},\kappa^{\rm ll},\kappa^{\rm geo}$ as defined in equation (\ref{sim:pb2}).
+Figure \ref{fig:psResiduals} shows the auto power spectra of $\kappa_{\rm born},\kappa_{\rm ll},\kappa_{\rm geo}$ as defined in equation (\ref{sim:pb2}).
 At lowest order the lensing potential contributes to the $\kappa$ power spectrum quadratically.
@@
 \label{res:powercross}
-\langle\tilde{\kappa}^{a}(\pmb{\ell})\tilde{\kappa}^{b,*}(\pmb{\ell}')\rangle = (2\pi)^2\delta^D(\pmb{\ell}+\pmb{\ell}')P_{a,b}^{\kappa\kappa}(\ell)
+\langle\tilde{\kappa}_a(\pmb{\ell})\tilde{\kappa}_b^*(\pmb{\ell}')\rangle = (2\pi)^2\delta^D(\pmb{\ell}+\pmb{\ell}')P_{a,b}^{\kappa\kappa}(\ell)
 \end{equation} 
@@
 Figure \ref{fig:psResiduals} shows the magnitudes of the $O(\Phi^3)$ post--Born corrections to the convergence power spectrum. 
+A similar analysis can be carried out for the skewness and kurtosis of the $\kappa$ field.
+The main contributions to the skewness and kurtosis are $O(\Phi^3),O(\Phi^4)$ respectively.
+The first post--Born corrections, on the other hand, come at $O(\Phi^5),O(\Phi^6)$.
+More in detail we have
+
+\begin{equation}
+\label{res:skewcross}
+\langle\kappa^3\rangle = \langle\kappa_{\rm born}^3\rangle + 3\langle\kappa_{\rm born}^2\kappa_{\rm ll}\rangle + 3\langle\kappa_{\rm born}^2\kappa_{\rm geo}\rangle + O(\Phi^5) 
+\end{equation}
+
+\begin{equation}
+\label{res:kurtcross}
+\langle\kappa^4\rangle_c = \langle\kappa_{\rm born}^4\rangle_c + 4\langle\kappa_{\rm born}^3\kappa_{\rm ll}\rangle_c + 4\langle\kappa_{\rm born}^3\kappa_{\rm geo}\rangle_c + O(\Phi^6)
+\end{equation}
+%
+Where the kurtosis connected components are defined as 
+\begin{equation}
+\label{res:kurtconnected}
+\langle\kappa^3_a\kappa_b\rangle_c = \langle\kappa^3_a\kappa_b\rangle - 3\langle\kappa_a^2\rangle\langle\kappa_a\kappa_b\rangle
+\end{equation}
+The magnitude of the post--Born corrections to the $\kappa$ skewness and kurtosis in equations (\ref{res:skewcross},\ref{res:kurtcross}) are shown in Figure \ref{fig:skResiduals}.
+We also studied the accuracy of the Born approximation in predicting the 9 higher order convergence moments defined in (\ref{par:moments}). The results are shown in Figure \ref{fig:pdfMoments}.
+
+\subsection{Parameter bias}
+When using forward models based on the Born approximation to fit observations, parameter biases may occur if the forward model is not accurate enough.
+We studied if this is the case by simulating 1000 LSST--like observations in which the convergence field $\kappa(\pt)$ is constructed using the full ray--tracing procedure.
+We used the Born approximation to fit these mock observations using the Fisher parameter estimator in (\ref{par:fisherest}).
+The results are shown in Figure \ref{fig:parbias}.
 
@@
 Figure \ref{fig:csample} shows that the dominant post--Born correction to the $\kappa$ reconstruction comes from the geodesic term (\ref{sim:gp}).
-This can be shown both looking at the lens-lens term, which is one order of magnitude smaller than the geodesic term, and looking at the $\kappa-\kappa^{\rm born}$ residuals, which show similar structure to the ones found in the $\kappa^{\rm geo}$ map.
+This can be shown both looking at the lens-lens term, which is one order of magnitude smaller than the geodesic term, and looking at the $\kappa-\kappa_{\rm born}$ residuals, which show similar structure to the ones found in the $\kappa_{\rm geo}$ map.
 
@@
 We can conclude that the dominant contributions to the residuals come from the Born--geodesic cross power, which dominates the Born--lens--lens cross power by two orders of magnitude on small scales.
-Figure \ref{fig:psResiduals} also gives indications that the perturbation series in powers of $\Phi$ becomes asymptotic on small angular scales as the higher orders $O(\Phi^4)$ tend to dominate the leading orders.
-This is likely due to the non--linearity of the density contrast on small scales.
+Figure \ref{fig:skResiduals} shows that the geodesic and lens--lens contributions to the $\kappa$ skewness and kurtosis are comparable and that the lowest non trivial post--Born corrections can fully account for the discrepancy between the Born approximated quantities and the ray--traced ones.
+Both Figures \ref{fig:psResiduals} and \ref{fig:skResiduals} give indications about the fact that the post--Born perturbation series break down at high orders in the lensing potential.
+In particular geodesic perturbations cannot be predicted accurately by a perturbation series, higher orders in $\Phi$ being dominant over smaller orders.
+We do not see this as an important limitation as the computational cost of the $O(\Phi^2)$ line--of--sight integrals is roughly the same as the ray--tracing one, as shown in Table \ref{tab:benchmarks}.
 
@@
 Figure \ref{fig:parbias} studies this possibility and shows that, while the Born approximation is sufficient to fit cosmology with the power spectrum of an LSST--like survey, even in the noiseless case, the same is not true for the higher $\kappa$ moments.
-The middle panel of Figure \ref{fig:parbias} show that high significance biases are observed when fitting a real observation with Born approximated $\kappa$ moments.
+The middle panel of Figure \ref{fig:parbias} shows that high significance biases are observed when fitting a real observation with Born approximated $\kappa$ moments.
 The bias however disappears when introducing galaxy shape noise, due to the resulting increased statistical error.
+This result leads us to the conclusion that the Born approximation is sufficient for future WL analyses.
+This approach also has the advantage of being 4 times computationally cheaper than full ray--tracing, as we show in Table \ref{tab:benchmarks} for a selected reference test case.
 
@@
 \begin{itemize}
-\item The main corrections to the Born approximations come from the perturbations in the light ray geodesic, with lens--lens coupling being at least one order of magnitude sub leading
+\item The lowest order post--Born corrections to the convergence power spectrum, skewness and kurtosis are sufficient to fully account for the discrepancies between ray--tracing and the Born approximation
+\item Using the \ttt{LensTools} software package, Born integration costs 4 times less than ray--tracing 
 \item The $\kappa$ power spectrum leads to negligible parameter bias for an LSST--like survey, even in the noiseless case
@@
 work was supported in part by the U.S. Department of Energy under
-Contract No. DE-SC00112704, and by the NSF Grant
-No. AST-1210877 (to Z.H.) and by the Research Opportunities and
+Contract No. DE-SC00112704, the NSF Grant
+No. AST-1210877 (to Z.H.), the Research Opportunities and
 Approaches to Data Science (ROADS) program at the Institute for Data
-Sciences and Engineering at Columbia University (to Z.H.).
+Sciences and Engineering at Columbia University (to Z.H.) and a Simons Fellowship (to Z.H.).
 

### 2016-11-02 Paper/Figures/generate.py

@@ -2,6 +2,9 @@
 from __future__ import division
 
 import sys,os,argparse
+from operator import add
+from functools import reduce
+
 sys.modules["mpi4py"] = None
 
 import itertools
@@ -53,7 +56,7 @@ def convergenceVisualize(cmd_args,smooth=0.5*u.arcmin,fontsize=22):
 	#Load data
 	cborn = ConvergenceMap.load(os.path.join(fiducial["c0"].getMapSet("kappaBorn").home,"born_z2.00_0001r.fits"))
 	cray = ConvergenceMap.load(os.path.join(fiducial["c0"].getMapSet("kappa").home,"WLconv_z2.00_0001r.fits"))
-	cll = ConvergenceMap.load(os.path.join(fiducial["c0"].getMapSet("kappaGP").home,"postBorn2-ll_z2.00_0001r.fits"))
+	cll = ConvergenceMap.load(os.path.join(fiducial["c0"].getMapSet("kappaLL").home,"postBorn2-ll_z2.00_0001r.fits"))
 	cgp = ConvergenceMap.load(os.path.join(fiducial["c0"].getMapSet("kappaGP").home,"postBorn2-gp_z2.00_0001r.fits"))
 
 	#Smooth
@@ -68,9 +71,9 @@ def convergenceVisualize(cmd_args,smooth=0.5*u.arcmin,fontsize=22):
 
 	#Titles
 	ax[0,0].set_title(r"$\kappa$",fontsize=fontsize)
-	ax[0,1].set_title(r"$\kappa-\kappa^{\rm born}$",fontsize=fontsize)
-	ax[1,0].set_title(r"$\kappa^{\rm ll}$",fontsize=fontsize)
-	ax[1,1].set_title(r"$\kappa^{\rm geo}$",fontsize=fontsize)
+	ax[0,1].set_title(r"$\kappa-\kappa_{\rm born}$",fontsize=fontsize)
+	ax[1,0].set_title(r"$\kappa_{\rm ll}$",fontsize=fontsize)
+	ax[1,1].set_title(r"$\kappa_{\rm geo}$",fontsize=fontsize)
 
 	#Switch off grids
 	for i in (0,1):
@@ -121,6 +124,128 @@ def powerResiduals(cmd_args,fontsize=22):
 	#Save
 	fig.tight_layout()
 	fig.savefig("powerResiduals."+cmd_args.type)
+
+####################################################################################################################
[…]

### 2016-11-03 batchcode/scripts/measure_from_maps.py
specify collection in measure features

@@ -192,6 +192,7 @@ if __name__=="__main__":
 	parser.add_argument("-c","--config",dest="config",action="store",default=None,help="config file")
 	parser.add_argument("-s","--smooth",dest="smooth",action="store",type=float,default=None,help="smoothing scale in arcmin")
 	parser.add_argument("-m","--maps",dest="maps",action="store",default=None,help="map sets file")
+	parser.add_argument("-C","--collection",dest="collection",action="store",default="c0",help="model collection")
 	cmd_args = parser.parse_args()
 
 	#Make sure config is provided
@@ -274,7 +275,7 @@ if __name__=="__main__":
 		#Perform the measurements for all the map sets
 		for ms in maps[cosmo_id]:
 
-			map_set = model["c0"].getMapSet(ms)
+			map_set = model[cmd_args.collection].getMapSet(ms)
 
 			#Log to user
 			logging.info("Processing model {0}, map set {1}".format(map_set.cosmo_id,map_set.settings.directory_name))

### 2016-11-03 Paper/Figures/generate.py
c0-->collection

@@ -48,16 +48,16 @@ plab = { "Om":r"$\Omega_m$", "w0":r"$w_0$", "wa":r"$w_a$", "si8":r"$\sigma_8$" }
 ###################################################################################################
 ###################################################################################################
 
-def convergenceVisualize(cmd_args,smooth=0.5*u.arcmin,fontsize=22):
+def convergenceVisualize(cmd_args,collection="c0",smooth=0.5*u.arcmin,fontsize=22):
 
 	#Initialize plot
 	fig,ax = plt.subplots(2,2,figsize=(16,16))
 
 	#Load data
-	cborn = ConvergenceMap.load(os.path.join(fiducial["c0"].getMapSet("kappaBorn").home,"born_z2.00_0001r.fits"))
-	cray = ConvergenceMap.load(os.path.join(fiducial["c0"].getMapSet("kappa").home,"WLconv_z2.00_0001r.fits"))
-	cll = ConvergenceMap.load(os.path.join(fiducial["c0"].getMapSet("kappaLL").home,"postBorn2-ll_z2.00_0001r.fits"))
-	cgp = ConvergenceMap.load(os.path.join(fiducial["c0"].getMapSet("kappaGP").home,"postBorn2-gp_z2.00_0001r.fits"))
+	cborn = ConvergenceMap.load(os.path.join(fiducial[collection].getMapSet("kappaBorn").home,"born_z2.00_0001r.fits"))
+	cray = ConvergenceMap.load(os.path.join(fiducial[collection].getMapSet("kappa").home,"WLconv_z2.00_0001r.fits"))
+	cll = ConvergenceMap.load(os.path.join(fiducial[collection].getMapSet("kappaLL").home,"postBorn2-ll_z2.00_0001r.fits"))
+	cgp = ConvergenceMap.load(os.path.join(fiducial[collection].getMapSet("kappaGP").home,"postBorn2-gp_z2.00_0001r.fits"))
 
 	#Smooth
 	for c in (cborn,cray,cll,cgp):
@@ -87,19 +87,19 @@ def convergenceVisualize(cmd_args,smooth=0.5*u.arcmin,fontsize=22):
 ###################################################################################################
 ###################################################################################################
 
-def powerResiduals(cmd_args,fontsize=22):
[…]

### 2016-11-22 Paper/paper.tex
measure with different levels of shape noise

@@
 
-\title{On the validity of the Born approximation for Weak Lensing observables}
+%ZH: I added beyond-Gaussian to distinguish ourselves from prior studies on 2-pt statistics:
+\title{On the validity of the Born approximation for beyond-Gaussian weak lensing observables}
 
@@
 \begin{abstract}
-Accurate forward modeling of Weak Lensing (WL) observables from cosmological parameters is a necessary tool for upcoming galaxy surveys.
+Accurate forward modeling of weak lensing (WL) observables from cosmological parameters is necessary for upcoming galaxy surveys.
 Because WL probes structures in the non--linear regime, analytical forward modeling is very challenging, if not impossible.
 Numerical simulations of WL features rely on ray--tracing through the outputs of $N$--body simulations, which requires knowledge of the gravitational potential and accurate solvers for light ray trajectories.
-A cheaper but less accurate procedure based on the Born approximation, on the other hand, requires knowledge of the density only and can be implemented more efficiently and at lower computational cost.
-In this work we show that the deviations of the Born--approximated convergence power spectrum, skewness and kurtosis from the ray--traced ones are consistent with the smallest non trivial post--Born corrections.
+A less accurate procedure, based on the Born approximation, only requires knowledge of the density field, and can be implemented more efficiently and at a lower computational cost.
+In this work, we use simulations to show that deviations of the Born--approximated convergence power spectrum, skewness and kurtosis from their fully ray--traced counterparts are consistent with the smallest non--trivial post--Born corrections.
+%ZH(***): I don't understand the next sentence -- let's discuss whether to keep or delete:
 We also show that perturbative approaches to the post--Born corrections break down at higher orders, making full ray--tracing more reliable. 
-Because we find that cosmological parameter biases induced by the Born approximation are negligible even for an LSST--like survey once galaxy shape noise is considered, we argue that the Born approximation is preferred for future analysis.
+%
+We find that cosmological parameter biases induced by the Born approximation are negligible even for an LSST--like survey, once galaxy shape noise is considered, and we conclude that the Born approximation is sufficient for future galaxy WL analyses.
 Using the \ttt{LensTools} software suite, we show that the Born approximation saves a factor of 4 in computing time with respect to the full ray--tracing in reconstructing the convergence.
@@
 %
-Weak Gravitational Lensing is a promising observational technique to probe the standard $w$CDM model of the universe, and can help in constraining the Dark Energy equation of state parameters \citep{wlreview}.
+Weak gravitational lensing (WL) is a promising observational technique to probe the standard $w$CDM model of the universe, and can help in constraining the Dark Energy equation of state parameters \citep{wlreview}.
 Accurate forward modeling of WL observables is crucial for parameter estimation purposes.
@@
 A variety of groups have studied the validity of the Born approximation for forward modeling of convergence power spectra and bi--spectra \citep{WLBispectrumDodelson}, spectra of WL cosmic flexions \citep{BornFlexion} and, in more recent work, CMB lensing bi--spectra \citep{CMBPrattenLewis}.
-In this work we focus on a numerical study of the Born approximation validity for forward modeling of a subset convergence real space low order moments.
-The paper is organized as follows: we give a brief review of the ray--tracing formalism, along with the Born approximation and its lowest order corrections.
-We then outline how cosmological parameter constraints can be derived from WL features.
-Finally, we summarize our main findings and discuss possible future developments of this study.
+In this work, we study the validity of the Born approximation for forward modeling a subset of low--order moments of the real--space convergence field.
+
+%ZH: grammatical comment:  when you have two nested adjectives in front of a subject, 
+%    you should always hyphenate  (lowest-order X, ... real-space X, etc...)
+This paper is organized as follows.
+In \S\ref{sec:sims}, we give a brief review of the ray--tracing formalism, along with the Born approximation and its lowest--order corrections.
+In \S~\ref{sec:params}, we then outline how cosmological parameter constraints can be derived from WL features.
+We present our main results in \S~\ref{sec:results}, which we discuss further in \S~\ref{sec:discuss}.
+Finally, in \S~\ref{sec:conclude}, we summarize our conclusions, and mention possible future extensions of this study.
 
@@
 \section{Simulations}
+\label{sec:sims}
 % 
-In this section we give an overview of the formalism behind WL simulations.
-WL observables are related to the matter density contrast $\delta$.
+In this section, we give an overview of the formalism behind WL simulations. WL observables are related to the matter density contrast $\delta$ (or potential $\phi$). 
+%ZH: I added potential above -- technically it's the total potential that matters
 Light rays crossing density inhomogeneities experience deflections, which cause observed galaxy shapes to be distorted.
@@
 %
-Where we indicated the transverse comoving coordinates as $\bb{x}_\perp$, the longitudinal comoving distance as $\chi$, the universe scale factor as $a$ and as $H_0$,$\Omega_m$ the Hubble parameter and the matter density parameter respectively.
-The time dependence of $\Phi,\delta$ has been absorbed in $\chi$ with the use of the distance--redshift relation.
-Under the flat sky approximation, the transverse coordinates $\bb{x}_\perp$ can be related as the angles as seen from an Earth based observer $\pmb{\beta}=\bb{x}_\perp/\chi$.
+Where we denote the transverse comoving coordinates as $\bb{x}_\perp$, the longitudinal comoving distance as $\chi$, the universe scale factor as $a$, and the Hubble parameter and the matter density parameter as  $H_0$ and $\Omega_m$, respectively.
+The time dependence of $\Phi,\delta$ has been absorbed into $\chi$ with the use of the distance--redshift relation.
+Under the flat--sky approximation, the transverse coordinates $\bb{x}_\perp$ can be related as the angles as seen from an Earth based observer $\pmb{\beta}=\bb{x}_\perp/\chi$.
 In the following paragraph we give a summary of the ray--tracing basics.
@@
 \begin{pmatrix}
-1-\kappa(\pt)-\gamma^1(\pt) & -\gamma^2(\pt) + \omega(\pt) \\
--\gamma^2(\pt) - \omega(\pt) & 1-\kappa(\pt)+\gamma^1(\pt)
+%ZH: I changed gamma^i to gamma_i  (this is more conventional and avoids confusion of gamma^2 with square of gamma).
+1-\kappa(\pt)-\gamma_1(\pt) & -\gamma_2(\pt) + \omega(\pt) \\
+-\gamma_2(\pt) - \omega(\pt) & 1-\kappa(\pt)+\gamma_1(\pt)
 \end{pmatrix}
@@
 %
-Where $\kappa,\pmb{\gamma},\omega$ refer respectively to the WL cosmic convergence, shear and rotation angle.
+Where $\kappa,\pmb{\gamma}$, and $\omega$ refer respectively to the WL cosmic convergence, shear and sky position angle.
+%rotation angle. 
+%ZH: not sure what you mean by rotation angle.  I replaced it by sky position
 The implicit solution (\ref{sim:geosol}) to the geodesic equation (\ref{sim:geodiff}) can be translated in an integral equation for the lensing Jacobian
@@
 \label{sim:jacsol}
-A_{ij}(\pt,\chi_s) = \delta^K_{ij}-2\int_0^{\chi_s} d\chi\chi W(\chi,\chi_s)\Phi_{ik}(\bb{x}_\perp(\chi,\pt),\chi)A_{kj}(\pt,\chi)
+A_{ij}(\pt,\chi_s) = \delta^K_{ij}-2\int_0^{\chi_s} d\chi\chi W(\chi,\chi_s)\Phi_{ik}(\bb{x}_\perp(\chi,\pt),\chi)A_{kj}(\pt,\chi).
 \end{equation} 
@@
 %
-We indicated the partial derivatives of the lensing potential $\Phi$ with respect to the transverse coordinates $x,y$ as subscripts.
-We also defined the single redshift source lensing kernel $W(\chi,\chi_s)=1-\chi/\chi_s$ and indicated the Kronecker delta symbol as $\delta^K$.
+We denote the partial derivatives of the lensing potential $\Phi$ with respect to the transverse coordinates $x,y$ as subscripts.
+We also defined the single--redshift source lensing kernel $W(\chi,\chi_s)\equiv 1-\chi/\chi_s$ and indicated the Kronecker delta symbol as $\delta^K$.
 The WL convergence $\kappa(\pt,\chi_s)$ can be calculated from the trace of the Jacobian
@@
 The integral in (\ref{sim:jacsol}) can be approximated using a series expansion in powers of $\Phi$, which can yield acceptable results in the limit in which $\Phi$ is small.
-To compute the lowest order approximation to (\ref{sim:jacsol}) one notes that the lensing potential appears on the right hand side and hence we can replace the Jacobian on the right hand side with its zeroth order expression, i.e.
+To compute the lowest--order approximation to
+%ZH: in many places you missed ``eq'' from in front of the equation number.  I tried to add all of them, but you could check if I still missed some.
+eq.~(\ref{sim:jacsol}) one notes that the lensing potential appears on the right hand side and hence we can replace the Jacobian on the right hand side with its zeroth order expression, i.e.
 the identity matrix.
@@
 %
-The Born approximated convergence in equation (\ref{sim:born}) has a simple interpretation: at lowest order in the lensing potential, $\kappa$ is the integrated matter density on the unperturbed line of sight, weighted by the lensing kernel $W$.
-Contrary to the exact ray--tracing approach, the Born approximation does not required knowledge of the solution to the Poisson equation (\ref{sim:poisson}) and is hence computationally cheaper.
+The Born--approximated convergence in eq.~(\ref{sim:born}) has a simple interpretation: at lowest order in the lensing potential, $\kappa$ is the integrated matter density on the unperturbed line of sight, weighted by the lensing kernel $W$.
+Contrary to the exact ray--tracing approach, the Born approximation does not require knowledge of the solution to the Poisson equation (\ref{sim:poisson}) and is hence computationally cheaper.
 In the next paragraph we examine the corrections to the Born approximation that come at second order in the potential $\Phi$.
 
-\subsection{Post Born corrections}
-Equation (\ref{sim:jacsol}) allows to express the convergence $\kappa$ at arbitrary high orders in $\Phi$ powers.
-The linear order expression corresponds to the Born approximation in equation (\ref{sim:born}).
+\subsection{Post--Born corrections}
+
+Equation (\ref{sim:jacsol}) allows us to express the convergence $\kappa$ at arbitrary high orders in $\Phi$ powers.
+The linear--order expression corresponds to the Born approximation in equation (\ref{sim:born}).
 At second order in $\Phi$ we can write, following \citep{WLBispectrumDodelson}
@@
 %
-The second order corrections can be expressed as double integrals along the unperturbed line of sight
+The second order O($\Phi^2$) corrections can be expressed as double integrals along the unperturbed line of sight
 
@@
 \label{sim:ll}
-\kappa_{\rm ll}(\pt,\chi_s) = \int_0^{\chi_s}d\chi\int_0^\chi d\chi' \chi\chi' W(\chi,\chi_s)W(\chi',\chi)\Phi_{ij}(\chi\pt,\chi)\Phi_{ij}(\chi'\pt,\chi')
+\kappa_{\rm ll}(\pt,\chi_s) = \int_0^{\chi_s}d\chi\int_0^\chi d\chi' \chi\chi' W(\chi,\chi_s)W(\chi',\chi)\Phi_{ij}(\chi\pt,\chi)\Phi_{ij}(\chi'\pt,\chi'),
 \end{equation}
@@
 \label{sim:gp}
-\kappa_{\rm geo}(\pt,\chi_s) = \frac{3H_0^2\Omega_m}{2c^2}\int_0^{\chi_s}d\chi\int_0^\chi d\chi' \frac{\chi\chi'}{a(\chi')} W(\chi,\chi_s)W(\chi',\chi)\nabla_\perp\Phi(\chi\pt,\chi)\cdot\nabla_\perp\delta(\chi'\pt,\chi')
+\kappa_{\rm geo}(\pt,\chi_s) = \frac{3H_0^2\Omega_m}{2c^2}\int_0^{\chi_s}d\chi\int_0^\chi d\chi' \frac{\chi\chi'}{a(\chi')} W(\chi,\chi_s)W(\chi',\chi)\nabla_\perp\Phi(\chi\pt,\chi)\cdot\nabla_\perp\delta(\chi'\pt,\chi').
 \end{equation}
@@
 %
-These second order expression have a simple physical interpretation.
-Equation (\ref{sim:ll}) encodes the post--Born correction to the convergence due to non local quadratic lens--lens couplings, which add to the density line of sight integration in (\ref{sim:born}).
-Equation (\ref{sim:gp}), on the other hand, encodes the integral of the density contrast on the real light ray trajectory, at lowest order in the geodesic deflections.
-The line of sight integrals (\ref{sim:born}), (\ref{sim:ll}) and (\ref{sim:gp}) can be computed efficiently with runtime that scales linearly with the number of lenses using the functionality of the \ttt{LensTools} suite \citep{LensTools-paper}.
+These second--order expressions have a simple physical interpretation.
+Equation (\ref{sim:ll}) encodes the post--Born correction to the convergence due to non--local quadratic lens--lens couplings, which add to the density line of sight integral in eq.~(\ref{sim:born}).
+Eq.~(\ref{sim:gp}), on the other hand, encodes the integral of the density contrast along the real light--ray trajectory, at lowest order in the geodesic deflections.
+The line of sight integrals eqs.~(\ref{sim:born}), (\ref{sim:ll}) and (\ref{sim:gp}) can be computed efficiently with runtime that scales linearly with the number of lenses using the functionality of the \ttt{LensTools} suite \citep{LensTools-paper}.
 A sample of the simulation outputs is shown in Figure \ref{fig:csample}.
 Benchmarks for the runtime of the ray--tracing and line--of--sight integrals operations, performed with \ttt{LensTools}, are provided in Table \ref{tab:benchmarks}.
-In the next section we show how to infer cosmological parameters from WL features forward models applied to observations.
+In the next section, we summarize the procedure to fit forward models of the WL features to observational data to infer cosmological parameters.
 
@@
 
-\caption{Time and memory usage benchmarks for the convergence reconstruction operations.
+\caption{CPU time and memory usage benchmarks for the convergence reconstruction operations.
 The test case we considered consists in a discretization with 42 uniformly spaced lenses between the observer and the sources at $z_s=2$, each with a resolution of $4096^2$ pixels.
@@
 \end{center}
-\caption{Sample convergence outputs for one realization of a $(3.5\,{\rm deg})^2$ field of view.
+\caption{Sample convergence outputs for one realization of a $(3.5\,{\rm deg})^2$ field, with source galaxies at redshift $z_s=2$. 
+%ZH: Added z_s above.
 The figure shows the convergence profile (top left), along with the Born approximation residuals (top right), the lens-lens post--Born contribution (bottom left) and the geodesic contribution (bottom right).
-The images have been smoothed with a Gaussian kernel of size $\theta_G=0.5\,{\rm arcmin}$.}
+The images have been smoothed with a Gaussian kernel of size $\theta_G=0.5\,{\rm arcmin}$.
+Note the different scales in the bottom panels: the geodesic term (right), is over an order of magnitude larger than the lens--lens term (left), and is comparable in level and detailed structure to the full residual (top right).}
+%ZH: Added above sentence
 \label{fig:csample}
@@
 \section{Parameter inference}
+\label{sec:params}
 % 
@@
 %
-the maximum likelihood parameter estimator (\ref{par:fisherest}) is given by (see \citep{DodelsonSchneider13,PetriVariance} for example)
+the maximum likelihood parameter estimator in eq.~(\ref{par:fisherest}) is given by (see \citep{DodelsonSchneider13,PetriVariance} for example)
 \begin{equation}
@@
 where $\bb{\Psi}=(\bb{C}^{\bb{d}\bb{d}})^{-1}$.
-The linearity assumption (\ref{par:linapprox}) is justified when the scatter of the measure feature $\bbh{d}_{\rm obs}$ around the expansion point $\bb{d}_0$ is expected to be small.
+The linearity assumption (eq.~\ref{par:linapprox}) is justified when the scatter of the measure feature $\bbh{d}_{\rm obs}$ around the expansion point $\bb{d}_0$ is expected to be small.
 This is true for upcoming large area surveys such as LSST \citep{LSST}, WFIRST \citep{WFIRST} and Euclid \citep{Euclid}.
@@
 
-To study the effect of the Born approximation on parameter constraints, we measure the fiducial features $\bb{d}_0$, the derivatives $\bb{M}$ and the feature covariance $\bb{C}^{\bb{d}\bb{d}}$ from $\kappa$ mocks constructed with the Born approximation (\ref{sim:born}).
-We then evaluate the induced parameter bias by applying the parameter estimator (\ref{par:fisherest}) to a mock observation constructed with full ray--tracing as in equations (\ref{sim:jacsol}), (\ref{sim:trkappa}).
-We perform the ray--tracing and the line of sight integrals for fixed redshift sources at $z_s=2$ uniformly distributed in a $(3.5\,{\rm deg})^2$ field of view, with a resolution of $2048^2$ pixels.
+To study the effect of the Born approximation on parameter constraints, we measure the fiducial features $\bb{d}_0$, the derivatives $\bb{M}$ and the feature covariance $\bb{C}^{\bb{d}\bb{d}}$ from $\kappa$ mocks constructed with the Born approximation (eq.~\ref{sim:born}).
+We then evaluate the induced parameter bias by applying the parameter estimator (eq.~\ref{par:fisherest}) to a mock observation constructed with full ray--tracing as in equations (\ref{sim:jacsol}) and (\ref{sim:trkappa}).
+We perform the ray--tracing and the line--of--sight integrals for sources at the  fixed redshift $z_s=2$, uniformly distributed on a square grid in a $(3.5\,{\rm deg})^2$ field of view, with a resolution of $2048^2$ pixels.
 To mimic an LSST--like mock observation, we use the 8192 realizations in our fiducial $\kappa$ ensemble to bootstrap the mean of 1000 fiducial feature measurements, which is equivalent approximately to a $10000\,{\rm deg}^2$ sky coverage.
@@
 
-\caption{Cosmological parameters used in our simulation suite}
+\caption{Cosmological parameters in our simulation suite}
 \label{tab:cosmopar}
@@
 
-We can add galaxy shape noise to our $\kappa$ mocks in the form of a pixel uncorrelated white Gaussian noise \citep{SongKnox} with rms
+We add galaxy shape noise to our $\kappa$ mocks in the form of a pixel uncorrelated white Gaussian noise \citep{SongKnox} with r,r.m.s.
 \begin{equation}
@@
 where the number of galaxies per pixel $N_g$ is based on a galaxy angular density of $15\,{\rm arcmin}^{-2}$. 
+%ZH(***): 15 is pretty conservative for LSST.
+I thought it would be closer to 30-40 --- and WFIRST is talking about 70-80.
+Would this smaller noise change the conclusions about the moments being unbiased??
 
-Our image feature choice includes the $\kappa$ power spectrum $P^{\kappa\kappa}(\ell)$ defined as 
+Our image feature choice includes the $\kappa$ power spectrum $P^{\kappa\kappa}(\ell)$, defined as 
 \begin{equation}
 \label{par:powerdef}
-\langle\tilde{\kappa}(\pmb{\ell})\tilde{\kappa}^*(\pmb{\ell}')\rangle = (2\pi)^2\delta^D(\pmb{\ell}+\pmb{\ell}')P^{\kappa\kappa}(\ell) 
+\langle\tilde{\kappa}(\pmb{\ell})\tilde{\kappa}^*(\pmb{\ell}')\rangle = (2\pi)^2\delta^D(\pmb{\ell}+\pmb{\ell}')P^{\kappa\kappa}(\ell),
 \end{equation}
 %
-Where the expectation value is taken over $\pmb{\ell}$ modes with the same magnitude $\ell=\vert\pmb{\ell}\vert$ and $\delta^D$ is the Dirac delta function.
+where the expectation value is taken over $\pmb{\ell}$ modes with the same magnitude $\ell=\vert\pmb{\ell}\vert$ and $\delta^D$ is the Dirac delta function.
 Because the $\kappa$ field is non--Gaussian, higher order statistics such as higher real space $\kappa$ moments have been shown to contain complementary information in addition to the one already supplied by the power spectrum \citep{MinkPetri,CFHTMink,NG-Jain1,NG-Jain2}.
-We consider the following set of $\kappa$ moments $\pmb{\mu}$
+We consider the following sets of $\kappa$ moments $\pmb{\mu}_i$:
 
@@
 \pmb{\mu}_3 = \left(\langle\kappa^3\rangle,\langle\kappa^2\nabla^2\kappa\rangle,\langle\vert\nabla\kappa\vert^2\nabla^2\kappa\rangle\right) \\ \\
-\pmb{\mu}_4 = \left(\langle\kappa^4\rangle_c,\langle\kappa^3\nabla^2\kappa\rangle_c,\langle\kappa\vert\nabla\kappa\vert^2\nabla^2\kappa\rangle_c,\langle\vert\nabla\kappa\vert^4\rangle_c\right) \\
+\pmb{\mu}_4 = \left(\langle\kappa^4\rangle_c,\langle\kappa^3\nabla^2\kappa\rangle_c,\langle\kappa\vert\nabla\kappa\vert^2\nabla^2\kappa\rangle_c,\langle\vert\nabla\kappa\vert^4\rangle_c\right).\\
 \end{matrix}
@@
 %
-Where the expectation values are taken with respect to pixels and the subscript $c$ indicated that we are considering the connected components of the quartic moments $\pmb{\mu}_4$.
+Here the expectation values are taken with respect to pixels and the subscript $c$ denotes the connected components of the quartic moments $\pmb{\mu}_4$.
 In the next section we outline our main results.
@@
 \section{Results}
+\label{sec:results}
 % 
-In this section we presents the results of this work, regarding the WL feature forward model accuracy and the cosmological parameter bias induced by the Born approximation.
+In this section, we present the main results of this work, regarding  accuracy of forward modeling the WL features, and the cosmological parameter biases induced by the Born approximation.
 
@@
 \begin{center}
-\includegraphics[scale=0.3]{Figures/powerResiduals.eps}
+%ZH: it is very hard to read the labels inside the figure legend.  Please increase the size.  I also scaled the figure to be larger overall:
+%\includegraphics[scale=0.3]{Figures/powerResiduals.eps}
+\includegraphics[scale=0.45]{Figures/powerResiduals.eps}
 \end{center}
-\caption{Contributions of different $\Phi$ orders to the $\kappa$ power spectrum: the left panel shows the auto power spectra $P_{\rm born,born}$ ($O(\Phi^2)$) and $P_{\rm ll},P_{\rm geo}$ ($O(\Phi^4)$).
+\caption{Contributions at different $\Phi$ orders to the $\kappa$ power spectrum: the left panel shows the auto power spectra $P_{\rm born,born}$ ($O(\Phi^2)$) and $P_{\rm ll},P_{\rm geo}$ ($O(\Phi^4)$).
 The right panel shows the residuals between the power spectrum of the full ray--traced $\kappa$ field and the one obtained with the Born approximation.
@@
 \begin{center}
-\includegraphics[scale=0.4]{Figures/delta_m2.eps}
-\includegraphics[scale=0.4]{Figures/delta_m5.eps}
+%ZH: same here -- hard to read the labels inside the figure legend.  Please increase the size.  I also scaled the figure to be larger overall:
+%\includegraphics[scale=0.4]{Figures/delta_m2.eps}
+%\includegraphics[scale=0.4]{Figures/delta_m5.eps}
+\includegraphics[scale=0.46]{Figures/delta_m2.eps}\includegraphics[scale=0.46]{Figures/delta_m5.eps}
 \end{center}
+%ZH(***): I think we could delete the solid green/red. For me they are more confusing than helpful -- but lets discuss.  
 \caption{Dominant post--Born corrections to the $\kappa$ skewness and kurtosis due to lens--lens coupling and geodesic perturbation, as a function of the scale $\theta_G$ of the Gaussian smoothing window.
@@
 \begin{center}
-\includegraphics[scale=0.25]{Figures/pdfMoments.eps}
+%ZH: I enlarged the figure 0.25->0.3
+%ZH: Can you capitalize the label ``born'' to ``Born'' in the figure legends?
+%ZH: Also, the x-labels like 0.00000185 look weird.  Can you change them to 1.85e-5 etc, like in the bottom panel with 1e-10 units ?
+\includegraphics[scale=0.3]{Figures/pdfMoments.eps}
 \end{center}
-\caption{Probability distribution function (PDF) of the 9 $\kappa$ moments defined in (\ref{par:moments}), over 8192 realizations of the fiducial cosmological model $\bb{p}_0$.
+\caption{Probability distribution function (PDF) of the 9 $\kappa$ moments defined in eq.~(\ref{par:moments}), over 8192 realizations of the fiducial cosmological model $\bb{p}_0$. 
+%ZH: added this:
+The top/middle/bottom rows show examples of 2nd, 3rd, and 4th-order moments. 
+%
 We show both the PDFs obtained with full ray--tracing (blue) and the Born approximation (green).
@@
 \begin{center}
-\includegraphics[scale=0.25]{Figures/bias_convergence_power_s0_nb100.eps}
-\includegraphics[scale=0.25]{Figures/bias_convergence_moments_s0_nb9.eps}
-\includegraphics[scale=0.25]{Figures/bias_convergence_momentsSN_s0_nb9.eps}
+\includegraphics[scale=0.3]{Figures/bias_convergence_power_s0_nb100.eps}
+\includegraphics[scale=0.3]{Figures/bias_convergence_moments_s0_nb9.eps}
+\includegraphics[scale=0.3]{Figures/bias_convergence_momentsSN_s0_nb9.eps}
 \end{center}
-\caption{Distribution of the parameter estimator (\ref{par:fisherest}) over 1000 realizations of an LSST--like survey.
-We show parameter estimates obtained using the noiseless $\kappa$ power spectrum (top panel), the noiseless $\kappa$ moments defined in (\ref{par:moments}) (middle panel) and the noisy $\kappa$ moments, based on a galaxy density of $15\,{\rm arcmin}^{-2}$ (bottom panel).
-We show both a control case, in which the observation has been constructed with the Born approximation (blue), and the real case, in which the observation has been constructed with full ray--tracing (green).}
+\caption{Distributions of the parameter estimator (eq.~\ref{par:fisherest}) over 1000 realizations of an LSST--like survey.
+We show parameter estimates obtained using the noiseless $\kappa$ power spectrum (top panels), the noiseless $\kappa$ moments defined in eq.~(\ref{par:moments}) (middle panels) and the noisy $\kappa$ moments, based on a galaxy density of $15\,{\rm arcmin}^{-2}$ (bottom panels).
+%ZH: Added this:
+We do not show results from the noisy power spectrum, because the noiseless power spectrum is already unbiased.
+%
+In each panel, we show both a control case, in which the mock observation has been constructed with the Born approximation (blue), and the ``real'' case, in which the observation has been constructed with full ray--tracing (green).}
 \label{fig:parbias}
@@
 
-In this paragraph we compare the accuracy of the Born approximation in predicting WL image features, in particular we focus on the $\kappa$ power spectrum and the 9 moments described in equation (\ref{par:moments}).
+In this subsection, we compare the accuracy of the Born approximation in predicting WL image features, in particular we focus on the $\kappa$ power spectrum and the 9 moments described in equation (\ref{par:moments}).
 Figure \ref{fig:psResiduals} shows the auto power spectra of $\kappa_{\rm born},\kappa_{\rm ll},\kappa_{\rm geo}$ as defined in equation (\ref{sim:pb2}).
 At lowest order the lensing potential contributes to the $\kappa$ power spectrum quadratically.
-The first post--Born correction to $P^{\kappa\kappa}$ comes to $O(\Phi^3)$ and is given by
+The first post--Born correction to $P^{\kappa\kappa}$ comes in at $O(\Phi^3)$ and is given by
 \begin{equation}
 \label{res:powercorr}
-P^{\kappa\kappa} = P^{\kappa\kappa}_{\rm born,born} + 2P^{\kappa\kappa}_{\rm born,ll} + 2P^{\kappa\kappa}_{\rm born,geo} + O(\Phi^4)
+P^{\kappa\kappa} = P^{\kappa\kappa}_{\rm born,born} + 2P^{\kappa\kappa}_{\rm born,ll} + 2P^{\kappa\kappa}_{\rm born,geo} + O(\Phi^4),
 \end{equation}
 %
-Where we defined the $\kappa$ cross spectra as
+where we defined the $\kappa$ cross spectra as
 \begin{equation}
 \label{res:powercross}
-\langle\tilde{\kappa}_a(\pmb{\ell})\tilde{\kappa}_b^*(\pmb{\ell}')\rangle = (2\pi)^2\delta^D(\pmb{\ell}+\pmb{\ell}')P_{a,b}^{\kappa\kappa}(\ell)
+\langle\tilde{\kappa}_a(\pmb{\ell})\tilde{\kappa}_b^*(\pmb{\ell}')\rangle = (2\pi)^2\delta^D(\pmb{\ell}+\pmb{\ell}')P_{a,b}^{\kappa\kappa}(\ell).
 \end{equation} 
@@
 Figure \ref{fig:psResiduals} shows the magnitudes of the $O(\Phi^3)$ post--Born corrections to the convergence power spectrum.
-A similar analysis can be carried out for the skewness and kurtosis of the $\kappa$ field.
-The main contributions to the skewness and kurtosis are $O(\Phi^3),O(\Phi^4)$ respectively.
-The first post--Born corrections, on the other hand, come at $O(\Phi^5),O(\Phi^6)$.
-More in detail we have
+
+A similar analysis can be carried out for the various skewness and kurtosis moments of the $\kappa$ field.
+The main contributions to the skewness and kurtosis enter at $O(\Phi^3)$ and $O(\Phi^4)$, respectively.
+The first post--Born corrections, on the other hand, enter at $O(\Phi^5),O(\Phi^6)$.
+In more detail, we have
 
@@
 \end{equation}
-
+and
 \begin{equation}
 \label{res:kurtcross}
-\langle\kappa^4\rangle_c = \langle\kappa_{\rm born}^4\rangle_c + 4\langle\kappa_{\rm born}^3\kappa_{\rm ll}\rangle_c + 4\langle\kappa_{\rm born}^3\kappa_{\rm geo}\rangle_c + O(\Phi^6)
+\langle\kappa^4\rangle_c = \langle\kappa_{\rm born}^4\rangle_c + 4\langle\kappa_{\rm born}^3\kappa_{\rm ll}\rangle_c + 4\langle\kappa_{\rm born}^3\kappa_{\rm geo}\rangle_c + O(\Phi^6).
 \end{equation}
 %
-Where the kurtosis connected components are defined as 
+Here the connected kurtosis components are defined as 
 \begin{equation}
 \label{res:kurtconnected}
-\langle\kappa^3_a\kappa_b\rangle_c = \langle\kappa^3_a\kappa_b\rangle - 3\langle\kappa_a^2\rangle\langle\kappa_a\kappa_b\rangle
+\langle\kappa^3_a\kappa_b\rangle_c = \langle\kappa^3_a\kappa_b\rangle - 3\langle\kappa_a^2\rangle\langle\kappa_a\kappa_b\rangle.
 \end{equation}
+
 The magnitude of the post--Born corrections to the $\kappa$ skewness and kurtosis in equations (\ref{res:skewcross},\ref{res:kurtcross}) are shown in Figure \ref{fig:skResiduals}.
-We also studied the accuracy of the Born approximation in predicting the 9 higher order convergence moments defined in (\ref{par:moments}). The results are shown in Figure \ref{fig:pdfMoments}.
+We also studied the accuracy of the Born approximation in predicting the 9 higher order convergence moments defined in eq.~(\ref{par:moments}). The results are shown in Figure \ref{fig:pdfMoments}.
 
@@
 We studied if this is the case by simulating 1000 LSST--like observations in which the convergence field $\kappa(\pt)$ is constructed using the full ray--tracing procedure.
-We used the Born approximation to fit these mock observations using the Fisher parameter estimator in (\ref{par:fisherest}).
+We used the Born approximation to fit these mock observations using the Fisher parameter estimator in eq.~(\ref{par:fisherest}).
 The results are shown in Figure \ref{fig:parbias}.
@@
 \section{Discussion}
+\label{sec:discuss}
 % 
-In this section we discuss our main findings.
-Figure \ref{fig:csample} shows that the dominant post--Born correction to the $\kappa$ reconstruction comes from the geodesic term (\ref{sim:gp}).
-This can be shown both looking at the lens-lens term, which is one order of magnitude smaller than the geodesic term, and looking at the $\kappa-\kappa_{\rm born}$ residuals, which show similar structure to the ones found in the $\kappa_{\rm geo}$ map.
+In this section, we discuss our main findings.
+Figure \ref{fig:csample} shows that the dominant post--Born correction to the $\kappa$ reconstruction comes from the geodesic term (eq.~\ref{sim:gp}).
+This can be seen by looking at the lens-lens term, which is aver an order of magnitude smaller
+%ZH: I changed above to ``over an order of magnitude''
+ than the geodesic term, and by looking at the full $\kappa-\kappa_{\rm born}$ residuals, which show a very similar overall level, as well as structural detail, to the ones found in the $\kappa_{\rm geo}$ map.
 
-Figure \ref{fig:psResiduals} shows a comparison between the Born approximated $\kappa$ power spectra and the ones obtained with full ray--tracing, separating different orders in $\Phi$.
+Figure \ref{fig:psResiduals} shows a comparison between the Born--approximated $\kappa$ power spectra and the ones obtained with full ray--tracing, separating different orders in $\Phi$.
 We can conclude that the dominant contributions to the residuals come from the Born--geodesic cross power, which dominates the Born--lens--lens cross power by two orders of magnitude on small scales.
-Figure \ref{fig:skResiduals} shows that the geodesic and lens--lens contributions to the $\kappa$ skewness and kurtosis are comparable and that the lowest non trivial post--Born corrections can fully account for the discrepancy between the Born approximated quantities and the ray--traced ones.
-Both Figures \ref{fig:psResiduals} and \ref{fig:skResiduals} give indications about the fact that the post--Born perturbation series break down at high orders in the lensing potential.
-In particular geodesic perturbations cannot be predicted accurately by a perturbation series, higher orders in $\Phi$ being dominant over smaller orders.
-We do not see this as an important limitation as the computational cost of the $O(\Phi^2)$ line--of--sight integrals is roughly the same as the ray--tracing one, as shown in Table \ref{tab:benchmarks}.
+Figure \ref{fig:skResiduals} shows that the geodesic and lens--lens contributions to the $\kappa$ skewness and kurtosis are comparable and that the lowest non--trivial post--Born corrections can fully account for the discrepancy between the Born--approximated quantities and the fully ray--traced ones.
+%ZH(***): I do not understand the sentences below.  Let's discuss.  I think we could possibly delete the solid lines from these figures, and this discussion?
+Figs.
+\ref{fig:psResiduals} and \ref{fig:skResiduals} indicate that the post--Born perturbation series breaks down at high orders in the potential.
+In particular geodesic perturbations cannot be predicted accurately by a perturbation series, higher orders in $\Phi$ dominating over smaller orders.
+This is not an important limitation, however, as the computational cost of the $O(\Phi^2)$ line--of--sight integrals is roughly the same as for ray--tracing (Table \ref{tab:benchmarks}).
 
-Figure \ref{fig:pdfMoments} shows the PDF of the 9 $\kappa$ moments defined in (\ref{par:moments}) over 1000 realizations of an LSST--like survey.
-The plot clearly shows that, while the Born approximation is a good predictor of the quadratic moments $\pmb{\mu}_2$ within one standard deviation, the higher moments $\pmb{\mu}_3,\pmb{\mu}_4$ show $2\div 3\sigma$ deviations from their Born approximated counterparts.
+Figure \ref{fig:pdfMoments} shows the PDF of the 9 $\kappa$ moments defined in eq.~(\ref{par:moments}) over 1000 realizations of an LSST--like survey.
+This figure clearly shows that, while the Born approximation is a good predictor of the quadratic moments $\pmb{\mu}_2$ within one standard deviation, the higher moments $\pmb{\mu}_3,\pmb{\mu}_4$ show $2\div 3\sigma$ deviations from their Born--approximated counterparts.
 This can lead to parameter biases when fitting observations.
 Figure \ref{fig:parbias} studies this possibility and shows that, while the Born approximation is sufficient to fit cosmology with the power spectrum of an LSST--like survey, even in the noiseless case, the same is not true for the higher $\kappa$ moments.
-The middle panel of Figure \ref{fig:parbias} shows that high significance biases are observed when fitting a real observation with Born approximated $\kappa$ moments.
+%ZH: Added below:
+We have previously shown that these moments contain significantly more information than the power spectrum \citep{MinkPetri}; an expectation that was confirmed when fitting the CFHTLenS data~\citep{CFHTMink}.
+The middle row of panels in Figure \ref{fig:parbias} shows that indeed the constraints from the moments are $\approx$ 3 times tighter than from the power spectrum (seen by the narrow widths of the PDFs).
+As a result, highly significant
+%
+biases are observed when fitting a real observation with Born--approximated $\kappa$ moments.
 The bias however disappears when introducing galaxy shape noise, due to the resulting increased statistical error.
@@
 \section{Conclusions}
-In this work we studied the effectiveness of the Born approximation in predicting Weak Lensing observables, and studied the approximation effects on parameter constraints.
-Our main findings can be summarized in the following points:
+\label{sec:conclude}
+%
+In this work, we used cosmological simulations to study the effectiveness of the Born approximation in predicting WL observables, and to compute the corresponding biases on parameter constraints.
+Our main findings can be summarized as follows:
 
 \begin{itemize}
-\item The lowest order post--Born corrections to the convergence power spectrum, skewness and kurtosis are sufficient to fully account for the discrepancies between ray--tracing and the Born approximation
-\item Using the \ttt{LensTools} software package, Born integration costs 4 times less than ray--tracing 
-\item The $\kappa$ power spectrum leads to negligible parameter bias for an LSST--like survey, even in the noiseless case
-\item Fitting an observation with Born approximated higher $\kappa$ moments leads to high significance bias in the $(\Omega_m,w_0,\sigma_8)$ in the noiseless case.
-The bias significance becomes negligible when galaxy shape noise is added due to an increased scatter in parameter estimates.
+\item The lowest--order post--Born corrections to the convergence power spectrum, skewness and kurtosis are sufficient to fully account for the discrepancies between ray--tracing and the Born approximation.
+\item Using the \ttt{LensTools} software package, Born integration costs 4 times less than ray--tracing, and consumes about half as much memory.
+%ZH: Added memory above. OK?
+\item The $\kappa$ power spectrum leads to negligible parameter bias for an LSST--like survey, even in the noiseless case.
+\item Fitting an observation with Born--approximated higher $\kappa$ moments leads to significant bias in the $(\Omega_m,w_0,\sigma_8)$ triplet in the noiseless case.
+However, this bias becomes negligible when galaxy shape noise is added, due to an increased scatter in parameter estimates.
 \end{itemize}
@@
 Future prospects involve study the Born approximation validity for CMB lensing observations. 
+%ZH(***): we should add 2-3 sentences here, saying that we expect Born approximation to fail more badly in CMB lensing, and cite papers that recently showed this already (e.g.
+by Anthony Lewis).
+You could steal this from the discussion section of our recent CMB lensing paper (with Jia, Colin, etc).
 
@@
 \section*{Acknowledgments}
-We thank Uros Seljak for useful discussions.
+We thank Uro\v{s} Seljak and Colin Hill for useful discussions.
 The $N$--body simulations in this work were performed at National Energy Research Scientific Computing Center (NERSC).
@@
 Approaches to Data Science (ROADS) program at the Institute for Data
-Sciences and Engineering at Columbia University (to Z.H.) and a Simons Fellowship (to Z.H.).
+Sciences and Engineering at Columbia University (to Z.H.) and a Simons Fellowship in Theoretical Physics (to Z.H.).
 

### 2016-11-22 Paper/Figures/generate.py

@@ -250,7 +250,7 @@ def pdfMoments(cmd_args,collection="c0",kappa_models=("kappa","kappaBorn"),figna
 ###################################################################################################
 ###################################################################################################
 
-def pbBias(cmd_args,feature_name="convergence_power_s0_nb100",title="Power spectrum",kappa_models=("Born",),callback=None,variation_idx=(0,),bootstrap_size=100,resample=1000,fontsize=22):
+def pbBias(cmd_args,feature_name="convergence_power_s0_nb100",title="Power spectrum",kappa_models=("Born",),callback=None,variation_idx=(0,),bootstrap_size=100,resample=1000,return_results=False,fontsize=22):
 	
 	#Initialize plot
 	fig,ax = plt.subplots(len(variation_idx),3,figsize=(24,8*len(variation_idx)))
@@ -311,6 +311,12 @@ def pbBias(cmd_args,feature_name="convergence_power_s0_nb100",title="Power spect
 			fitted_parameters_born = fisher.fit(feature_born,features_covariance)
 			fitted_parameters_ray = fisher.fit(feature_ray,features_covariance)
 
+			if return_results:
+				assert len(kappa_models)==1
+				assert len(variation_idx)==1
+
+				return fitted_parameters_born,fitted_parameters_ray
+
 			##########
 			#Plotting#
 			##########
@@ -330,6 +336,45 @@ def pbBias(cmd_args,feature_name="convergence_power_s0_nb100",title="Power spect
 	#Save
 	fig.tight_layout()
 	fig.savefig("bias_{0}.{1}".format(feature_name,cmd_args.type))
+
+def pbBiasNgal(cmd_args,feature_names="convergence_momentsSN{0}_s0_nb9",ngal=(15,),kappa_model="Born",callback=None,variation_idx=0,bootstrap_size=100,resample=1000,fontsize=22):
+	
+	#Set up plot
+	fig,ax = plt.subplots()
+
+	#Parameter placeholders
+	lines = dict()
+
+	#Cycle over ngal
+	for ng in ngal:
+
+		#Fit parameters with Born, ray
+		pb,pr = pbBias(cmd_args,feature_name=feature_names.format(ng),
+			kappa_models=(kappa_model,),callback=callback,variation_idx=(variation_idx,),bootstrap_size=bootstrap_size,
[…]

### 2016-11-22 batchcode/scripts/measure_from_maps.py

@@ -191,6 +191,7 @@ if __name__=="__main__":
 	parser = argparse.ArgumentParser()
 	parser.add_argument("-c","--config",dest="config",action="store",default=None,help="config file")
 	parser.add_argument("-s","--smooth",dest="smooth",action="store",type=float,default=None,help="smoothing scale in arcmin")
+	parser.add_argument("-N","--ngal",dest="ngal",action="store",type=int,default=None,help="number of galaxies per sq arcmin")
 	parser.add_argument("-m","--maps",dest="maps",action="store",default=None,help="map sets file")
 	parser.add_argument("-C","--collection",dest="collection",action="store",default="c0",help="model collection")
 	cmd_args = parser.parse_args()
@@ -228,12 +229,16 @@ if __name__=="__main__":
 	#Redshift
 	redshift = options["redshift"]
 	add_shape_noise = options["add_shape_noise"]
-	ngal = options["ngal"]
 
 	#Smoothing
 	smoothing = options["smoothing"]
 	if cmd_args.smooth is not None:
 		smoothing = cmd_args.smooth
+
+	#Ngal per arcmin
+	ngal = options["ngal"]
+	if cmd_args.ngal is not None:
+		ngal = cmd_args.ngal
 
 	#Savename
 	savename = options["method"]

### 2016-11-22 Paper/paper.tex
added bias vs ngal

@@
 A less accurate procedure, based on the Born approximation, only requires knowledge of the density field, and can be implemented more efficiently and at a lower computational cost.
-In this work, we use simulations to show that deviations of the Born--approximated convergence power spectrum, skewness and kurtosis from their fully ray--traced counterparts are consistent with the smallest non--trivial post--Born corrections.
-%ZH(***): I don't understand the next sentence -- let's discuss whether to keep or delete:
-We also show that perturbative approaches to the post--Born corrections break down at higher orders, making full ray--tracing more reliable. 
-%
-We find that cosmological parameter biases induced by the Born approximation are negligible even for an LSST--like survey, once galaxy shape noise is considered, and we conclude that the Born approximation is sufficient for future galaxy WL analyses.
+In this work, we use simulations to show that deviations of the Born--approximated convergence power spectrum, skewness and kurtosis from their fully ray--traced counterparts are consistent with the smallest non--trivial post--Born corrections (so-called geodesic and lens-lens terms).
+We find, however, that the perturbative approach for the geodesic correction breaks down at higher orders.
+We also find that cosmological parameter biases induced by the Born approximation are negligible even for an LSST--like survey, once galaxy shape noise is considered, and we conclude that the Born approximation is sufficient for future galaxy WL analyses.
 Using the \ttt{LensTools} software suite, we show that the Born approximation saves a factor of 4 in computing time with respect to the full ray--tracing in reconstructing the convergence.
@@
 % 
-In this section, we give an overview of the formalism behind WL simulations. WL observables are related to the matter density contrast $\delta$ (or potential $\phi$). 
-%ZH: I added potential above -- technically it's the total potential that matters
+In this section, we give an overview of the formalism behind WL simulations.
+WL observables are related to the matter density contrast $\delta$ (or potential $\Phi$).
 Light rays crossing density inhomogeneities experience deflections, which cause observed galaxy shapes to be distorted.
@@
 From the three dimensional density contrast $\delta$, the two dimensional lensing potential $\Phi$ can be inferred by solving the Poisson equation
+%ZH: I added potential above -- technically it's the total potential that matters
 
@@
 %
-Where $\kappa,\pmb{\gamma}$, and $\omega$ refer respectively to the WL cosmic convergence, shear and sky position angle.
+Where $\kappa,\pmb{\gamma}$, and $\omega$ refer respectively to the WL cosmic convergence, shear and rotation.
 %rotation angle. 
 %ZH: not sure what you mean by rotation angle.  I replaced it by sky position
+%AP: I meant rotation angle, see email attached figure for reference
 The implicit solution (\ref{sim:geosol}) to the geodesic equation (\ref{sim:geodiff}) can be translated in an integral equation for the lensing Jacobian
@@
 \label{sim:ll}
-\kappa_{\rm ll}(\pt,\chi_s) = \int_0^{\chi_s}d\chi\int_0^\chi d\chi' \chi\chi' W(\chi,\chi_s)W(\chi',\chi)\Phi_{ij}(\chi\pt,\chi)\Phi_{ij}(\chi'\pt,\chi'),
+\kappa_{\rm ll}(\pt,\chi_s) = -2\int_0^{\chi_s}d\chi\int_0^\chi d\chi' \chi\chi' W(\chi,\chi_s)W(\chi',\chi)\Phi_{ij}(\chi\pt,\chi)\Phi_{ij}(\chi'\pt,\chi'),
 \end{equation}
@@
 \label{sim:gp}
-\kappa_{\rm geo}(\pt,\chi_s) = \frac{3H_0^2\Omega_m}{2c^2}\int_0^{\chi_s}d\chi\int_0^\chi d\chi' \frac{\chi\chi'}{a(\chi')} W(\chi,\chi_s)W(\chi',\chi)\nabla_\perp\Phi(\chi\pt,\chi)\cdot\nabla_\perp\delta(\chi'\pt,\chi').
+\kappa_{\rm geo}(\pt,\chi_s) = -\frac{3H_0^2\Omega_m}{c^2}\int_0^{\chi_s}d\chi\int_0^\chi d\chi' \frac{\chi\chi'}{a(\chi')} W(\chi,\chi_s)W(\chi',\chi)\nabla_\perp\Phi(\chi\pt,\chi)\cdot\nabla_\perp\delta(\chi'\pt,\chi').
 \end{equation}
@@
 \multicolumn{4}{c}{\textbf{Fiducial}} \\ \hline
-0.26 & -1 & 0.8 & 8192 \\ \hline
+0.26 & $-1$ & 0.8 & 8192 \\ \hline
 
 \multicolumn{4}{c}{\textbf{Variations}} \\ \hline
-0.29 & -1 & 0.8 & 1024 \\
-0.26 & -0.8 & 0.8 & 1024 \\
-0.26 & -1 & 0.9 & 1024 \\ \hline
+0.29 & $-1$ & 0.8 & 1024 \\
+0.26 & $-0.8$ & 0.8 & 1024 \\
+0.26 & $-1$ & 0.9 & 1024 \\ \hline
 
@@
 
-We add galaxy shape noise to our $\kappa$ mocks in the form of a pixel uncorrelated white Gaussian noise \citep{SongKnox} with r,r.m.s.
+We add galaxy shape noise to our $\kappa$ mocks in the form of a pixel uncorrelated white Gaussian noise \citep{SongKnox} with a root mean square of
 \begin{equation}
@@
 %
-where the number of galaxies per pixel $N_g$ is based on a galaxy angular density of $15\,{\rm arcmin}^{-2}$. 
+where $N_g$ is the number of galaxies per pixel. 
 %ZH(***): 15 is pretty conservative for LSST.
@@
 %ZH: it is very hard to read the labels inside the figure legend.  Please increase the size.  I also scaled the figure to be larger overall:
-%\includegraphics[scale=0.3]{Figures/powerResiduals.eps}
 \includegraphics[scale=0.45]{Figures/powerResiduals.eps}
@@
 %ZH: same here -- hard to read the labels inside the figure legend.  Please increase the size.  I also scaled the figure to be larger overall:
-%\includegraphics[scale=0.4]{Figures/delta_m2.eps}
-%\includegraphics[scale=0.4]{Figures/delta_m5.eps}
 \includegraphics[scale=0.46]{Figures/delta_m2.eps}\includegraphics[scale=0.46]{Figures/delta_m5.eps}
 \end{center}
-%ZH(***): I think we could delete the solid green/red. For me they are more confusing than helpful -- but lets discuss.  
 \caption{Dominant post--Born corrections to the $\kappa$ skewness and kurtosis due to lens--lens coupling and geodesic perturbation, as a function of the scale $\theta_G$ of the Gaussian smoothing window.
@@
 The top/middle/bottom rows show examples of 2nd, 3rd, and 4th-order moments.
-%
 We show both the PDFs obtained with full ray--tracing (blue) and the Born approximation (green).
@@
 We show parameter estimates obtained using the noiseless $\kappa$ power spectrum (top panels), the noiseless $\kappa$ moments defined in eq.~(\ref{par:moments}) (middle panels) and the noisy $\kappa$ moments, based on a galaxy density of $15\,{\rm arcmin}^{-2}$ (bottom panels).
+We do not show results from the noisy power spectrum, because the noiseless power spectrum is already unbiased.
 %ZH: Added this:
-We do not show results from the noisy power spectrum, because the noiseless power spectrum is already unbiased.
 %
@@
 \end{figure*}
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.4]{Figures/bias_ngal_convergence_momentsSN_s50_nb9.eps}
+\end{center}
+\caption{Parameter bias dependence on the galaxy density angular $n_g$ used to compute the shape noise rms in eq.
+(\ref{par:shaperms}).
+The plotted quantity is the difference between the mean of 1000 parameter fits using the estimator (\ref{par:fisherest}) with $\bb{M}$ measured with and without the Born approximation.
+The difference is shown in units of the estimator standard deviation.
+We show the trend for $\Omega_m$ (blue), $w_0$ (red) and $\sigma_8$ (green).}
+\label{fig:parbiasSN}
+\end{figure}
 
@@
 Figure \ref{fig:psResiduals} shows the magnitudes of the $O(\Phi^3)$ post--Born corrections to the convergence power spectrum.
-
 A similar analysis can be carried out for the various skewness and kurtosis moments of the $\kappa$ field.
@@
 The results are shown in Figure \ref{fig:parbias}.
+We also studied how our conclusions are influenced by the survey angular galaxy density $n_g$, which controls the amplitude of the shape noise in the $\kappa$ reconstruction.
+The dependence of moments--based parameter biases on $n_g$ is shown in Figure \ref{fig:parbiasSN}.
 
@@
 Figure \ref{fig:csample} shows that the dominant post--Born correction to the $\kappa$ reconstruction comes from the geodesic term (eq.~\ref{sim:gp}).
-This can be seen by looking at the lens-lens term, which is aver an order of magnitude smaller
+This can be seen by looking at the lens-lens term, which is aver an order of magnitude smaller than the geodesic term, and by looking at the full $\kappa-\kappa_{\rm born}$ residuals, which show a very similar overall level, as well as structural detail, to the ones found in the $\kappa_{\rm geo}$ map.
 %ZH: I changed above to ``over an order of magnitude''
- than the geodesic term, and by looking at the full $\kappa-\kappa_{\rm born}$ residuals, which show a very similar overall level, as well as structural detail, to the ones found in the $\kappa_{\rm geo}$ map.
 
@@
 Figure \ref{fig:skResiduals} shows that the geodesic and lens--lens contributions to the $\kappa$ skewness and kurtosis are comparable and that the lowest non--trivial post--Born corrections can fully account for the discrepancy between the Born--approximated quantities and the fully ray--traced ones.
-%ZH(***): I do not understand the sentences below.  Let's discuss.  I think we could possibly delete the solid lines from these figures, and this discussion?
 Figs.
-\ref{fig:psResiduals} and \ref{fig:skResiduals} indicate that the post--Born perturbation series breaks down at high orders in the potential.
-In particular geodesic perturbations cannot be predicted accurately by a perturbation series, higher orders in $\Phi$ dominating over smaller orders.
-This is not an important limitation, however, as the computational cost of the $O(\Phi^2)$ line--of--sight integrals is roughly the same as for ray--tracing (Table \ref{tab:benchmarks}).
+\ref{fig:psResiduals} and \ref{fig:skResiduals} indicate that the post--Born perturbation series breaks down for the geodesic correction.
+In particular, higher-order terms, involving $\langle \kappa \kappa_{\rm geo}^2\rangle$, cause large deviations (as seen by the difference between the solid and dashed green curves).
+Therefore, in practice, in order to go beyond Born approximation, it is more advantageous, both for accuracy and for CPU time, to perform full ray--tracing (whose computational cost is comparable to those of the $O(\Phi^2)$ line--of--sight integrals; Table \ref{tab:benchmarks}).
 
@@
 The middle row of panels in Figure \ref{fig:parbias} shows that indeed the constraints from the moments are $\approx$ 3 times tighter than from the power spectrum (seen by the narrow widths of the PDFs).
-As a result, highly significant
-%
-biases are observed when fitting a real observation with Born--approximated $\kappa$ moments.
-The bias however disappears when introducing galaxy shape noise, due to the resulting increased statistical error.
+As a result, highly significant biases are observed when fitting a real observation with Born--approximated $\kappa$ moments.
+The bias however disappears when introducing galaxy shape noise, due to the resulting increased statistical error, as can be seen in Figure \ref{fig:parbiasSN}.
+The Figure shows that even for galaxy angular densities as high as $\approx 60\,{\rm arcmin}^{-2}$, that will be achievable in future surveys such as WFIRST \citep{WFIRST}, Born--induced parameter biases are within the one sigma margin.
 This result leads us to the conclusion that the Born approximation is sufficient for future WL analyses.

### 2016-11-22 Paper/Figures/generate.py

@@ -110,8 +110,8 @@ def powerResiduals(cmd_args,collection="c0",fontsize=22):
 	ax[1].plot(ell,ell*(ell+1)*np.abs(pLL_cross.mean(0))/np.pi,label=r"$2{\rm born}\times{\rm ll}$")
 
 	#Labels
-	for n in (0,1):
-		ax[n].legend(loc="upper left",prop={"size":15})
+	ax[0].legend(loc="lower right",prop={"size":20})
+	ax[1].legend(loc="upper left",prop={"size":20})
 
 	for n in (0,1):
 		ax[n].set_xscale("log")
@@ -161,7 +161,7 @@ def plotSmooth(cmd_args,lines,collection="c0",moment=2,smooth=(0.5,1.,2.,3.,5.,7
 	#Labels
 	ax.set_xlabel(r"$\theta_G({\rm arcmin})$",fontsize=fontsize)
 	ax.set_ylabel(ylabel,fontsize=fontsize)
-	ax.legend(loc="upper center",prop={"size":13})
+	ax.legend(bbox_to_anchor=(0., 1.02, 1., .102),loc=3,ncol=2,mode="expand", borderaxespad=0.)
 
 	#Save
 	fig.savefig("delta_m{0}.{1}".format(moment,cmd_args.type))
@@ -173,7 +173,7 @@ def plotSmoothSkew(cmd_args,collection="c0",smooth=(0.5,1.,2.,3.,5.,7.,10.),font
 	#Lines to plot
 	lines = {
 
-	r"$\kappa^3_{\rm full}-\kappa^3_{\rm born}$" : ("kappa",("convergence_moments_s{0}_nb9.npy",),moment,True,"denim blue","-",0),
+	r"$\kappa^3_{\rm ray}-\kappa^3_{\rm born}$" : ("kappa",("convergence_moments_s{0}_nb9.npy",),moment,True,"denim blue","-",0),
 	r"$\kappa^3_{\rm born+geo}-\kappa^3_{\rm born}$" : ("kappaB+GP",("convergence_moments_s{0}_nb9.npy",),moment,True,"medium green","-",1),
 	r"$\kappa^3_{\rm born+ll}-\kappa^3_{\rm born}$" : ("kappaB+LL",("convergence_moments_s{0}_nb9.npy",),moment,True,"pale red","-",2),
[…]

### 2016-11-23 Paper/paper.tex
incorporated suggestions

@@
 \begin{center}
-\includegraphics[scale=0.4]{Figures/bias_ngal_convergence_momentsSN_s50_nb9.eps}
+\includegraphics[scale=0.45]{Figures/bias_ngal_convergence_momentsSN_s50_nb9.eps}
 \end{center}
@@
 This can be seen by looking at the lens-lens term, which is aver an order of magnitude smaller than the geodesic term, and by looking at the full $\kappa-\kappa_{\rm born}$ residuals, which show a very similar overall level, as well as structural detail, to the ones found in the $\kappa_{\rm geo}$ map.
+The reader might have noticed the curious alignment feature in Figure \ref{fig:csample}, in which all the dipolar structures in $\kappa_{\rm geo}$ appear to be horizontally aligned throughout the field of view.
+We believe that this alignment is not a numerical effect, but is originated physically by the $\nabla\delta$ terms in eq.~(\ref{sim:gp}).
+Early in the line--of--sight integration, the field of view covers a very small section of the simulation box ($\sim7\,{\rm Mpc}$ for the first lens), within which dipolar structures are aligned.
+These alignments survive after the full integration is completed due to the $\nabla\delta\cdot\nabla\Phi$ term, which couples lenses at different redshifts.
+To provide evidence that the closest lenses to the observer are responsible for the alignment features, we performed the line--of--sight integration for $\kappa_{\rm geo}$ by rotating the first 5 lenses by 90 degrees.
+This is sufficient to coherently flip the dipolar structures from horizontal to vertical throughout the field of view.
 %ZH: I changed above to ``over an order of magnitude''
@@
 However, this bias becomes negligible when galaxy shape noise is added, due to an increased scatter in parameter estimates.
+This conclusion holds even for future space--based surveys that can probe galaxy angular densities as high as $60\,{\rm arcmin}^{-2}$.
 \end{itemize}
 %
-Future prospects involve study the Born approximation validity for CMB lensing observations. 
+In this work we examined the validity of the Born approximation for WL galaxy surveys, but a similar study could in principle be carried for the lensing potential reconstruction from CMB temperature and polarization data.
+Lensing of the CMB probes structures over a wider range of redshifts and hence CMB lensing observables can be expected to be more Gaussian distributed than their galaxy lensing counterparts.
+This suggests the possibility that non--Gaussian features in CMB lensing data could come from post--Born corrections of $O(\Phi^2)$ rather than inherent non--Gaussianity in the Born $O(\Phi)$ terms.
+This possibility has been suggested by \citep{CMBPrattenLewis}, who looked at the CMB lensing $\kappa$ bi--spectrum.
+Because of the high significance with which non--Gaussianities in the CMB lensing potential can be detected with future Stage IV experiments \citep{CMBLNG}, we propose to investigate post--Born corrections to CMB lensing observables in future work.
+
 %ZH(***): we should add 2-3 sentences here, saying that we expect Born approximation to fail more badly in CMB lensing, and cite papers that recently showed this already (e.g.
@@
 You could steal this from the discussion section of our recent CMB lensing paper (with Jia, Colin, etc).
+%AP: does this work?
 

### 2016-11-28 Paper/paper.tex
incorporated latest comments

@@
 
-%ZH: I added beyond-Gaussian to distinguish ourselves from prior studies on 2-pt statistics:
 \title{On the validity of the Born approximation for beyond-Gaussian weak lensing observables}
@@
 
-%ZH: grammatical comment:  when you have two nested adjectives in front of a subject, 
-%    you should always hyphenate  (lowest-order X, ... real-space X, etc...)
 This paper is organized as follows.
@@
 From the three dimensional density contrast $\delta$, the two dimensional lensing potential $\Phi$ can be inferred by solving the Poisson equation
-%ZH: I added potential above -- technically it's the total potential that matters
 
@@
 \label{sim:poisson}
-\nabla_\perp^2\Phi(\bb{x}_\perp,\chi) = \frac{3H_0^2\Omega_m}{2c^2a(\chi)} \delta(\bb{x}_\perp,\chi)
+\nabla_\perp^2\Phi(\bb{x}_\perp,\chi) = \frac{3H_0^2\Omega_m}{2c^2a(\chi)} \delta(\bb{x}_\perp,\chi).
 \end{equation} 
@@
 WL observables are related to the differential deflection that nearby light rays experience when traveling from the observer to the source.
-Indicating with $\pt$ the starting angular position of a light ray at $\chi=0$ and with $\pmb{\beta}_s$ the angular position of the light ray at $\chi=\chi_s$, we are interested in the Jacobian matrix $\bb{A}_s(\pt)=\partial\pmb{\beta}_s(\pt)/\partial \pt$, which is usually parametrized as
+Indicating with $\pt$ the starting angular position of a light ray at $\chi=0$ and with $\pmb{\beta}_s$ the angular position of the light ray at $\chi=\chi_s$, we are interested in the Jacobian matrix $\bb{A}_s(\pt)=\partial\pmb{\beta}_s(\pt)/\partial \pt$, which can be parametrized as
 
 \begin{equation}
+\label{sim:lensjac}
 \bb{A}_s(\pt) = 
 \begin{pmatrix}
-%ZH: I changed gamma^i to gamma_i  (this is more conventional and avoids confusion of gamma^2 with square of gamma).
+%
 1-\kappa(\pt)-\gamma_1(\pt) & -\gamma_2(\pt) + \omega(\pt) \\
@@
 %
-Where $\kappa,\pmb{\gamma}$, and $\omega$ refer respectively to the WL cosmic convergence, shear and rotation.
-%rotation angle. 
-%ZH: not sure what you mean by rotation angle.  I replaced it by sky position
-%AP: I meant rotation angle, see email attached figure for reference
-The implicit solution (\ref{sim:geosol}) to the geodesic equation (\ref{sim:geodiff}) can be translated in an integral equation for the lensing Jacobian
+Where $\kappa$, and $\pmb{\gamma}$ refer respectively to the WL
+convergence and shear, and $\omega$ to the rotation angle (which is
+$O(\Phi^2)$ and is often excluded from the parametrization in eq.~(\ref{sim:lensjac})).  The implicit solution
+(\ref{sim:geosol}) to the geodesic equation (\ref{sim:geodiff}) can be
+translated in an integral equation for the lensing Jacobian
 
@@
 The integral in (\ref{sim:jacsol}) can be approximated using a series expansion in powers of $\Phi$, which can yield acceptable results in the limit in which $\Phi$ is small.
-To compute the lowest--order approximation to
-%ZH: in many places you missed ``eq'' from in front of the equation number.  I tried to add all of them, but you could check if I still missed some.
-eq.~(\ref{sim:jacsol}) one notes that the lensing potential appears on the right hand side and hence we can replace the Jacobian on the right hand side with its zeroth order expression, i.e.
+To compute the lowest--order approximation to eq.~(\ref{sim:jacsol}) one notes that the lensing potential appears on the right hand side and hence we can replace the Jacobian on the right hand side with its zeroth order expression, i.e.
 the identity matrix.
@@
 \caption{Sample convergence outputs for one realization of a $(3.5\,{\rm deg})^2$ field, with source galaxies at redshift $z_s=2$.
-%ZH: Added z_s above.
 The figure shows the convergence profile (top left), along with the Born approximation residuals (top right), the lens-lens post--Born contribution (bottom left) and the geodesic contribution (bottom right).
@@
 Note the different scales in the bottom panels: the geodesic term (right), is over an order of magnitude larger than the lens--lens term (left), and is comparable in level and detailed structure to the full residual (top right).}
-%ZH: Added above sentence
 \label{fig:csample}
@@
 where $N_g$ is the number of galaxies per pixel.
-%ZH(***): 15 is pretty conservative for LSST.
-I thought it would be closer to 30-40 --- and WFIRST is talking about 70-80.
-Would this smaller noise change the conclusions about the moments being unbiased??
 
@@
 \begin{center}
-%ZH: it is very hard to read the labels inside the figure legend.  Please increase the size.  I also scaled the figure to be larger overall:
 \includegraphics[scale=0.45]{Figures/powerResiduals.eps}
@@
 \begin{center}
-%ZH: same here -- hard to read the labels inside the figure legend.  Please increase the size.  I also scaled the figure to be larger overall:
 \includegraphics[scale=0.46]{Figures/delta_m2.eps}\includegraphics[scale=0.46]{Figures/delta_m5.eps}
@@
 \begin{center}
-%ZH: I enlarged the figure 0.25->0.3
-%ZH: Can you capitalize the label ``born'' to ``Born'' in the figure legends?
-%ZH: Also, the x-labels like 0.00000185 look weird.  Can you change them to 1.85e-5 etc, like in the bottom panel with 1e-10 units ?
 \includegraphics[scale=0.3]{Figures/pdfMoments.eps}
@@
 \caption{Probability distribution function (PDF) of the 9 $\kappa$ moments defined in eq.~(\ref{par:moments}), over 8192 realizations of the fiducial cosmological model $\bb{p}_0$.
-%ZH: added this:
 The top/middle/bottom rows show examples of 2nd, 3rd, and 4th-order moments.
@@
 We do not show results from the noisy power spectrum, because the noiseless power spectrum is already unbiased.
-%ZH: Added this:
-%
 In each panel, we show both a control case, in which the mock observation has been constructed with the Born approximation (blue), and the ``real'' case, in which the observation has been constructed with full ray--tracing (green).}
@@
 This is sufficient to coherently flip the dipolar structures from horizontal to vertical throughout the field of view.
-%ZH: I changed above to ``over an order of magnitude''
 
@@
 Figure \ref{fig:parbias} studies this possibility and shows that, while the Born approximation is sufficient to fit cosmology with the power spectrum of an LSST--like survey, even in the noiseless case, the same is not true for the higher $\kappa$ moments.
-%ZH: Added below:
 We have previously shown that these moments contain significantly more information than the power spectrum \citep{MinkPetri}; an expectation that was confirmed when fitting the CFHTLenS data~\citep{CFHTMink}.
@@
 \item Using the \ttt{LensTools} software package, Born integration costs 4 times less than ray--tracing, and consumes about half as much memory.
-%ZH: Added memory above. OK?
 \item The $\kappa$ power spectrum leads to negligible parameter bias for an LSST--like survey, even in the noiseless case.
@@
 
-%ZH(***): we should add 2-3 sentences here, saying that we expect Born approximation to fail more badly in CMB lensing, and cite papers that recently showed this already (e.g.
-by Anthony Lewis).
-You could steal this from the discussion section of our recent CMB lensing paper (with Jia, Colin, etc).
-%AP: does this work?
-
 %%%%%%%%%%%%%%%%%%%%%%%%%% ACKNOWLEDGMENTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We thank the LSST Dark Energy Science Collaboration (DESC) for the allocation of time.
-The ray--tracing simulations and parameter estimation calculations were performed at the NSF XSEDE facility, supported by grant number
-ACI-1053575, and at the New York Center for Computational Sciences, a
-cooperative effort between Brookhaven National Laboratory and Stony
-Brook University, supported in part by the State of New York. This
-work was supported in part by the U.S. Department of Energy under
-Contract No. DE-SC00112704, the NSF Grant
-No. AST-1210877 (to Z.H.), the Research Opportunities and
-Approaches to Data Science (ROADS) program at the Institute for Data
-Sciences and Engineering at Columbia University (to Z.H.) and a Simons Fellowship in Theoretical Physics (to Z.H.).
+The ray--tracing simulations and parameter estimation calculations were performed at the NSF XSEDE facility, supported by grant number ACI-1053575, and at the New York Center for Computational Sciences, a cooperative effort between Brookhaven National Laboratory and Stony Brook University, supported in part by the State of New York.
+This work was supported in part by the U.S.
+Department of Energy under Contract No.
+DE-SC00112704, the NSF Grant No.
+AST-1210877 (to Z.H.), the Research Opportunities and Approaches to Data Science (ROADS) program at the Institute for Data Sciences and Engineering at Columbia University (to Z.H.) and a Simons Fellowship in Theoretical Physics (to Z.H.).
 

### 2016-11-29 Paper/paper.tex
incorporated latest batch of comments

@@
 \author{Morgan May}
+\affiliation{Department of Physics, Columbia University, New York, NY 10027, USA}
 \affiliation{Physics Department, Brookhaven National Laboratory, Upton, NY 11973, USA}
@@
 Numerical efforts for feature forward modeling are based on ray--tracing simulations that make use of the multi--lens--plane algorithm \citep{RayTracingJain,RayTracingHartlap} to predict cosmic shear from outputs of $N$--body simulations.
-Approximate techniques based on the Born approximation allow for a computationally cheaper, but potentially inaccurate, forward modeling \citep{RayTracingHartlap} which requires only knowledge of the matter density contrast integrated along the observer unperturbed line of sight.
+Approximate techniques based on the Born approximation allow for a computationally faster, but potentially inaccurate, forward modeling \citep{RayTracingHartlap} which requires only knowledge of the matter density contrast integrated along the observer unperturbed line of sight.
 A variety of groups have studied the validity of the Born approximation for forward modeling of convergence power spectra and bi--spectra \citep{WLBispectrumDodelson}, spectra of WL cosmic flexions \citep{BornFlexion} and, in more recent work, CMB lensing bi--spectra \citep{CMBPrattenLewis}.
@@
 Light ray trajectories correspond to null geodesics in the space--time metric induced by the density fluctuations $\delta(\bb{x}_\perp,\chi)$.
-It can be shown that with the spacetime parametrization adopted in this section, the geodesic equation takes the form (see \citep{BornFlexion} for a possible reference)
+It can be shown that with the spacetime parametrization adopted in this section, the geodesic equation takes the form (see \citep{BornFlexion})
 
@@
 The exact solution of (\ref{sim:geodiff}) based on (\ref{sim:jacsol}) is computationally expensive because it requires knowledge of the lensing potential $\Phi$.
-In the next paragraph we review the details of a computationally cheaper but approximate approach based on the Born approximation.
+In the next paragraph we review the details of a computationally faster but approximate approach based on the Born approximation.
 
@@
 The Born--approximated convergence in eq.~(\ref{sim:born}) has a simple interpretation: at lowest order in the lensing potential, $\kappa$ is the integrated matter density on the unperturbed line of sight, weighted by the lensing kernel $W$.
-Contrary to the exact ray--tracing approach, the Born approximation does not require knowledge of the solution to the Poisson equation (\ref{sim:poisson}) and is hence computationally cheaper.
+Contrary to the exact ray--tracing approach, the Born approximation does not require knowledge of the solution to the Poisson equation (\ref{sim:poisson}) and is hence computationally faster.
 In the next paragraph we examine the corrections to the Born approximation that come at second order in the potential $\Phi$.
@@
 %
-the maximum likelihood parameter estimator in eq.~(\ref{par:fisherest}) is given by (see \citep{DodelsonSchneider13,PetriVariance} for example)
+the maximum likelihood parameter estimator is given by (see \citep{DodelsonSchneider13,PetriVariance} for example)
 \begin{equation}
@@
 We do not show results from the noisy power spectrum, because the noiseless power spectrum is already unbiased.
-In each panel, we show both a control case, in which the mock observation has been constructed with the Born approximation (blue), and the ``real'' case, in which the observation has been constructed with full ray--tracing (green).}
+In each panel, we show both a control case, in which the mock observation has been constructed with the Born approximation (blue), and the ``real'' case, in which the observation has been constructed with full ray--tracing (green).
+The $\kappa$ power spectrum from which the constraints in the upper panel have been derived, has been measured in 100 uniformly spaced bands with $\ell \in [150,10000]$}
 \label{fig:parbias}
@@
 Figure \ref{fig:csample} shows that the dominant post--Born correction to the $\kappa$ reconstruction comes from the geodesic term (eq.~\ref{sim:gp}).
-This can be seen by looking at the lens-lens term, which is aver an order of magnitude smaller than the geodesic term, and by looking at the full $\kappa-\kappa_{\rm born}$ residuals, which show a very similar overall level, as well as structural detail, to the ones found in the $\kappa_{\rm geo}$ map.
+This can be seen by looking at the lens-lens term, which is over an order of magnitude smaller than the geodesic term, and by looking at the full $\kappa-\kappa_{\rm born}$ residuals, which show a very similar overall level, as well as structural detail, to the ones found in the $\kappa_{\rm geo}$ map.
 The reader might have noticed the curious alignment feature in Figure \ref{fig:csample}, in which all the dipolar structures in $\kappa_{\rm geo}$ appear to be horizontally aligned throughout the field of view.
@@
 Figure \ref{fig:pdfMoments} shows the PDF of the 9 $\kappa$ moments defined in eq.~(\ref{par:moments}) over 1000 realizations of an LSST--like survey.
-This figure clearly shows that, while the Born approximation is a good predictor of the quadratic moments $\pmb{\mu}_2$ within one standard deviation, the higher moments $\pmb{\mu}_3,\pmb{\mu}_4$ show $2\div 3\sigma$ deviations from their Born--approximated counterparts.
+This figure clearly shows that, while the Born approximation is a good predictor of the quadratic moments $\pmb{\mu}_2$ within one standard deviation, the higher moments $\pmb{\mu}_3,\pmb{\mu}_4$ show 2 to 3$\sigma$ deviations from their Born--approximated counterparts.
 This can lead to parameter biases when fitting observations.
@@
 This result leads us to the conclusion that the Born approximation is sufficient for future WL analyses.
-This approach also has the advantage of being 4 times computationally cheaper than full ray--tracing, as we show in Table \ref{tab:benchmarks} for a selected reference test case.
+This approach also has the advantage of being 4 times computationally faster than full ray--tracing, as we show in Table \ref{tab:benchmarks} for a selected reference test case.
 
@@
 \item Using the \ttt{LensTools} software package, Born integration costs 4 times less than ray--tracing, and consumes about half as much memory.
-\item The $\kappa$ power spectrum leads to negligible parameter bias for an LSST--like survey, even in the noiseless case.
+\item The Born approximation for the $\kappa$ power spectrum leads to negligible parameter bias for an LSST--like survey, even in the noiseless case.
 \item Fitting an observation with Born--approximated higher $\kappa$ moments leads to significant bias in the $(\Omega_m,w_0,\sigma_8)$ triplet in the noiseless case.

### 2016-11-29 Paper/Figures/generate.py

@@ -176,9 +176,9 @@ def plotSmoothSkew(cmd_args,collection="c0",smooth=(0.5,1.,2.,3.,5.,7.,10.),font
 	r"$\kappa^3_{\rm ray}-\kappa^3_{\rm born}$" : ("kappa",("convergence_moments_s{0}_nb9.npy",),moment,True,"denim blue","-",0),
 	r"$\kappa^3_{\rm born+geo}-\kappa^3_{\rm born}$" : ("kappaB+GP",("convergence_moments_s{0}_nb9.npy",),moment,True,"medium green","-",1),
 	r"$\kappa^3_{\rm born+ll}-\kappa^3_{\rm born}$" : ("kappaB+LL",("convergence_moments_s{0}_nb9.npy",),moment,True,"pale red","-",2),
-	r"$3\kappa^2_{\rm born}\kappa_{\rm geo}$" : ("kappaBorn",("cross_skewGP_s{0}_nb1.npy",),0,False,"medium green","--",3),
-	r"$3\kappa^2_{\rm born}\kappa_{\rm ll}$" : ("kappaBorn",("cross_skewLL_s{0}_nb1.npy",),0,False,"pale red","--",4),
-	r"$3\kappa^2_{\rm born}\kappa_{\rm ll}+3\kappa^2_{\rm born}\kappa_{\rm geo}$" : ("kappaBorn",("cross_skewLL_s{0}_nb1.npy","cross_skewGP_s{0}_nb1.npy"),0,False,"denim blue","--",5),
+	r"$3\kappa^2_{\rm born}\kappa_{\rm geo}$" : ("kappaBorn",("cross_skewGP_s{0}_nb1.npy",),0,False,"medium green","--",4),
+	r"$3\kappa^2_{\rm born}\kappa_{\rm ll}$" : ("kappaBorn",("cross_skewLL_s{0}_nb1.npy",),0,False,"pale red","--",5),
+	r"$3\kappa^2_{\rm born}\kappa_{\rm ll}+3\kappa^2_{\rm born}\kappa_{\rm geo}$" : ("kappaBorn",("cross_skewLL_s{0}_nb1.npy","cross_skewGP_s{0}_nb1.npy"),0,False,"denim blue","--",3),
 
 	}
 
@@ -194,9 +194,9 @@ def plotSmoothKurt(cmd_args,collection="c0",smooth=(0.5,1.,2.,3.,5.,7.,10.),font
[…]

### 2016-11-29 Paper/paper.tex
benchmark table caption

@@
 \caption{CPU time and memory usage benchmarks for the convergence reconstruction operations.
-The test case we considered consists in a discretization with 42 uniformly spaced lenses between the observer and the sources at $z_s=2$, each with a resolution of $4096^2$ pixels.
+The test case we considered consists in a discretization with $N_l=42$ uniformly spaced lenses between the observer and the sources at $z_s=2$, each with a resolution of $4096^2$ pixels.
 The $\kappa$ field is resolved with $2048^2$ light rays.
-We show both the runtime for producing a single field of view and the CPU hours needed to perform the reconstruction 1000 times, to mock an LSST--like galaxy survey.}
+We show both the runtime for producing a single field of view and the CPU hours needed to perform the reconstruction 1000 times, to mock an LSST--like galaxy survey.
+Run times do not include the Poisson solution calculation, as this can be recycled to produce multiple field of view realizations.
+The Poisson solution run time is negligible in the account of the total CPU time needed for the production of $N_r\gg N_l$ field of view realizations.}
 \label{tab:benchmarks}

### 2016-11-30 Paper/paper.tex
added note on sampling procedure

@@
 This is true for upcoming large area surveys such as LSST \citep{LSST}, WFIRST \citep{WFIRST} and Euclid \citep{Euclid}.
-In this work we use $N$--body simulations coupled with the \ttt{LensTools} routines to simulate multiple realizations of a convergence field $\h{\kappa}(\pt)$ for different combinations of the cosmological parameter triplet $(\Omega_m,w_0,\sigma_8)$.
+In this work we use $N$--body simulations coupled with the \ttt{LensTools} routines to simulate multiple realizations (using a sampling procedure analogous to the one outlined in \citep{PetriVariance}) of a convergence field $\h{\kappa}(\pt)$ for different combinations of the cosmological parameter triplet $(\Omega_m,w_0,\sigma_8)$.
 We choose the values $\bbh{p}_0=(0.26,-1,0.8)$ as our fiducial cosmological parameters and vary one parameter at a time as in Table \ref{tab:cosmopar} to measure the feature derivatives $\bb{M}$.

### 2016-12-08 Paper/paper.tex
incorporated uros comments + citation

@@
 In this work, we use simulations to show that deviations of the Born--approximated convergence power spectrum, skewness and kurtosis from their fully ray--traced counterparts are consistent with the smallest non--trivial post--Born corrections (so-called geodesic and lens-lens terms).
-We find, however, that the perturbative approach for the geodesic correction breaks down at higher orders.
+We find, however, that the perturbative approach for the geodesic correction \textbf{\color{red} does not correctly predict convergence moments} at higher orders.
 We also find that cosmological parameter biases induced by the Born approximation are negligible even for an LSST--like survey, once galaxy shape noise is considered, and we conclude that the Born approximation is sufficient for future galaxy WL analyses.
@@
 Approximate techniques based on the Born approximation allow for a computationally faster, but potentially inaccurate, forward modeling \citep{RayTracingHartlap} which requires only knowledge of the matter density contrast integrated along the observer unperturbed line of sight.
-A variety of groups have studied the validity of the Born approximation for forward modeling of convergence power spectra and bi--spectra \citep{WLBispectrumDodelson}, spectra of WL cosmic flexions \citep{BornFlexion} and, in more recent work, CMB lensing bi--spectra \citep{CMBPrattenLewis}.
+A variety of groups have studied the validity of the Born approximation for forward modeling of convergence power spectra \citep{HirataKrause} and bi--spectra \citep{WLBispectrumDodelson}, spectra of WL cosmic flexions \citep{BornFlexion} and, in more recent work, CMB lensing bi--spectra \citep{CMBPrattenLewis}.
 In this work, we study the validity of the Born approximation for forward modeling a subset of low--order moments of the real--space convergence field.
@@
 Figs.
-\ref{fig:psResiduals} and \ref{fig:skResiduals} indicate that the post--Born perturbation series breaks down for the geodesic correction.
-In particular, higher-order terms, involving $\langle \kappa \kappa_{\rm geo}^2\rangle$, cause large deviations (as seen by the difference between the solid and dashed green curves).
+\ref{fig:psResiduals} and \ref{fig:skResiduals} indicate \textbf{\color{red} that truncating $\kappa$ at $O(\Phi^2)$ post--Born terms, leads to inaccurate predictions of the power spectrum and moments.
+In particular, higher-order terms involving $\langle \kappa_{\rm born}^n \kappa_{\rm ll}^m \kappa_{\rm geo}^2\rangle$ and higher, cause large deviations (as seen by the difference between the solid and dashed green curves) that, in an exact approach, are canceled by $O(\Phi^3)$ corrections to $\kappa$, as pointed out by \citep{HirataKrause}}.
 Therefore, in practice, in order to go beyond Born approximation, it is more advantageous, both for accuracy and for CPU time, to perform full ray--tracing (whose computational cost is comparable to those of the $O(\Phi^2)$ line--of--sight integrals; Table \ref{tab:benchmarks}).

### 2017-01-17 Paper/paper.tex
removed complex conjugate
add NYU affiliation
edit paper after referee comments

@@
 \affiliation{Department of Astronomy, Columbia University, New York, NY 10027, USA}
+\affiliation{Department of Physics, New York University, New York, NY 10003, USA}
 
@@
 This however is a challenging problem due to the non--linear nature of WL image fields.
-Numerical efforts for feature forward modeling are based on ray--tracing simulations that make use of the multi--lens--plane algorithm \citep{RayTracingJain,RayTracingHartlap} to predict cosmic shear from outputs of $N$--body simulations.
+Numerical efforts for feature forward modeling are based on ray--tracing simulations \textbf{\color{red} that make use of the multi--lens--plane algorithm \citep{RayTracingJain,RayTracingHartlap,RayTracingPN}, or the direct approach \citep{RayTracingBarreira},} to predict cosmic shear from outputs of $N$--body simulations.
 Approximate techniques based on the Born approximation allow for a computationally faster, but potentially inaccurate, forward modeling \citep{RayTracingHartlap} which requires only knowledge of the matter density contrast integrated along the observer unperturbed line of sight.
@@
 \label{par:powerdef}
-\langle\tilde{\kappa}(\pmb{\ell})\tilde{\kappa}^*(\pmb{\ell}')\rangle = (2\pi)^2\delta^D(\pmb{\ell}+\pmb{\ell}')P^{\kappa\kappa}(\ell),
+\langle\tilde{\kappa}(\pmb{\ell})\tilde{\kappa}(\pmb{\ell}')\rangle = (2\pi)^2\delta^D(\pmb{\ell}+\pmb{\ell}')P^{\kappa\kappa}(\ell),
 \end{equation}
@@
 \label{res:powercross}
-\langle\tilde{\kappa}_a(\pmb{\ell})\tilde{\kappa}_b^*(\pmb{\ell}')\rangle = (2\pi)^2\delta^D(\pmb{\ell}+\pmb{\ell}')P_{a,b}^{\kappa\kappa}(\ell).
+\langle\tilde{\kappa}_a(\pmb{\ell})\tilde{\kappa}_b(\pmb{\ell}')\rangle = (2\pi)^2\delta^D(\pmb{\ell}+\pmb{\ell}')P_{a,b}^{\kappa\kappa}(\ell).
 \end{equation} 
@@
 This can be seen by looking at the lens-lens term, which is over an order of magnitude smaller than the geodesic term, and by looking at the full $\kappa-\kappa_{\rm born}$ residuals, which show a very similar overall level, as well as structural detail, to the ones found in the $\kappa_{\rm geo}$ map.
+\textbf{\color{red} When considering a real observation, in which $\kappa$ is estimated from source ellipticities, one should consider an additional reduced shear correction to $\kappa$, which is of order $O(\Phi^2)$ \citep{HirataKrause} and is proportional to $\gamma\kappa$.
+We estimated this correction to be one order of magnitude smaller than the dominant geodesic term}.
 The reader might have noticed the curious alignment feature in Figure \ref{fig:csample}, in which all the dipolar structures in $\kappa_{\rm geo}$ appear to be horizontally aligned throughout the field of view.
@@
 %
-In this work we examined the validity of the Born approximation for WL galaxy surveys, but a similar study could in principle be carried for the lensing potential reconstruction from CMB temperature and polarization data.
+In this work we examined the validity of the Born approximation for WL galaxy surveys, but a similar study could in principle be carried for the lensing potential reconstruction from CMB temperature and polarization data \citep{CMBCalabrese}.
 Lensing of the CMB probes structures over a wider range of redshifts and hence CMB lensing observables can be expected to be more Gaussian distributed than their galaxy lensing counterparts.

### 2017-01-20 batchcode/scripts/measure_from_maps.py
measure reduced shear contribution to power spectrum

@@ -6,7 +6,7 @@ import logging
 import json
 import argparse
 
-from lenstools.image.convergence import ConvergenceMap
+from lenstools import ConvergenceMap,ShearMap
 from lenstools.image.noise import GaussianNoiseGenerator
 
 from lenstools.statistics.ensemble import Ensemble
@@ -38,6 +38,38 @@ def convergence_power(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,
 			conv = conv.smooth(smoothing*u.arcmin,kind="gaussianFFT")
 
 		l,Pl = conv.powerSpectrum(l_edges)
+		return Pl
+
+	except IOError:
+		return None
+
+#################################################################################################################
+##############Reduced shear correction to the power spectrum#####################################################
+#################################################################################################################
+
+def redshear_power(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal=15,smoothing=0.0):
+
+	try:
+		conv = ConvergenceMap.load(map_set.path(fname))
+
+		if "0001r" in fname:
+			np.save(os.path.join(map_set.home_subdir,"num_ell_nb{0}.npy".format(len(l_edges)-1)),conv.countModes(l_edges))
+	
+		if add_shape_noise:
+			gen = GaussianNoiseGenerator.forMap(conv)
+			conv = conv + gen.getShapeNoise(z=z,ngal=ngal*(u.arcmin**-2),seed=hash(os.path.basename(fname))%4294967295)
+
+		if smoothing>0.:
+			conv = conv.smooth(smoothing*u.arcmin,kind="gaussianFFT")
+
+		#Construct shear map, compute kappa*gamma correction, back to convergence
+		shear = ShearMap.fromConvergence(conv)
+		for n in (0,1):
+			shear.data[n]*=conv.data
+		conv2 = shear.convergence()
+
+		#Measure cross
+		l,Pl = conv.cross(conv2,l_edges=l_edges)
 		return Pl
 
 	except IOError:

### 2017-01-23 Paper/Figures/generate.py
add reduced shear trends

@@ -100,23 +100,28 @@ def powerResiduals(cmd_args,collection="c0",fontsize=22):
 	pLL_cross = np.load(os.path.join(fiducial[collection].getMapSet("kappaBorn").home,"cross_powerLL_s0_nb100.npy"))
 	pGP = np.load(os.path.join(fiducial[collection].getMapSet("kappaGP").home,"convergence_power_s0_nb100.npy"))
 	pGP_cross = np.load(os.path.join(fiducial[collection].getMapSet("kappaBorn").home,"cross_powerGP_s0_nb100.npy"))
+	p_redshear_cross = np.load(os.path.join(fiducial[collection].getMapSet("kappaBorn").home,"redshear_power_s0_nb100.npy"))
 
 	#Plot
-	ax[0].plot(ell,ell*(ell+1)*pBorn.mean(0)/(2.*np.pi),label="born")
-	ax[0].plot(ell,ell*(ell+1)*pGP.mean(0)/(2.*np.pi),label="geodesic")
-	ax[0].plot(ell,ell*(ell+1)*pLL.mean(0)/(2.*np.pi),label="lens-lens")
+	ax[0].plot(ell,ell*(ell+1)*pBorn.mean(0)/(2.*np.pi),label=r"${\rm born}$")
+	ax[0].plot(ell,ell*(ell+1)*pGP.mean(0)/(2.*np.pi),label=r"${\rm geodesic}$")
+	ax[0].plot(ell,ell*(ell+1)*pLL.mean(0)/(2.*np.pi),label=r"${\rm lens-lens}$")
 	ax[1].plot(ell,ell*(ell+1)*(np.abs(pFull.mean(0)-pBorn.mean(0)))/(2.0*np.pi),label=r"${\rm ray-born}$")
 	ax[1].plot(ell,ell*(ell+1)*np.abs(pGP_cross.mean(0))/np.pi,label=r"$2{\rm born}\times{\rm geo}$")
 	ax[1].plot(ell,ell*(ell+1)*np.abs(pLL_cross.mean(0))/np.pi,label=r"$2{\rm born}\times{\rm ll}$")
+	ax[1].plot(ell,ell*(ell+1)*np.abs(p_redshear_cross.mean(0))/np.pi,label=r"$2(\kappa\gamma)_{\rm born}$")
+
+	#Shape noise
[…]

### 2017-01-24 batchcode/scripts/measure_from_maps.py
subtract means in reduced shear corrections

@@ -79,6 +79,7 @@ def redshear_skew(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal
 	
 	try:
 		conv = ConvergenceMap.load(map_set.path(fname))
+		conv.data -= conv.data.mean()
 	
 		if add_shape_noise:
 			gen = GaussianNoiseGenerator.forMap(conv)
@@ -103,6 +104,7 @@ def redshear_kurt(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal
 	
 	try:
 		conv = ConvergenceMap.load(map_set.path(fname))
+		conv.data -= conv.data.mean()
 	
 		if add_shape_noise:
 			gen = GaussianNoiseGenerator.forMap(conv)

### 2017-01-25 Paper/paper.tex
finished modifications for resubmission

@@
 A less accurate procedure, based on the Born approximation, only requires knowledge of the density field, and can be implemented more efficiently and at a lower computational cost.
-In this work, we use simulations to show that deviations of the Born--approximated convergence power spectrum, skewness and kurtosis from their fully ray--traced counterparts are consistent with the smallest non--trivial post--Born corrections (so-called geodesic and lens-lens terms).
-We find, however, that the perturbative approach for the geodesic correction \textbf{\color{red} does not correctly predict convergence moments} at higher orders.
-We also find that cosmological parameter biases induced by the Born approximation are negligible even for an LSST--like survey, once galaxy shape noise is considered, and we conclude that the Born approximation is sufficient for future galaxy WL analyses.
+\textbf{\color{red} In this work, we use simulations to show that deviations of the Born--approximated convergence power spectrum, skewness and kurtosis from their fully ray--traced counterparts are consistent with the smallest non--trivial $O(\Phi^3)$ post--Born corrections (so-called geodesic and lens-lens terms).
+In this work, we use simulations to show that deviations of the Born--approximated convergence power spectrum, skewness and kurtosis from their fully ray--traced counterparts are consistent with the smallest non--trivial post--Born corrections.
+Our results imply a cancelation among the larger $O(\Phi^4)$ (and higher order) terms, consistent with previous analytic work.} We also find that cosmological parameter biases induced by the Born approximation are negligible even for an LSST--like survey, once galaxy shape noise is considered, and we conclude that the Born approximation is sufficient for future galaxy WL analyses.
 Using the \ttt{LensTools} software suite, we show that the Born approximation saves a factor of 4 in computing time with respect to the full ray--tracing in reconstructing the convergence.
@@
 The right panel shows the residuals between the power spectrum of the full ray--traced $\kappa$ field and the one obtained with the Born approximation.
-The residuals are compared to the two $O(\Phi^3)$ terms $2P_{\rm born,ll},2P_{\rm born,geo}$.
+\textbf{\color{red} For reference, we show the shape noise contributions (black dashed) and the first non--trivial reduced shear corrections to $P^{\kappa\kappa}$(purple), which can be both added to the forward models after the line of sight integration.} The residuals are compared to the two $O(\Phi^3)$ terms $2P_{\rm born,ll},2P_{\rm born,geo}$.
 The quantities shown are the ensemble averages over 8192 realizations of $\kappa$ in the fiducial cosmology $\bb{p}_0$.}
@@
 We show both the cases in which the residuals $\delta\kappa^3,\delta\kappa^4$ are computed adding equations (\ref{sim:ll},\ref{sim:gp}) to the Born field (solid lines) and in which the residuals are computed from the dominant $\Phi$ orders only as in equations (\ref{res:skewcross},\ref{res:kurtcross}) (dashed lines).
-The quantities shown are the ensemble averages over 8192 realizations of $\kappa$ in the fiducial cosmology $\bb{p}_0$.}
+\textbf{\color{red} For reference we show the first non--trivial corrections due to reduced shear (black lines).} The quantities shown are the ensemble averages over 8192 realizations of $\kappa$ in the fiducial cosmology $\bb{p}_0$.}
 \label{fig:skResiduals}
@@
 \ref{fig:psResiduals} and \ref{fig:skResiduals} indicate \textbf{\color{red} that truncating $\kappa$ at $O(\Phi^2)$ post--Born terms, leads to inaccurate predictions of the power spectrum and moments.
-In particular, higher-order terms involving $\langle \kappa_{\rm born}^n \kappa_{\rm ll}^m \kappa_{\rm geo}^2\rangle$ and higher, cause large deviations (as seen by the difference between the solid and dashed green curves) that, in an exact approach, are canceled by $O(\Phi^3)$ corrections to $\kappa$, as pointed out by \citep{HirataKrause}}.
+In particular, higher-order terms involving $\langle \kappa_{\rm born}^n \kappa_{\rm ll}^m \kappa_{\rm geo}^2\rangle$ and higher, cause large deviations (as seen by the difference between the solid and dashed green curves) that, in an exact approach, are canceled by $O(\Phi^3)$ corrections to $\kappa$, as pointed out by \citep{HirataKrause,CMBPrattenLewis,ScoccimarroLoop}}.
 Therefore, in practice, in order to go beyond Born approximation, it is more advantageous, both for accuracy and for CPU time, to perform full ray--tracing (whose computational cost is comparable to those of the $O(\Phi^2)$ line--of--sight integrals; Table \ref{tab:benchmarks}).
+
+\textbf{\color{red} In real observations, the convergence $\kappa$ is recostructed via the Kaiser--Squires inversion procedure \citep{KaiserSquires}, applied on the reduced shear $\pmb{\gamma}/(1-\kappa)$.
+In order to avoid possible biases in parameter inferences, one needs to take this into account.
+This can be done within the Born approximation, as the quantity $\kappa\pmb{\gamma}$ is the dominant $O(\Phi^2)$ reduced shear correction, which can be calculated from the Born $\kappa$ images and is independent from the line of sight intergration procedure.
+The $O(\Phi^2)$ reduced shear correction to $\kappa$ is easily incorporated in the forward models.}
 

### 2017-01-25 Paper/Figures/generate.py

@@ -109,7 +109,7 @@ def powerResiduals(cmd_args,collection="c0",fontsize=22):
 	ax[1].plot(ell,ell*(ell+1)*(np.abs(pFull.mean(0)-pBorn.mean(0)))/(2.0*np.pi),label=r"${\rm ray-born}$")
 	ax[1].plot(ell,ell*(ell+1)*np.abs(pGP_cross.mean(0))/np.pi,label=r"$2{\rm born}\times{\rm geo}$")
 	ax[1].plot(ell,ell*(ell+1)*np.abs(pLL_cross.mean(0))/np.pi,label=r"$2{\rm born}\times{\rm ll}$")
-	ax[1].plot(ell,ell*(ell+1)*np.abs(p_redshear_cross.mean(0))/np.pi,label=r"$2(\kappa\gamma)_{\rm born}$")
+	ax[1].plot(ell,ell*(ell+1)*np.abs(p_redshear_cross.mean(0))/np.pi,label=r"$2\kappa_{\rm born}\times(\kappa\gamma)_{\rm born}$")
 
 	#Shape noise
 	pshape = ((0.15+0.035*2.0)**2)/((45*(u.arcmin**-2)).to(u.rad**-2).value)

### 2017-01-25 batchcode/scripts/measure_from_maps.py
fix smoothing of reduced shear

@@ -85,14 +85,16 @@ def redshear_skew(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal
 			gen = GaussianNoiseGenerator.forMap(conv)
 			conv = conv + gen.getShapeNoise(z=z,ngal=ngal*(u.arcmin**-2),seed=hash(os.path.basename(fname))%4294967295)
 
-		if smoothing>0.:
-			conv = conv.smooth(smoothing*u.arcmin,kind="gaussianFFT")
-
 		#Construct shear map, compute kappa*gamma correction, back to convergence
 		shear = ShearMap.fromConvergence(conv)
 		for n in (0,1):
 			shear.data[n]*=conv.data
 		conv2 = shear.convergence()
+
+		#Smooth
+		if smoothing>0.:
+			conv = conv.smooth(smoothing*u.arcmin,kind="gaussianFFT")
+			conv2 = conv2.smooth(smoothing*u.arcmin,kind="gaussianFFT")
 
 		#Measure skewness correction
 		return np.array([(3*(conv.data**2)*(conv2.data)).mean()])
@@ -110,14 +112,16 @@ def redshear_kurt(fname,map_set,l_edges,kappa_edges,z,add_shape_noise=False,ngal
 			gen = GaussianNoiseGenerator.forMap(conv)
 			conv = conv + gen.getShapeNoise(z=z,ngal=ngal*(u.arcmin**-2),seed=hash(os.path.basename(fname))%4294967295)
 
-		if smoothing>0.:
-			conv = conv.smooth(smoothing*u.arcmin,kind="gaussianFFT")
-
 		#Construct shear map, compute kappa*gamma correction, back to convergence
 		shear = ShearMap.fromConvergence(conv)
 		for n in (0,1):
 			shear.data[n]*=conv.data
 		conv2 = shear.convergence()
+
+		#Smooth
+		if smoothing>0.:
+			conv = conv.smooth(smoothing*u.arcmin,kind="gaussianFFT")
+			conv2 = conv2.smooth(smoothing*u.arcmin,kind="gaussianFFT")
 
 		#Measure kurtosis correction
 		kurt = 4*((conv.data**3)*conv2.data).mean() - 12*((conv.data**2).mean())*(conv.data*conv2.data).mean()

### 2017-01-25 Paper/paper.tex
finished modifications for resubmission (2)

@@
 \textbf{\color{red} In this work, we use simulations to show that deviations of the Born--approximated convergence power spectrum, skewness and kurtosis from their fully ray--traced counterparts are consistent with the smallest non--trivial $O(\Phi^3)$ post--Born corrections (so-called geodesic and lens-lens terms).
-In this work, we use simulations to show that deviations of the Born--approximated convergence power spectrum, skewness and kurtosis from their fully ray--traced counterparts are consistent with the smallest non--trivial post--Born corrections.
 Our results imply a cancelation among the larger $O(\Phi^4)$ (and higher order) terms, consistent with previous analytic work.} We also find that cosmological parameter biases induced by the Born approximation are negligible even for an LSST--like survey, once galaxy shape noise is considered, and we conclude that the Born approximation is sufficient for future galaxy WL analyses.
@@
 We show both the cases in which the residuals $\delta\kappa^3,\delta\kappa^4$ are computed adding equations (\ref{sim:ll},\ref{sim:gp}) to the Born field (solid lines) and in which the residuals are computed from the dominant $\Phi$ orders only as in equations (\ref{res:skewcross},\ref{res:kurtcross}) (dashed lines).
-\textbf{\color{red} For reference we show the first non--trivial corrections due to reduced shear (black lines).} The quantities shown are the ensemble averages over 8192 realizations of $\kappa$ in the fiducial cosmology $\bb{p}_0$.}
+\textbf{\color{red} For reference we show the first non--trivial corrections due to reduced shear (black lines), which can be calculated from the Born images.} The quantities shown are the ensemble averages over 8192 realizations of $\kappa$ in the fiducial cosmology $\bb{p}_0$.}
 \label{fig:skResiduals}
@@
 This can be seen by looking at the lens-lens term, which is over an order of magnitude smaller than the geodesic term, and by looking at the full $\kappa-\kappa_{\rm born}$ residuals, which show a very similar overall level, as well as structural detail, to the ones found in the $\kappa_{\rm geo}$ map.
-\textbf{\color{red} When considering a real observation, in which $\kappa$ is estimated from source ellipticities, one should consider an additional reduced shear correction to $\kappa$, which is of order $O(\Phi^2)$ \citep{HirataKrause} and is proportional to $\gamma\kappa$.
-We estimated this correction to be one order of magnitude smaller than the dominant geodesic term}.
 The reader might have noticed the curious alignment feature in Figure \ref{fig:csample}, in which all the dipolar structures in $\kappa_{\rm geo}$ appear to be horizontally aligned throughout the field of view.
@@
 Figure \ref{fig:skResiduals} shows that the geodesic and lens--lens contributions to the $\kappa$ skewness and kurtosis are comparable and that the lowest non--trivial post--Born corrections can fully account for the discrepancy between the Born--approximated quantities and the fully ray--traced ones.
-Figs.
+\textbf{\color{red} The geodesic and lens--lens corrections to the skewness we find agree, as orders of magnitude, with the ones already published in \citep{WLBispectrumDodelson}, although our measured reduced shear correction is larger.
+We stress, however, that our estimates and the ones in \citep{WLBispectrumDodelson} have been produced under different assumptions, in particular \citep{WLBispectrumDodelson} use a fully analytical approach based on the Limber approximation, different form forms for the smoothing windows and use their own assumptions for the form of the $\kappa$ bispectrum.} Figs.
 \ref{fig:psResiduals} and \ref{fig:skResiduals} indicate \textbf{\color{red} that truncating $\kappa$ at $O(\Phi^2)$ post--Born terms, leads to inaccurate predictions of the power spectrum and moments.

### 2017-02-14 Paper/paper.tex
corrected conclusions on moments

@@
 \textbf{\color{red} In this work, we use simulations to show that deviations of the Born--approximated convergence power spectrum, skewness and kurtosis from their fully ray--traced counterparts are consistent with the smallest non--trivial $O(\Phi^3)$ post--Born corrections (so-called geodesic and lens-lens terms).
-Our results imply a cancelation among the larger $O(\Phi^4)$ (and higher order) terms, consistent with previous analytic work.} We also find that cosmological parameter biases induced by the Born approximation are negligible even for an LSST--like survey, once galaxy shape noise is considered, and we conclude that the Born approximation is sufficient for future galaxy WL analyses.
-Using the \ttt{LensTools} software suite, we show that the Born approximation saves a factor of 4 in computing time with respect to the full ray--tracing in reconstructing the convergence.
+Our results imply a cancelation among the larger $O(\Phi^4)$ (and higher order) terms, consistent with previous analytic work.} \textbf{\color{blue} We also find that cosmological parameter biases induced by the Born approximation on the power spectrum are negligible even for an LSST--like survey, once galaxy shape noise is considered.
+The same conclusion is not true when considering higher order statistics, such as the $\kappa$ skewness and kurtosis.} Using the \ttt{LensTools} software suite, we show that the Born approximation saves a factor of 4 in computing time with respect to the full ray--tracing in reconstructing the convergence.
 \end{abstract}
@@
 Numerical efforts for feature forward modeling are based on ray--tracing simulations \textbf{\color{red} that make use of the multi--lens--plane algorithm \citep{RayTracingJain,RayTracingHartlap,RayTracingPN}, or the direct approach \citep{RayTracingBarreira},} to predict cosmic shear from outputs of $N$--body simulations.
-Approximate techniques based on the Born approximation allow for a computationally faster, but potentially inaccurate, forward modeling \citep{RayTracingHartlap} which requires only knowledge of the matter density contrast integrated along the observer unperturbed line of sight.
+Approximate techniques based on the Born approximation allow for a computationally faster, but potentially inaccurate, forward modeling which requires only knowledge of the matter density contrast integrated along the observer unperturbed line of sight.
+\textbf{\color{blue} This has been done both in the flat sky \citep{RayTracingHartlap} and full sky \citep{Fosalba1,Fosalba2} limits}.
 A variety of groups have studied the validity of the Born approximation for forward modeling of convergence power spectra \citep{HirataKrause} and bi--spectra \citep{WLBispectrumDodelson}, spectra of WL cosmic flexions \citep{BornFlexion} and, in more recent work, CMB lensing bi--spectra \citep{CMBPrattenLewis}.
@@
 \begin{center}
-\includegraphics[scale=0.3]{Figures/bias_convergence_power_s0_nb100.eps}
-\includegraphics[scale=0.3]{Figures/bias_convergence_moments_s0_nb9.eps}
-\includegraphics[scale=0.3]{Figures/bias_convergence_momentsSN_s0_nb9.eps}
+\includegraphics[scale=0.3]{Figures/bias_convergence_powerSN30_s0_nb100.eps}
+\includegraphics[scale=0.3]{Figures/bias_convergence_momentsSN15_s50_nb9.eps}
+\includegraphics[scale=0.3]{Figures/bias_convergence_momentsSN30_s50_nb9.eps}
 \end{center}
 \caption{Distributions of the parameter estimator (eq.~\ref{par:fisherest}) over 1000 realizations of an LSST--like survey.
-We show parameter estimates obtained using the noiseless $\kappa$ power spectrum (top panels), the noiseless $\kappa$ moments defined in eq.~(\ref{par:moments}) (middle panels) and the noisy $\kappa$ moments, based on a galaxy density of $15\,{\rm arcmin}^{-2}$ (bottom panels).
-We do not show results from the noisy power spectrum, because the noiseless power spectrum is already unbiased.
+We show parameter estimates obtained using the $\kappa$ power spectrum (top panels) \textbf{\color{blue} with shape noise added ($n_g=30\,{\rm galaxies/arcmin}^2$)} and the $\kappa$ moments defined in eq.~(\ref{par:moments}) \textbf{\color{blue} with shape noise added with both a galaxy density of 15 (middle panels) and 30 (bottom panels) galaxies/arcmin$^2$}.
 In each panel, we show both a control case, in which the mock observation has been constructed with the Born approximation (blue), and the ``real'' case, in which the observation has been constructed with full ray--tracing (green).
-The $\kappa$ power spectrum from which the constraints in the upper panel have been derived, has been measured in 100 uniformly spaced bands with $\ell \in [150,10000]$}
+The $\kappa$ power spectrum from which the constraints in the upper panel have been derived, has been measured in 100 uniformly spaced bands with $\ell \in [150,10000]$.
+\textbf{\color{blue} A Gaussian smoothing window of size $\theta_G=0.5\,{\rm arcmin}$ has been applied to the $\kappa$ maps prior to measuring the moments.}}
 \label{fig:parbias}
@@
 \begin{center}
-\includegraphics[scale=0.45]{Figures/bias_ngal_convergence_momentsSN_s50_nb9.eps}
+\includegraphics[scale=0.45]{Figures/bias_ngal_convergence_powerSN_s0_nb100.eps}
 \end{center}
-\caption{Parameter bias dependence on the galaxy density angular $n_g$ used to compute the shape noise rms in eq.
+\caption{Parameter bias \textbf{\color{blue}, obtained from the $\kappa$ power spectrum, as a function of} the galaxy density angular $n_g$ used to compute the shape noise rms in eq.
 (\ref{par:shaperms}).
@@
 We also studied how our conclusions are influenced by the survey angular galaxy density $n_g$, which controls the amplitude of the shape noise in the $\kappa$ reconstruction.
-The dependence of moments--based parameter biases on $n_g$ is shown in Figure \ref{fig:parbiasSN}.
+The dependence of \textbf{\color{blue} power spectrum based} parameter biases on $n_g$ is shown in Figure \ref{fig:parbiasSN}.
 
@@
 This can lead to parameter biases when fitting observations.
-Figure \ref{fig:parbias} studies this possibility and shows that, while the Born approximation is sufficient to fit cosmology with the power spectrum of an LSST--like survey, even in the noiseless case, the same is not true for the higher $\kappa$ moments.
+Figure \ref{fig:parbias} studies this possibility and shows that the Born approximation is sufficient to fit cosmology with the power spectrum of an LSST--like survey, \textbf{\color{blue} with the result holding also for galaxy densities as high as $60\,{\rm galaxies/arcmin}^2$, as can be seen in Figure \ref{fig:parbiasSN}.
+While the Born approximation is sufficient to obtain unbiased cosmological constraints from the $\kappa$ power spectrum, the same is not true for the higher order $\kappa$ moments}.
 We have previously shown that these moments contain significantly more information than the power spectrum \citep{MinkPetri}; an expectation that was confirmed when fitting the CFHTLenS data~\citep{CFHTMink}.
-The middle row of panels in Figure \ref{fig:parbias} shows that indeed the constraints from the moments are $\approx$ 3 times tighter than from the power spectrum (seen by the narrow widths of the PDFs).
+The middle \textbf{\color{blue} and bottom} row of panels in Figure \ref{fig:parbias} show that indeed the constraints from the moments are $\approx$ 2 times tighter than from the power spectrum (seen by the narrow widths of the PDFs).
 As a result, highly significant biases are observed when fitting a real observation with Born--approximated $\kappa$ moments.
-The bias however disappears when introducing galaxy shape noise, due to the resulting increased statistical error, as can be seen in Figure \ref{fig:parbiasSN}.
-The Figure shows that even for galaxy angular densities as high as $\approx 60\,{\rm arcmin}^{-2}$, that will be achievable in future surveys such as WFIRST \citep{WFIRST}, Born--induced parameter biases are within the one sigma margin.
-This result leads us to the conclusion that the Born approximation is sufficient for future WL analyses.
+\textbf{\color{blue} Although the presence of Gaussian galaxy shape noise reduces the significance of this bias, it cannot completely eliminate it, as higher order moments are sensitive to non--Gaussian statistical information.
+These results lead us to the conclusion that the Born approximation is sufficient for future WL analyses that make use of the $\kappa$ power spectrum.
 This approach also has the advantage of being 4 times computationally faster than full ray--tracing, as we show in Table \ref{tab:benchmarks} for a selected reference test case.
+When considering higher order moments of $\kappa$, however, full ray--tracing is required to obtain unbiased constraints on cosmology.}
 
@@
 \item Using the \ttt{LensTools} software package, Born integration costs 4 times less than ray--tracing, and consumes about half as much memory.
-\item The Born approximation for the $\kappa$ power spectrum leads to negligible parameter bias for an LSST--like survey, even in the noiseless case.
-\item Fitting an observation with Born--approximated higher $\kappa$ moments leads to significant bias in the $(\Omega_m,w_0,\sigma_8)$ triplet in the noiseless case.
-However, this bias becomes negligible when galaxy shape noise is added, due to an increased scatter in parameter estimates.
-This conclusion holds even for future space--based surveys that can probe galaxy angular densities as high as $60\,{\rm arcmin}^{-2}$.
+\item The Born approximation for the $\kappa$ power spectrum leads to negligible parameter bias for an LSST--like survey\textbf{\color{blue}, and holds for survey galaxy densities as high as $60\,{\rm galaxies/arcmin^2}$.}
+\item Fitting an observation with Born--approximated higher $\kappa$ moments leads to significant bias in the $(\Omega_m,w_0,\sigma_8)$ triplet\textbf{\color{blue}, even in the presence of galaxy shape noise.}
 \end{itemize}

### 2017-02-14 Paper/Figures/generate.py

@@ -259,7 +259,7 @@ def pdfMoments(cmd_args,collection="c0",kappa_models=("kappa","kappaBorn"),figna
 ###################################################################################################
 ###################################################################################################
 
-def pbBias(cmd_args,feature_name="convergence_power_s0_nb100",title="Power spectrum",kappa_models=("Born",),callback=None,variation_idx=(0,),bootstrap_size=100,resample=1000,return_results=False,fontsize=22):
+def pbBias(cmd_args,feature_name="convergence_power_s0_nb100",title="Power spectrum",kappa_models=("Born",),callback=None,variation_idx=(0,),bootstrap_size=1000,resample=1000,return_results=False,fontsize=22):
 	
 	#Initialize plot
 	fig,ax = plt.subplots(len(variation_idx),3,figsize=(24,8*len(variation_idx)))
@@ -271,7 +271,7 @@ def pbBias(cmd_args,feature_name="convergence_power_s0_nb100",title="Power spect
 
 	#Observation
 	bootstrap_mean = lambda e: e.values.mean(0)
-	feature_ray = Ensemble.read(os.path.join(fiducial["c0"].getMapSet("kappa").home,feature_name+".npy"),callback_loader=callback).bootstrap(bootstrap_mean,bootstrap_size=bootstrap_size,resample=resample)
+	feature_ray = Ensemble.read(os.path.join(fiducial["c0"].getMapSet("kappa").home,feature_name+".npy"),callback_loader=callback).bootstrap(bootstrap_mean,bootstrap_size=bootstrap_size,resample=resample,seed=0)
 
 	#Containers for cosmological model
 	modelFeatures = dict()
@@ -305,7 +305,7 @@ def pbBias(cmd_args,feature_name="convergence_power_s0_nb100",title="Power spect
 		#Load in the feature to fit, bootstrap the mean#
 		################################################
 	
-		feature_born = features[fiducial.cosmo_id].bootstrap(bootstrap_mean,bootstrap_size=bootstrap_size,resample=resample)
[…]

### 2017-02-28 Paper/paper.tex
second round of edits with fixed conclusions

@@
 \textbf{\color{red} In this work, we use simulations to show that deviations of the Born--approximated convergence power spectrum, skewness and kurtosis from their fully ray--traced counterparts are consistent with the smallest non--trivial $O(\Phi^3)$ post--Born corrections (so-called geodesic and lens-lens terms).
-Our results imply a cancelation among the larger $O(\Phi^4)$ (and higher order) terms, consistent with previous analytic work.} \textbf{\color{blue} We also find that cosmological parameter biases induced by the Born approximation on the power spectrum are negligible even for an LSST--like survey, once galaxy shape noise is considered.
+Our results imply a cancellation among the larger $O(\Phi^4)$ (and higher order) terms, consistent with previous analytic work.} \textbf{\color{blue} We also find that cosmological parameter bias induced by the Born approximated power spectrum is negligible even for an LSST--like survey, once galaxy shape noise is considered.
 The same conclusion is not true when considering higher order statistics, such as the $\kappa$ skewness and kurtosis.} Using the \ttt{LensTools} software suite, we show that the Born approximation saves a factor of 4 in computing time with respect to the full ray--tracing in reconstructing the convergence.
@@
 % 
-In this section, we present the main results of this work, regarding accuracy of forward modeling the WL features, and the cosmological parameter biases induced by the Born approximation.
+In this section, we present the main results of this work, regarding accuracy of forward modeling the WL features, and the cosmological parameter bias induced by the Born approximation.
 
@@
 The right panel shows the residuals between the power spectrum of the full ray--traced $\kappa$ field and the one obtained with the Born approximation.
-\textbf{\color{red} For reference, we show the shape noise contributions (black dashed) and the first non--trivial reduced shear corrections to $P^{\kappa\kappa}$(purple), which can be both added to the forward models after the line of sight integration.} The residuals are compared to the two $O(\Phi^3)$ terms $2P_{\rm born,ll},2P_{\rm born,geo}$.
+\textbf{\color{red} For reference, we show the shape noise contributions (black dashed) and the first non--trivial reduced shear corrections to $P^{\kappa\kappa}$(purple), which can be both added to the forward models after the line of sight integration.} \textbf{\color{blue} Gaussian convolution effects with a window of size $\theta_G=0.5\,{\rm arcmin}$ are included.} The residuals are compared to the two $O(\Phi^3)$ terms $2P_{\rm born,ll},2P_{\rm born,geo}$.
 The quantities shown are the ensemble averages over 8192 realizations of $\kappa$ in the fiducial cosmology $\bb{p}_0$.}
@@
 \subsection{Parameter bias}
-When using forward models based on the Born approximation to fit observations, parameter biases may occur if the forward model is not accurate enough.
+When using forward models based on the Born approximation to fit observations, parameter bias may occur if the forward model is not accurate enough.
 We studied if this is the case by simulating 1000 LSST--like observations in which the convergence field $\kappa(\pt)$ is constructed using the full ray--tracing procedure.
@@
 We also studied how our conclusions are influenced by the survey angular galaxy density $n_g$, which controls the amplitude of the shape noise in the $\kappa$ reconstruction.
-The dependence of \textbf{\color{blue} power spectrum based} parameter biases on $n_g$ is shown in Figure \ref{fig:parbiasSN}.
+\textbf{\color{blue} The scaling of the power spectrum--induced} parameter bias with $n_g$ is shown in Figure \ref{fig:parbiasSN}.
 
@@
 The reader might have noticed the curious alignment feature in Figure \ref{fig:csample}, in which all the dipolar structures in $\kappa_{\rm geo}$ appear to be horizontally aligned throughout the field of view.
-We believe that this alignment is not a numerical effect, but is originated physically by the $\nabla\delta$ terms in eq.~(\ref{sim:gp}).
+We believe that this alignment is not a numerical effect, but originates physically by the $\nabla\delta$ terms in eq.~(\ref{sim:gp}).
 Early in the line--of--sight integration, the field of view covers a very small section of the simulation box ($\sim7\,{\rm Mpc}$ for the first lens), within which dipolar structures are aligned.
@@
 \textbf{\color{red} The geodesic and lens--lens corrections to the skewness we find agree, as orders of magnitude, with the ones already published in \citep{WLBispectrumDodelson}, although our measured reduced shear correction is larger.
-We stress, however, that our estimates and the ones in \citep{WLBispectrumDodelson} have been produced under different assumptions, in particular \citep{WLBispectrumDodelson} use a fully analytical approach based on the Limber approximation, different form forms for the smoothing windows and use their own assumptions for the form of the $\kappa$ bispectrum.} Figs.
+We stress, however, that our estimates and the ones in \citep{WLBispectrumDodelson} have been produced under different assumptions, in particular \citep{WLBispectrumDodelson} use a fully analytical approach based on the Limber approximation, different form forms for the smoothing windows and use their own assumptions for the form of the $\kappa$ bi--spectrum.} Figs.
 \ref{fig:psResiduals} and \ref{fig:skResiduals} indicate \textbf{\color{red} that truncating $\kappa$ at $O(\Phi^2)$ post--Born terms, leads to inaccurate predictions of the power spectrum and moments.
@@
 
-\textbf{\color{red} In real observations, the convergence $\kappa$ is recostructed via the Kaiser--Squires inversion procedure \citep{KaiserSquires}, applied on the reduced shear $\pmb{\gamma}/(1-\kappa)$.
+\textbf{\color{red} In real observations, the convergence $\kappa$ is reconstructed via the Kaiser--Squires inversion procedure \citep{KaiserSquires}, applied on the reduced shear $\pmb{\gamma}/(1-\kappa)$.
 In order to avoid possible biases in parameter inferences, one needs to take this into account.
-This can be done within the Born approximation, as the quantity $\kappa\pmb{\gamma}$ is the dominant $O(\Phi^2)$ reduced shear correction, which can be calculated from the Born $\kappa$ images and is independent from the line of sight intergration procedure.
+This can be done within the Born approximation, as the quantity $\kappa\pmb{\gamma}$ is the dominant $O(\Phi^2)$ reduced shear correction, which can be calculated from the Born $\kappa$ images and is independent from the line of sight integration procedure.
 The $O(\Phi^2)$ reduced shear correction to $\kappa$ is easily incorporated in the forward models.}
@@
 This figure clearly shows that, while the Born approximation is a good predictor of the quadratic moments $\pmb{\mu}_2$ within one standard deviation, the higher moments $\pmb{\mu}_3,\pmb{\mu}_4$ show 2 to 3$\sigma$ deviations from their Born--approximated counterparts.
-This can lead to parameter biases when fitting observations.
+This can lead to parameter bias when fitting observations.
 Figure \ref{fig:parbias} studies this possibility and shows that the Born approximation is sufficient to fit cosmology with the power spectrum of an LSST--like survey, \textbf{\color{blue} with the result holding also for galaxy densities as high as $60\,{\rm galaxies/arcmin}^2$, as can be seen in Figure \ref{fig:parbiasSN}.
-While the Born approximation is sufficient to obtain unbiased cosmological constraints from the $\kappa$ power spectrum, the same is not true for the higher order $\kappa$ moments}.
-We have previously shown that these moments contain significantly more information than the power spectrum \citep{MinkPetri}; an expectation that was confirmed when fitting the CFHTLenS data~\citep{CFHTMink}.
+The accuracy requirements, however, might be stricter for deeper surveys, such as Euclid \citep{Euclid}, which requires systematic effects not to be greater than $\sigma/3$.
+While the Born approximation is accurate in predicting the $\kappa$ power spectrum, the same is not true for higher order $\kappa$ moments}.
+We have previously shown that these moments contain significantly more information than the power spectrum \citep{MinkPetri}, an expectation that was confirmed when fitting CFHTLenS data~\citep{CFHTMink}.
 The middle \textbf{\color{blue} and bottom} row of panels in Figure \ref{fig:parbias} show that indeed the constraints from the moments are $\approx$ 2 times tighter than from the power spectrum (seen by the narrow widths of the PDFs).
-As a result, highly significant biases are observed when fitting a real observation with Born--approximated $\kappa$ moments.
-\textbf{\color{blue} Although the presence of Gaussian galaxy shape noise reduces the significance of this bias, it cannot completely eliminate it, as higher order moments are sensitive to non--Gaussian statistical information.
-These results lead us to the conclusion that the Born approximation is sufficient for future WL analyses that make use of the $\kappa$ power spectrum.
+As a result, highly significant biases are observed when fitting an observation with Born--approximated $\kappa$ moments.
+\textbf{\color{blue} Although the presence of Gaussian galaxy shape noise reduces the significance of this bias, it cannot completely eliminate it, as higher order moments are sensitive to non--Gaussian statistical information in $\kappa$ images.
+These results lead us to the conclusion that the Born approximation is sufficient for future WL analyses that use the $\kappa$ power spectrum to constrain cosmology.
 This approach also has the advantage of being 4 times computationally faster than full ray--tracing, as we show in Table \ref{tab:benchmarks} for a selected reference test case.
-When considering higher order moments of $\kappa$, however, full ray--tracing is required to obtain unbiased constraints on cosmology.}
+When considering higher order moments of $\kappa$, however, full ray--tracing is required in order to obtain unbiased constraints.}
 
@@
 In this work we examined the validity of the Born approximation for WL galaxy surveys, but a similar study could in principle be carried for the lensing potential reconstruction from CMB temperature and polarization data \citep{CMBCalabrese}.
-Lensing of the CMB probes structures over a wider range of redshifts and hence CMB lensing observables can be expected to be more Gaussian distributed than their galaxy lensing counterparts.
-This suggests the possibility that non--Gaussian features in CMB lensing data could come from post--Born corrections of $O(\Phi^2)$ rather than inherent non--Gaussianity in the Born $O(\Phi)$ terms.
+Lensing of the CMB probes structures over a wider range of redshifts and hence CMB lensing observables can be expected to \textbf{\color{blue} closer to} Gaussian than their galaxy lensing counterparts.
+This suggests the possibility that non--Gaussian features in CMB lensing data could come from post--Born corrections of $O(\Phi^2)$ rather than \textbf{\color{blue} from intrinsic} non--Gaussianity in the Born $O(\Phi)$ terms.
 This possibility has been suggested by \citep{CMBPrattenLewis}, who looked at the CMB lensing $\kappa$ bi--spectrum.
-Because of the high significance with which non--Gaussianities in the CMB lensing potential can be detected with future Stage IV experiments \citep{CMBLNG}, we propose to investigate post--Born corrections to CMB lensing observables in future work.
+Because of the high significance with which non--Gaussianity in the CMB lensing potential can be detected with future Stage IV experiments \citep{CMBLNG}, we propose to investigate post--Born corrections to CMB lensing observables in future work.
 

### 2017-02-28 Paper/Figures/generate.py

@@ -94,6 +94,10 @@ def powerResiduals(cmd_args,collection="c0",fontsize=22):
 
 	#Load data
 	ell = np.load(os.path.join(batch.home,"ell_nb100.npy"))
+	thetaG = 0.5*u.arcmin
+	smooth = np.exp(-(ell*(thetaG.to(u.rad).value))**2)
+
+	#Plot
 	pFull = np.load(os.path.join(fiducial[collection].getMapSet("kappa").home,"convergence_power_s0_nb100.npy"))
 	pBorn = np.load(os.path.join(fiducial[collection].getMapSet("kappaBorn").home,"convergence_power_s0_nb100.npy"))
 	pLL = np.load(os.path.join(fiducial[collection].getMapSet("kappaLL").home,"convergence_power_s0_nb100.npy"))
@@ -103,25 +107,26 @@ def powerResiduals(cmd_args,collection="c0",fontsize=22):
 	p_redshear_cross = np.load(os.path.join(fiducial[collection].getMapSet("kappaBorn").home,"redshear_power_s0_nb100.npy"))
 
 	#Plot
-	ax[0].plot(ell,ell*(ell+1)*pBorn.mean(0)/(2.*np.pi),label=r"${\rm born}$")
-	ax[0].plot(ell,ell*(ell+1)*pGP.mean(0)/(2.*np.pi),label=r"${\rm geodesic}$")
-	ax[0].plot(ell,ell*(ell+1)*pLL.mean(0)/(2.*np.pi),label=r"${\rm lens-lens}$")
-	ax[1].plot(ell,ell*(ell+1)*(np.abs(pFull.mean(0)-pBorn.mean(0)))/(2.0*np.pi),label=r"${\rm ray-born}$")
-	ax[1].plot(ell,ell*(ell+1)*np.abs(pGP_cross.mean(0))/np.pi,label=r"$2{\rm born}\times{\rm geo}$")
-	ax[1].plot(ell,ell*(ell+1)*np.abs(pLL_cross.mean(0))/np.pi,label=r"$2{\rm born}\times{\rm ll}$")
-	ax[1].plot(ell,ell*(ell+1)*np.abs(p_redshear_cross.mean(0))/np.pi,label=r"$2\kappa_{\rm born}\times(\kappa\gamma)_{\rm born}$")
[…]

### 2017-03-23 Paper/paper.tex
remove colored fonts

@@
 A less accurate procedure, based on the Born approximation, only requires knowledge of the density field, and can be implemented more efficiently and at a lower computational cost.
-\textbf{\color{red} In this work, we use simulations to show that deviations of the Born--approximated convergence power spectrum, skewness and kurtosis from their fully ray--traced counterparts are consistent with the smallest non--trivial $O(\Phi^3)$ post--Born corrections (so-called geodesic and lens-lens terms).
-Our results imply a cancellation among the larger $O(\Phi^4)$ (and higher order) terms, consistent with previous analytic work.} \textbf{\color{blue} We also find that cosmological parameter bias induced by the Born approximated power spectrum is negligible even for an LSST--like survey, once galaxy shape noise is considered.
-The same conclusion is not true when considering higher order statistics, such as the $\kappa$ skewness and kurtosis.} Using the \ttt{LensTools} software suite, we show that the Born approximation saves a factor of 4 in computing time with respect to the full ray--tracing in reconstructing the convergence.
+In this work, we use simulations to show that deviations of the Born--approximated convergence power spectrum, skewness and kurtosis from their fully ray--traced counterparts are consistent with the smallest non--trivial $O(\Phi^3)$ post--Born corrections (so-called geodesic and lens-lens terms).
+Our results imply a cancellation among the larger $O(\Phi^4)$ (and higher order) terms, consistent with previous analytic work.
+We also find that cosmological parameter bias induced by the Born approximated power spectrum is negligible even for an LSST--like survey, once galaxy shape noise is considered.
+The same conclusion is not true when considering higher order statistics, such as the $\kappa$ skewness and kurtosis.
+Using the \ttt{LensTools} software suite, we show that the Born approximation saves a factor of 4 in computing time with respect to the full ray--tracing in reconstructing the convergence.
 \end{abstract}
@@
 This however is a challenging problem due to the non--linear nature of WL image fields.
-Numerical efforts for feature forward modeling are based on ray--tracing simulations \textbf{\color{red} that make use of the multi--lens--plane algorithm \citep{RayTracingJain,RayTracingHartlap,RayTracingPN}, or the direct approach \citep{RayTracingBarreira},} to predict cosmic shear from outputs of $N$--body simulations.
+Numerical efforts for feature forward modeling are based on ray--tracing simulations that make use of the multi--lens--plane algorithm \citep{RayTracingJain,RayTracingHartlap,RayTracingPN}, or the direct approach \citep{RayTracingBarreira}, to predict cosmic shear from outputs of $N$--body simulations.
 Approximate techniques based on the Born approximation allow for a computationally faster, but potentially inaccurate, forward modeling which requires only knowledge of the matter density contrast integrated along the observer unperturbed line of sight.
-\textbf{\color{blue} This has been done both in the flat sky \citep{RayTracingHartlap} and full sky \citep{Fosalba1,Fosalba2} limits}.
+This has been done both in the flat sky \citep{RayTracingHartlap} and full sky \citep{Fosalba1,Fosalba2} limits.
 A variety of groups have studied the validity of the Born approximation for forward modeling of convergence power spectra \citep{HirataKrause} and bi--spectra \citep{WLBispectrumDodelson}, spectra of WL cosmic flexions \citep{BornFlexion} and, in more recent work, CMB lensing bi--spectra \citep{CMBPrattenLewis}.
@@
 The right panel shows the residuals between the power spectrum of the full ray--traced $\kappa$ field and the one obtained with the Born approximation.
-\textbf{\color{red} For reference, we show the shape noise contributions (black dashed) and the first non--trivial reduced shear corrections to $P^{\kappa\kappa}$(purple), which can be both added to the forward models after the line of sight integration.} \textbf{\color{blue} Gaussian convolution effects with a window of size $\theta_G=0.5\,{\rm arcmin}$ are included.} The residuals are compared to the two $O(\Phi^3)$ terms $2P_{\rm born,ll},2P_{\rm born,geo}$.
+For reference, we show the shape noise contributions (black dashed) and the first non--trivial reduced shear corrections to $P^{\kappa\kappa}$(purple), which can be both added to the forward models after the line of sight integration.
+Gaussian convolution effects with a window of size $\theta_G=0.5\,{\rm arcmin}$ are included.
+The residuals are compared to the two $O(\Phi^3)$ terms $2P_{\rm born,ll},2P_{\rm born,geo}$.
 The quantities shown are the ensemble averages over 8192 realizations of $\kappa$ in the fiducial cosmology $\bb{p}_0$.}
@@
 We show both the cases in which the residuals $\delta\kappa^3,\delta\kappa^4$ are computed adding equations (\ref{sim:ll},\ref{sim:gp}) to the Born field (solid lines) and in which the residuals are computed from the dominant $\Phi$ orders only as in equations (\ref{res:skewcross},\ref{res:kurtcross}) (dashed lines).
-\textbf{\color{red} For reference we show the first non--trivial corrections due to reduced shear (black lines), which can be calculated from the Born images.} The quantities shown are the ensemble averages over 8192 realizations of $\kappa$ in the fiducial cosmology $\bb{p}_0$.}
+For reference we show the first non--trivial corrections due to reduced shear (black lines), which can be calculated from the Born images.
+The quantities shown are the ensemble averages over 8192 realizations of $\kappa$ in the fiducial cosmology $\bb{p}_0$.}
 \label{fig:skResiduals}
@@
 \caption{Distributions of the parameter estimator (eq.~\ref{par:fisherest}) over 1000 realizations of an LSST--like survey.
-We show parameter estimates obtained using the $\kappa$ power spectrum (top panels) \textbf{\color{blue} with shape noise added ($n_g=30\,{\rm galaxies/arcmin}^2$)} and the $\kappa$ moments defined in eq.~(\ref{par:moments}) \textbf{\color{blue} with shape noise added with both a galaxy density of 15 (middle panels) and 30 (bottom panels) galaxies/arcmin$^2$}.
+We show parameter estimates obtained using the $\kappa$ power spectrum (top panels) with shape noise added ($n_g=30\,{\rm galaxies/arcmin}^2$) and the $\kappa$ moments defined in eq.~(\ref{par:moments}) with shape noise added with both a galaxy density of 15 (middle panels) and 30 (bottom panels) galaxies/arcmin$^2$.
 In each panel, we show both a control case, in which the mock observation has been constructed with the Born approximation (blue), and the ``real'' case, in which the observation has been constructed with full ray--tracing (green).
 The $\kappa$ power spectrum from which the constraints in the upper panel have been derived, has been measured in 100 uniformly spaced bands with $\ell \in [150,10000]$.
-\textbf{\color{blue} A Gaussian smoothing window of size $\theta_G=0.5\,{\rm arcmin}$ has been applied to the $\kappa$ maps prior to measuring the moments.}}
+A Gaussian smoothing window of size $\theta_G=0.5\,{\rm arcmin}$ has been applied to the $\kappa$ maps prior to measuring the moments.}
 \label{fig:parbias}
@@
 \end{center}
-\caption{Parameter bias \textbf{\color{blue}, obtained from the $\kappa$ power spectrum, as a function of} the galaxy density angular $n_g$ used to compute the shape noise rms in eq.
+\caption{Parameter bias, obtained from the $\kappa$ power spectrum, as a function of the galaxy density angular $n_g$ used to compute the shape noise rms in eq.
 (\ref{par:shaperms}).
@@
 We also studied how our conclusions are influenced by the survey angular galaxy density $n_g$, which controls the amplitude of the shape noise in the $\kappa$ reconstruction.
-\textbf{\color{blue} The scaling of the power spectrum--induced} parameter bias with $n_g$ is shown in Figure \ref{fig:parbiasSN}.
+The scaling of the power spectrum--induced parameter bias with $n_g$ is shown in Figure \ref{fig:parbiasSN}.
 
@@
 Figure \ref{fig:skResiduals} shows that the geodesic and lens--lens contributions to the $\kappa$ skewness and kurtosis are comparable and that the lowest non--trivial post--Born corrections can fully account for the discrepancy between the Born--approximated quantities and the fully ray--traced ones.
-\textbf{\color{red} The geodesic and lens--lens corrections to the skewness we find agree, as orders of magnitude, with the ones already published in \citep{WLBispectrumDodelson}, although our measured reduced shear correction is larger.
-We stress, however, that our estimates and the ones in \citep{WLBispectrumDodelson} have been produced under different assumptions, in particular \citep{WLBispectrumDodelson} use a fully analytical approach based on the Limber approximation, different form forms for the smoothing windows and use their own assumptions for the form of the $\kappa$ bi--spectrum.} Figs.
-\ref{fig:psResiduals} and \ref{fig:skResiduals} indicate \textbf{\color{red} that truncating $\kappa$ at $O(\Phi^2)$ post--Born terms, leads to inaccurate predictions of the power spectrum and moments.
-In particular, higher-order terms involving $\langle \kappa_{\rm born}^n \kappa_{\rm ll}^m \kappa_{\rm geo}^2\rangle$ and higher, cause large deviations (as seen by the difference between the solid and dashed green curves) that, in an exact approach, are canceled by $O(\Phi^3)$ corrections to $\kappa$, as pointed out by \citep{HirataKrause,CMBPrattenLewis,ScoccimarroLoop}}.
+The geodesic and lens--lens corrections to the skewness we find agree, as orders of magnitude, with the ones already published in \citep{WLBispectrumDodelson}, although our measured reduced shear correction is larger.
+We stress, however, that our estimates and the ones in \citep{WLBispectrumDodelson} have been produced under different assumptions, in particular \citep{WLBispectrumDodelson} use a fully analytical approach based on the Limber approximation, different form forms for the smoothing windows and use their own assumptions for the form of the $\kappa$ bi--spectrum.
+Figs.
+\ref{fig:psResiduals} and \ref{fig:skResiduals} indicate that truncating $\kappa$ at $O(\Phi^2)$ post--Born terms, leads to inaccurate predictions of the power spectrum and moments.
+In particular, higher-order terms involving $\langle \kappa_{\rm born}^n \kappa_{\rm ll}^m \kappa_{\rm geo}^2\rangle$ and higher, cause large deviations (as seen by the difference between the solid and dashed green curves) that, in an exact approach, are canceled by $O(\Phi^3)$ corrections to $\kappa$, as pointed out by \citep{HirataKrause,CMBPrattenLewis,ScoccimarroLoop}.
 Therefore, in practice, in order to go beyond Born approximation, it is more advantageous, both for accuracy and for CPU time, to perform full ray--tracing (whose computational cost is comparable to those of the $O(\Phi^2)$ line--of--sight integrals; Table \ref{tab:benchmarks}).
 
-\textbf{\color{red} In real observations, the convergence $\kappa$ is reconstructed via the Kaiser--Squires inversion procedure \citep{KaiserSquires}, applied on the reduced shear $\pmb{\gamma}/(1-\kappa)$.
+In real observations, the convergence $\kappa$ is reconstructed via the Kaiser--Squires inversion procedure \citep{KaiserSquires}, applied on the reduced shear $\pmb{\gamma}/(1-\kappa)$.
 In order to avoid possible biases in parameter inferences, one needs to take this into account.
 This can be done within the Born approximation, as the quantity $\kappa\pmb{\gamma}$ is the dominant $O(\Phi^2)$ reduced shear correction, which can be calculated from the Born $\kappa$ images and is independent from the line of sight integration procedure.
-The $O(\Phi^2)$ reduced shear correction to $\kappa$ is easily incorporated in the forward models.}
+The $O(\Phi^2)$ reduced shear correction to $\kappa$ is easily incorporated in the forward models.
 
@@
 This can lead to parameter bias when fitting observations.
-Figure \ref{fig:parbias} studies this possibility and shows that the Born approximation is sufficient to fit cosmology with the power spectrum of an LSST--like survey, \textbf{\color{blue} with the result holding also for galaxy densities as high as $60\,{\rm galaxies/arcmin}^2$, as can be seen in Figure \ref{fig:parbiasSN}.
+Figure \ref{fig:parbias} studies this possibility and shows that the Born approximation is sufficient to fit cosmology with the power spectrum of an LSST--like survey, with the result holding also for galaxy densities as high as $60\,{\rm galaxies/arcmin}^2$, as can be seen in Figure \ref{fig:parbiasSN}.
 The accuracy requirements, however, might be stricter for deeper surveys, such as Euclid \citep{Euclid}, which requires systematic effects not to be greater than $\sigma/3$.
-While the Born approximation is accurate in predicting the $\kappa$ power spectrum, the same is not true for higher order $\kappa$ moments}.
+While the Born approximation is accurate in predicting the $\kappa$ power spectrum, the same is not true for higher order $\kappa$ moments.
 We have previously shown that these moments contain significantly more information than the power spectrum \citep{MinkPetri}, an expectation that was confirmed when fitting CFHTLenS data~\citep{CFHTMink}.
-The middle \textbf{\color{blue} and bottom} row of panels in Figure \ref{fig:parbias} show that indeed the constraints from the moments are $\approx$ 2 times tighter than from the power spectrum (seen by the narrow widths of the PDFs).
+The middle and bottom row of panels in Figure \ref{fig:parbias} show that indeed the constraints from the moments are $\approx$ 2 times tighter than from the power spectrum (seen by the narrow widths of the PDFs).
 As a result, highly significant biases are observed when fitting an observation with Born--approximated $\kappa$ moments.
-\textbf{\color{blue} Although the presence of Gaussian galaxy shape noise reduces the significance of this bias, it cannot completely eliminate it, as higher order moments are sensitive to non--Gaussian statistical information in $\kappa$ images.
+Although the presence of Gaussian galaxy shape noise reduces the significance of this bias, it cannot completely eliminate it, as higher order moments are sensitive to non--Gaussian statistical information in $\kappa$ images.
 These results lead us to the conclusion that the Born approximation is sufficient for future WL analyses that use the $\kappa$ power spectrum to constrain cosmology.
 This approach also has the advantage of being 4 times computationally faster than full ray--tracing, as we show in Table \ref{tab:benchmarks} for a selected reference test case.
-When considering higher order moments of $\kappa$, however, full ray--tracing is required in order to obtain unbiased constraints.}
+When considering higher order moments of $\kappa$, however, full ray--tracing is required in order to obtain unbiased constraints.
 
@@
 \item Using the \ttt{LensTools} software package, Born integration costs 4 times less than ray--tracing, and consumes about half as much memory.
-\item The Born approximation for the $\kappa$ power spectrum leads to negligible parameter bias for an LSST--like survey\textbf{\color{blue}, and holds for survey galaxy densities as high as $60\,{\rm galaxies/arcmin^2}$.}
-\item Fitting an observation with Born--approximated higher $\kappa$ moments leads to significant bias in the $(\Omega_m,w_0,\sigma_8)$ triplet\textbf{\color{blue}, even in the presence of galaxy shape noise.}
+\item The Born approximation for the $\kappa$ power spectrum leads to negligible parameter bias for an LSST--like survey, and holds for survey galaxy densities as high as $60\,{\rm galaxies/arcmin^2}$.
+\item Fitting an observation with Born--approximated higher $\kappa$ moments leads to significant bias in the $(\Omega_m,w_0,\sigma_8)$ triplet, even in the presence of galaxy shape noise.    
 \end{itemize}
@@
 In this work we examined the validity of the Born approximation for WL galaxy surveys, but a similar study could in principle be carried for the lensing potential reconstruction from CMB temperature and polarization data \citep{CMBCalabrese}.
-Lensing of the CMB probes structures over a wider range of redshifts and hence CMB lensing observables can be expected to \textbf{\color{blue} closer to} Gaussian than their galaxy lensing counterparts.
-This suggests the possibility that non--Gaussian features in CMB lensing data could come from post--Born corrections of $O(\Phi^2)$ rather than \textbf{\color{blue} from intrinsic} non--Gaussianity in the Born $O(\Phi)$ terms.
+Lensing of the CMB probes structures over a wider range of redshifts and hence CMB lensing observables can be expected to closer to Gaussian than their galaxy lensing counterparts.
+This suggests the possibility that non--Gaussian features in CMB lensing data could come from post--Born corrections of $O(\Phi^2)$ rather than from intrinsic non--Gaussianity in the Born $O(\Phi)$ terms.
 This possibility has been suggested by \citep{CMBPrattenLewis}, who looked at the CMB lensing $\kappa$ bi--spectrum.

### 2017-05-06 Paper/paper.tex
round 3 of referee comments

@@
 We also find that cosmological parameter bias induced by the Born approximated power spectrum is negligible even for an LSST--like survey, once galaxy shape noise is considered.
-The same conclusion is not true when considering higher order statistics, such as the $\kappa$ skewness and kurtosis.
-Using the \ttt{LensTools} software suite, we show that the Born approximation saves a factor of 4 in computing time with respect to the full ray--tracing in reconstructing the convergence.
+\textbf{\color{red} When considering higher order statistics such as the $\kappa$ skewness and kurtosis, however, we find significant bias of up to 2.5$\sigma$.} Using the \ttt{LensTools} software suite, we show that the Born approximation saves a factor of 4 in computing time with respect to the full ray--tracing in reconstructing the convergence.
 \end{abstract}
@@
 This however is a challenging problem due to the non--linear nature of WL image fields.
-Numerical efforts for feature forward modeling are based on ray--tracing simulations that make use of the multi--lens--plane algorithm \citep{RayTracingJain,RayTracingHartlap,RayTracingPN}, or the direct approach \citep{RayTracingBarreira}, to predict cosmic shear from outputs of $N$--body simulations.
+Numerical efforts for feature forward modeling are based on ray--tracing simulations that make use of the multi--lens--plane algorithm \citep{RayTracingJain,RayTracingHartlap,RayTracingPN}, or the direct approach \citep{RayTracingBecker,RayTracingBode,RayTracingBarreira}, to predict cosmic shear from outputs of $N$--body simulations.
 Approximate techniques based on the Born approximation allow for a computationally faster, but potentially inaccurate, forward modeling which requires only knowledge of the matter density contrast integrated along the observer unperturbed line of sight.
@@
 \caption{CPU time and memory usage benchmarks for the convergence reconstruction operations.
-The test case we considered consists in a discretization with $N_l=42$ uniformly spaced lenses between the observer and the sources at $z_s=2$, each with a resolution of $4096^2$ pixels.
-The $\kappa$ field is resolved with $2048^2$ light rays.
-We show both the runtime for producing a single field of view and the CPU hours needed to perform the reconstruction 1000 times, to mock an LSST--like galaxy survey.
+The test case we \textbf{\color{red} refer to in this table matches the specifications of the simulations used in this work.
+We we divide the line of sight in $N_l=42$ uniformly spaced lenses between the observer and the sources at $z_s=2$, each with a resolution of $4096^2$ pixels.
+The $\kappa$ field is resolved with $2048^2$ light rays.} We show both the runtime for producing a single field of view and the CPU hours needed to perform the reconstruction 1000 times, to mock an LSST--like galaxy survey.
 Run times do not include the Poisson solution calculation, as this can be recycled to produce multiple field of view realizations.
@@
 The images have been smoothed with a Gaussian kernel of size $\theta_G=0.5\,{\rm arcmin}$.
-Note the different scales in the bottom panels: the geodesic term (right), is over an order of magnitude larger than the lens--lens term (left), and is comparable in level and detailed structure to the full residual (top right).}
+Note the different scales in the bottom panels: the geodesic term (right), is over an order of magnitude larger than the lens--lens term (left), and is comparable in level and detailed structure to the full residual (top right).
+\textbf{\color{blue} The ``22'' and ``33'' post--Born corrections to the $\kappa$ power spectrum, which are widely mentioned in the literature \citep{HirataKrause} are not directly observable from these $\kappa$ images.}}
 \label{fig:csample}
@@
 The right panel shows the residuals between the power spectrum of the full ray--traced $\kappa$ field and the one obtained with the Born approximation.
-For reference, we show the shape noise contributions (black dashed) and the first non--trivial reduced shear corrections to $P^{\kappa\kappa}$(purple), which can be both added to the forward models after the line of sight integration.
-Gaussian convolution effects with a window of size $\theta_G=0.5\,{\rm arcmin}$ are included.
+For reference, we show the shape noise contributions (black dashed) and the first non--trivial reduced shear corrections to $P^{\kappa\kappa}$ \textbf{\color{red} (black solid)}, which can be both added to the forward models after the line of sight integration.
+\textbf{\color{red} We also show as an orange line the level of cosmic variance for the power spectrum expected in a LSST--like survey.} Gaussian convolution effects with a window of size $\theta_G=0.5\,{\rm arcmin}$ are included.
 The residuals are compared to the two $O(\Phi^3)$ terms $2P_{\rm born,ll},2P_{\rm born,geo}$.
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
-\includegraphics[scale=0.45]{Figures/bias_ngal_convergence_powerSN_s0_nb100.eps}
+\includegraphics[scale=0.45]{Figures/bias_ngal_convergence_powerSN_s0_nb100.eps} \includegraphics[scale=0.45]{Figures/bias_ngal_convergence_momentsSN_s50_nb9.eps}
 \end{center}
-\caption{Parameter bias, obtained from the $\kappa$ power spectrum, as a function of the galaxy density angular $n_g$ used to compute the shape noise rms in eq.
+\caption{Parameter bias, obtained from the $\kappa$ power spectrum \textbf{\color{red} (left panel) and the $\kappa$ moments (right panel)}, as a function of the galaxy density angular $n_g$ used to compute the shape noise rms in eq.
 (\ref{par:shaperms}).
@@
 \label{fig:parbiasSN}
-\end{figure}
+\end{figure*}
 
@@
 We also studied how our conclusions are influenced by the survey angular galaxy density $n_g$, which controls the amplitude of the shape noise in the $\kappa$ reconstruction.
-The scaling of the power spectrum--induced parameter bias with $n_g$ is shown in Figure \ref{fig:parbiasSN}.
+\textbf{\color{red}The scaling of the bias induced by the Born approximation on the power spectrum and $\kappa$ moments as a function of} $n_g$ is shown in Figure \ref{fig:parbiasSN}.
 
@@
 The geodesic and lens--lens corrections to the skewness we find agree, as orders of magnitude, with the ones already published in \citep{WLBispectrumDodelson}, although our measured reduced shear correction is larger.
-We stress, however, that our estimates and the ones in \citep{WLBispectrumDodelson} have been produced under different assumptions, in particular \citep{WLBispectrumDodelson} use a fully analytical approach based on the Limber approximation, different form forms for the smoothing windows and use their own assumptions for the form of the $\kappa$ bi--spectrum.
-Figs.
+\textbf{\color{red} We stress, however, that our estimates and the ones in \citep{WLBispectrumDodelson} have been produced under different assumptions.
+In particular, \citep{WLBispectrumDodelson} use a fully analytical approach based on the Limber approximation, they consider different smoothing window functions and use their own assumptions for the bi--spectrum of $\kappa$.} Figs.
 \ref{fig:psResiduals} and \ref{fig:skResiduals} indicate that truncating $\kappa$ at $O(\Phi^2)$ post--Born terms, leads to inaccurate predictions of the power spectrum and moments.
 In particular, higher-order terms involving $\langle \kappa_{\rm born}^n \kappa_{\rm ll}^m \kappa_{\rm geo}^2\rangle$ and higher, cause large deviations (as seen by the difference between the solid and dashed green curves) that, in an exact approach, are canceled by $O(\Phi^3)$ corrections to $\kappa$, as pointed out by \citep{HirataKrause,CMBPrattenLewis,ScoccimarroLoop}.
-Therefore, in practice, in order to go beyond Born approximation, it is more advantageous, both for accuracy and for CPU time, to perform full ray--tracing (whose computational cost is comparable to those of the $O(\Phi^2)$ line--of--sight integrals; Table \ref{tab:benchmarks}).
+\textbf{\color{blue} For example, regarding the skewness of $\kappa$, the residuals $\kappa^3_{\rm born+geo}-\kappa^3_{\rm born}$ contain terms up to order $O(\Phi^6)$.
+Some of these high order terms should be canceled by $O(\Phi^3)$ corrections to the $\kappa$ image.
+These cancellations do not show up if one truncates the expansion of $\kappa$ to $O(\Phi^2)$.
+This is the reason behind the discrepancy between the green curves in Figure \ref{fig:skResiduals}.} Therefore, in practice, in order to go beyond Born approximation, it is more advantageous, both for accuracy and for CPU time, to perform full ray--tracing (whose computational cost is comparable to those of the $O(\Phi^2)$ line--of--sight integrals; Table \ref{tab:benchmarks}).
 
@@
 Figure \ref{fig:pdfMoments} shows the PDF of the 9 $\kappa$ moments defined in eq.~(\ref{par:moments}) over 1000 realizations of an LSST--like survey.
-This figure clearly shows that, while the Born approximation is a good predictor of the quadratic moments $\pmb{\mu}_2$ within one standard deviation, the higher moments $\pmb{\mu}_3,\pmb{\mu}_4$ show 2 to 3$\sigma$ deviations from their Born--approximated counterparts.
-This can lead to parameter bias when fitting observations.
-Figure \ref{fig:parbias} studies this possibility and shows that the Born approximation is sufficient to fit cosmology with the power spectrum of an LSST--like survey, with the result holding also for galaxy densities as high as $60\,{\rm galaxies/arcmin}^2$, as can be seen in Figure \ref{fig:parbiasSN}.
+\textbf{\color{red} This figure clearly shows that, while the Born approximation is a good predictor of the quadratic moments $\pmb{\mu}_2$ within one standard deviation, the higher moments $\pmb{\mu}_3,\pmb{\mu}_4$ show 2 to 3$\sigma$ deviations from their Born--approximated counterparts.
+This can lead to parameter bias when fitting observations.} Figure \ref{fig:parbias} studies this possibility and shows that the Born approximation is sufficient to fit cosmology with the power spectrum of an LSST--like survey, with the result holding also for galaxy densities as high as $60\,{\rm galaxies/arcmin}^2$, as can be seen in Figure \ref{fig:parbiasSN}.
 The accuracy requirements, however, might be stricter for deeper surveys, such as Euclid \citep{Euclid}, which requires systematic effects not to be greater than $\sigma/3$.
-While the Born approximation is accurate in predicting the $\kappa$ power spectrum, the same is not true for higher order $\kappa$ moments.
+\textbf{\color{red} While the Born approximation is accurate in predicting the $\kappa$ power spectrum, the same is not true for higher order $\kappa$ moments.
 We have previously shown that these moments contain significantly more information than the power spectrum \citep{MinkPetri}, an expectation that was confirmed when fitting CFHTLenS data~\citep{CFHTMink}.
@@
 These results lead us to the conclusion that the Born approximation is sufficient for future WL analyses that use the $\kappa$ power spectrum to constrain cosmology.
-This approach also has the advantage of being 4 times computationally faster than full ray--tracing, as we show in Table \ref{tab:benchmarks} for a selected reference test case.
-When considering higher order moments of $\kappa$, however, full ray--tracing is required in order to obtain unbiased constraints.
+This approach also has the advantage of being 4 times computationally faster than full ray--tracing, as we show in Table \ref{tab:benchmarks} for a selected reference test case.}
+
+\textbf{\color{blue} A few technical considerations are in order here.
+When adopting the Born approximation, it seems tempting to collapse all the particles in the $N$--body outputs in a single lens plane transverse to the line of sight, assigning to each particle a weight $W(\chi,\chi_s)$.
+Unfortunately the function $W$ is concave in $\chi$ and this ``single--lens--plane'' approach under--estimates $\kappa$ by a non--negligible amount.
+In order to avoid this concavity effect we need to use multiple discrete steps.
+We do not need to perform the full ray--tracing calculations however, but we can simply add the density values on the lens planes as light rays travel between them.
+The Born algorithm scales as $O(N_l)$.
+Ray--tracing has the same big $O$ complexity, but takes more time because at each step in the integration one needs to compute $O(N_R)$ second derivatives and $2\times 2$ matrix products, where $N_R$ is the number of light rays that resolve the $\kappa$ image.
+The quadratic corrections to $\kappa$ can also be computed in $O(N_l)$ when appropriate caching is used, but has a slightly different runtime compared to ray--tracing due to the different structure of the linear algebra operations involved.
+The memory usage is regulated by the number of two dimensional grids that need to be cached in order to perform the integration steps: in the Born case just a density grid is needed, but in the other cases one needs to keep track of the intermediate $\Phi$ derivatives as well.}
+
+When forward modeling higher order moments of $\kappa$ full ray--tracing is required in order to obtain unbiased constraints.
 
@@
 \begin{itemize}
-\item The lowest--order post--Born corrections to the convergence power spectrum, skewness and kurtosis are sufficient to fully account for the discrepancies between ray--tracing and the Born approximation.
+\item \textbf{\color{blue} The post--Born corrections to the convergence power spectrum, skewness and kurtosis are well explained by the next--to--leading orders in the $\Phi$ expansion of each statistic.}
 \item Using the \ttt{LensTools} software package, Born integration costs 4 times less than ray--tracing, and consumes about half as much memory.
 \item The Born approximation for the $\kappa$ power spectrum leads to negligible parameter bias for an LSST--like survey, and holds for survey galaxy densities as high as $60\,{\rm galaxies/arcmin^2}$.
-\item Fitting an observation with Born--approximated higher $\kappa$ moments leads to significant bias in the $(\Omega_m,w_0,\sigma_8)$ triplet, even in the presence of galaxy shape noise.    
+\item \textbf{\color{red} Fitting an observation with Born--approximated higher $\kappa$ moments leads to significant bias in the $(\Omega_m,w_0,\sigma_8)$ triplet, even in the presence of galaxy shape noise.}
 \end{itemize}

### 2017-05-06 Paper/Figures/generate.py

@@ -113,7 +113,9 @@ def powerResiduals(cmd_args,collection="c0",fontsize=22):
 	ax[1].plot(ell,ell*(ell+1)*smooth*(np.abs(pFull.mean(0)-pBorn.mean(0)))/(2.0*np.pi),label=r"${\rm ray-born}$")
 	ax[1].plot(ell,ell*(ell+1)*smooth*np.abs(pGP_cross.mean(0))/np.pi,label=r"$2{\rm born}\times{\rm geo}$")
 	ax[1].plot(ell,ell*(ell+1)*smooth*np.abs(pLL_cross.mean(0))/np.pi,label=r"$2{\rm born}\times{\rm ll}$")
-	ax[1].plot(ell,ell*(ell+1)*smooth*np.abs(p_redshear_cross.mean(0))/np.pi,label=r"$2\kappa_{\rm born}\times(\kappa\gamma)_{\rm born}$")
+	ax[1].plot(ell,ell*(ell+1)*smooth*np.abs(p_redshear_cross.mean(0))/np.pi,label=r"$2\kappa_{\rm born}\times(\kappa\gamma)_{\rm born}$",color=sns.xkcd_rgb["dark grey"])
+	ax[1].plot(ell,ell*(ell+1)*smooth*pFull.std(0)/(2.0*np.pi)/1000.,label=r"${\rm Cosmic}$ ${\rm variance (LSST)}$",color=sns.xkcd_rgb["pumpkin"])
+	ax[1].plot(ell,ell*(ell+1)*smooth*np.abs(pFull.mean(0)-pBorn.mean(0)-2*pGP_cross.mean(0)-2*pLL_cross.mean(0))/(2.0*np.pi),label=r"${\rm ray-born}-2{\rm born}\times{\rm geo}-2{\rm born}\times{\rm ll}$",linestyle="--",color=sns.xkcd_rgb["denim blue"])
 
 	#Shape noise
 	pshape = ((0.15+0.035*2.0)**2)/((45*(u.arcmin**-2)).to(u.rad**-2).value)
@@ -355,7 +357,10 @@ def pbBias(cmd_args,feature_name="convergence_power_s0_nb100",title="Power spect
 	fig.tight_layout()
 	fig.savefig("bias_{0}.{1}".format(feature_name,cmd_args.type))
 
[…]

### 2017-05-17 Paper/paper.tex
round 4 of referee comments

@@
 The difference is shown in units of the estimator standard deviation.
-We show the trend for $\Omega_m$ (blue), $w_0$ (red) and $\sigma_8$ (green).}
+We show the trend for $\Omega_m$ (blue), $w_0$ (red) and $\sigma_8$ (green).
+\textbf{\color{ForestGreen} The quoted $\sigma_{\rm ray}$ is calculated as a standard deviation.
+Parameter estimates PDFs are not Gaussian because the estimator $\hat{\mathbf{d}}_{\rm obs}$ which appears in equation (\ref{par:fisherest}) in general is non--Gaussian distributed.
+When we average over multiple fields of view though (this is the case for LSST), the Gaussianity assumption is justified by the central limit theorem.
+This is why the standard deviation $\sigma_{\rm ray}$ is a reasonable benchmark for statistical significance.}}
 \label{fig:parbiasSN}
@@
 We can conclude that the dominant contributions to the residuals come from the Born--geodesic cross power, which dominates the Born--lens--lens cross power by two orders of magnitude on small scales.
-Figure \ref{fig:skResiduals} shows that the geodesic and lens--lens contributions to the $\kappa$ skewness and kurtosis are comparable and that the lowest non--trivial post--Born corrections can fully account for the discrepancy between the Born--approximated quantities and the fully ray--traced ones.
+\textbf{\color{ForestGreen} The dashed blue line in Figure \ref{fig:psResiduals} corresponds to the residuals $P_{\rm ray} - P_{\rm born} - 2P_{\rm born,ll} - 2P_{\rm born,geo}$, which are comparable to the $O(\Phi^3)$ terms themselves.
+This means that the $O(\Phi^4)$ post--Born terms are completely overshot by cosmic variance and numerical noise in this case.} Figure \ref{fig:skResiduals} shows that the geodesic and lens--lens contributions to the $\kappa$ skewness and kurtosis are comparable and that the lowest non--trivial post--Born corrections can fully account for the discrepancy between the Born--approximated quantities and the fully ray--traced ones.
 The geodesic and lens--lens corrections to the skewness we find agree, as orders of magnitude, with the ones already published in \citep{WLBispectrumDodelson}, although our measured reduced shear correction is larger.
@@
 \section*{Acknowledgments}
+\textbf{\color{ForestGreen} We thank the anonymous referee for the useful and insightful comments}.
 We thank Uro\v{s} Seljak and Colin Hill for useful discussions.

### 2017-05-18 Paper/paper.tex
remove color fonts

--- 2017-03-23 Paper/paper.tex
@@
 We also find that cosmological parameter bias induced by the Born approximated power spectrum is negligible even for an LSST--like survey, once galaxy shape noise is considered.
-The same conclusion is not true when considering higher order statistics, such as the $\kappa$ skewness and kurtosis.
+When considering higher order statistics such as the $\kappa$ skewness and kurtosis, however, we find significant bias of up to 2.5$\sigma$.
 Using the \ttt{LensTools} software suite, we show that the Born approximation saves a factor of 4 in computing time with respect to the full ray--tracing in reconstructing the convergence.
@@
 \caption{CPU time and memory usage benchmarks for the convergence reconstruction operations.
-The test case we considered consists in a discretization with $N_l=42$ uniformly spaced lenses between the observer and the sources at $z_s=2$, each with a resolution of $4096^2$ pixels.
+The test case we refer to in this table matches the specifications of the simulations used in this work.
+We we divide the line of sight in $N_l=42$ uniformly spaced lenses between the observer and the sources at $z_s=2$, each with a resolution of $4096^2$ pixels.
 The $\kappa$ field is resolved with $2048^2$ light rays.
@@
 The images have been smoothed with a Gaussian kernel of size $\theta_G=0.5\,{\rm arcmin}$.
-Note the different scales in the bottom panels: the geodesic term (right), is over an order of magnitude larger than the lens--lens term (left), and is comparable in level and detailed structure to the full residual (top right).}
+Note the different scales in the bottom panels: the geodesic term (right), is over an order of magnitude larger than the lens--lens term (left), and is comparable in level and detailed structure to the full residual (top right).
+The ``22'' and ``33'' post--Born corrections to the $\kappa$ power spectrum, which are widely mentioned in the literature \citep{HirataKrause} are not directly observable from these $\kappa$ images.}
 \label{fig:csample}
@@
 The right panel shows the residuals between the power spectrum of the full ray--traced $\kappa$ field and the one obtained with the Born approximation.
-For reference, we show the shape noise contributions (black dashed) and the first non--trivial reduced shear corrections to $P^{\kappa\kappa}$(purple), which can be both added to the forward models after the line of sight integration.
+For reference, we show the shape noise contributions (black dashed) and the first non--trivial reduced shear corrections to $P^{\kappa\kappa}$ (black solid), which can be both added to the forward models after the line of sight integration.
+We also show as an orange line the level of cosmic variance for the power spectrum expected in a LSST--like survey.
 Gaussian convolution effects with a window of size $\theta_G=0.5\,{\rm arcmin}$ are included.
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
-\includegraphics[scale=0.45]{Figures/bias_ngal_convergence_powerSN_s0_nb100.eps}
+\includegraphics[scale=0.45]{Figures/bias_ngal_convergence_powerSN_s0_nb100.eps} \includegraphics[scale=0.45]{Figures/bias_ngal_convergence_momentsSN_s50_nb9.eps}
 \end{center}
-\caption{Parameter bias, obtained from the $\kappa$ power spectrum, as a function of the galaxy density angular $n_g$ used to compute the shape noise rms in eq.
+\caption{Parameter bias, obtained from the $\kappa$ power spectrum (left panel) and the $\kappa$ moments (right panel), as a function of the galaxy density angular $n_g$ used to compute the shape noise rms in eq.
 (\ref{par:shaperms}).
@@
 The difference is shown in units of the estimator standard deviation.
-We show the trend for $\Omega_m$ (blue), $w_0$ (red) and $\sigma_8$ (green).}
+We show the trend for $\Omega_m$ (blue), $w_0$ (red) and $\sigma_8$ (green).
+The quoted $\sigma_{\rm ray}$ is calculated as a standard deviation.
+Parameter estimates PDFs are not Gaussian because the estimator $\hat{\mathbf{d}}_{\rm obs}$ which appears in equation (\ref{par:fisherest}) in general is non--Gaussian distributed.
+When we average over multiple fields of view though (this is the case for LSST), the Gaussianity assumption is justified by the central limit theorem.
+This is why the standard deviation $\sigma_{\rm ray}$ is a reasonable benchmark for statistical significance.}
 \label{fig:parbiasSN}
-\end{figure}
+\end{figure*}
 
@@
 We also studied how our conclusions are influenced by the survey angular galaxy density $n_g$, which controls the amplitude of the shape noise in the $\kappa$ reconstruction.
-The scaling of the power spectrum--induced parameter bias with $n_g$ is shown in Figure \ref{fig:parbiasSN}.
+The scaling of the bias induced by the Born approximation on the power spectrum and $\kappa$ moments as a function of $n_g$ is shown in Figure \ref{fig:parbiasSN}.
 
@@
 We can conclude that the dominant contributions to the residuals come from the Born--geodesic cross power, which dominates the Born--lens--lens cross power by two orders of magnitude on small scales.
+The dashed blue line in Figure \ref{fig:psResiduals} corresponds to the residuals $P_{\rm ray} - P_{\rm born} - 2P_{\rm born,ll} - 2P_{\rm born,geo}$, which are comparable to the $O(\Phi^3)$ terms themselves.
+This means that the $O(\Phi^4)$ post--Born terms are completely overshot by cosmic variance and numerical noise in this case.
 Figure \ref{fig:skResiduals} shows that the geodesic and lens--lens contributions to the $\kappa$ skewness and kurtosis are comparable and that the lowest non--trivial post--Born corrections can fully account for the discrepancy between the Born--approximated quantities and the fully ray--traced ones.
 The geodesic and lens--lens corrections to the skewness we find agree, as orders of magnitude, with the ones already published in \citep{WLBispectrumDodelson}, although our measured reduced shear correction is larger.
-We stress, however, that our estimates and the ones in \citep{WLBispectrumDodelson} have been produced under different assumptions, in particular \citep{WLBispectrumDodelson} use a fully analytical approach based on the Limber approximation, different form forms for the smoothing windows and use their own assumptions for the form of the $\kappa$ bi--spectrum.
+We stress, however, that our estimates and the ones in \citep{WLBispectrumDodelson} have been produced under different assumptions.
+In particular, \citep{WLBispectrumDodelson} use a fully analytical approach based on the Limber approximation, they consider different smoothing window functions and use their own assumptions for the bi--spectrum of $\kappa$.
 Figs.
@@
 In particular, higher-order terms involving $\langle \kappa_{\rm born}^n \kappa_{\rm ll}^m \kappa_{\rm geo}^2\rangle$ and higher, cause large deviations (as seen by the difference between the solid and dashed green curves) that, in an exact approach, are canceled by $O(\Phi^3)$ corrections to $\kappa$, as pointed out by \citep{HirataKrause,CMBPrattenLewis,ScoccimarroLoop}.
+For example, regarding the skewness of $\kappa$, the residuals $\kappa^3_{\rm born+geo}-\kappa^3_{\rm born}$ contain terms up to order $O(\Phi^6)$.
+Some of these high order terms should be canceled by $O(\Phi^3)$ corrections to the $\kappa$ image.
+These cancellations do not show up if one truncates the expansion of $\kappa$ to $O(\Phi^2)$.
+This is the reason behind the discrepancy between the green curves in Figure \ref{fig:skResiduals}.
 Therefore, in practice, in order to go beyond Born approximation, it is more advantageous, both for accuracy and for CPU time, to perform full ray--tracing (whose computational cost is comparable to those of the $O(\Phi^2)$ line--of--sight integrals; Table \ref{tab:benchmarks}).
@@
 This approach also has the advantage of being 4 times computationally faster than full ray--tracing, as we show in Table \ref{tab:benchmarks} for a selected reference test case.
-When considering higher order moments of $\kappa$, however, full ray--tracing is required in order to obtain unbiased constraints.
+
+A few technical considerations are in order here.
+When adopting the Born approximation, it seems tempting to collapse all the particles in the $N$--body outputs in a single lens plane transverse to the line of sight, assigning to each particle a weight $W(\chi,\chi_s)$.
+Unfortunately the function $W$ is concave in $\chi$ and this ``single--lens--plane'' approach under--estimates $\kappa$ by a non--negligible amount.
+In order to avoid this concavity effect we need to use multiple discrete steps.
+We do not need to perform the full ray--tracing calculations however, but we can simply add the density values on the lens planes as light rays travel between them.
+The Born algorithm scales as $O(N_l)$.
+Ray--tracing has the same big $O$ complexity, but takes more time because at each step in the integration one needs to compute $O(N_R)$ second derivatives and $2\times 2$ matrix products, where $N_R$ is the number of light rays that resolve the $\kappa$ image.
+The quadratic corrections to $\kappa$ can also be computed in $O(N_l)$ when appropriate caching is used, but has a slightly different runtime compared to ray--tracing due to the different structure of the linear algebra operations involved.
+The memory usage is regulated by the number of two dimensional grids that need to be cached in order to perform the integration steps: in the Born case just a density grid is needed, but in the other cases one needs to keep track of the intermediate $\Phi$ derivatives as well.
+
+When forward modeling higher order moments of $\kappa$ full ray--tracing is required in order to obtain unbiased constraints.
 
@@
 \begin{itemize}
-\item The lowest--order post--Born corrections to the convergence power spectrum, skewness and kurtosis are sufficient to fully account for the discrepancies between ray--tracing and the Born approximation.
+\item The post--Born corrections to the convergence power spectrum, skewness and kurtosis are well explained by the next--to--leading orders in the $\Phi$ expansion of each statistic. 
 \item Using the \ttt{LensTools} software package, Born integration costs 4 times less than ray--tracing, and consumes about half as much memory.
@@
 \section*{Acknowledgments}
+We thank the anonymous referee for the useful and insightful comments.
 We thank Uro\v{s} Seljak and Colin Hill for useful discussions.
